\subsection{Space and Time}

\begin{tcolorbox}[title=Problem 8, breakable]
    \begin{enumerate}
        \item Use the definition (1.7) to prove that the scalar product 
        is distributive, that is $\vec{r} \cdot (\vec{u} + \vec{v}) = \vec{r} \cdot \vec{u} + \vec{r} \cdot \vec{v}$. 
        \item If $\vec{r}$ and $\vec{s}$ are vectors that depend on time, prove that the product rule for differentiating 
        products applies to $\vec{r} \cdot \vec{s}$, that is, that 
        \[\frac{d}{ds} (\vec{r} \cdot \vec{s}) = \vec{r} \cdot \frac{d \vec{s}}{dt} + \frac{d \vec{r}}{dt} \cdot \vec{s}.\]
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    We have 
    \[
        \vec{r} \cdot (\vec{u} + \vec{v}) 
        = \sum_{i = 1}^3 r_i (u_i + v_i) 
        = \sum_{i = 1}^3 (r_i u_i + r_i v_i) 
        = \sum_{i = 1}^3 r_i u_i + \sum_{i = 1}^3 r_i v_i 
        = \vec{r} \cdot \vec{u} + \vec{r} \cdot \vec{v}.
    \]
\end{proof}

\begin{proof}
    Suppose $\vec{r}$ and $\vec{s}$ depend on time $t$. Then
    \[
        \frac{d}{dt} (\vec{r} \cdot \vec{s}) 
        = \frac{d}{dt} \left( \sum_{i=1}^3 r_i s_i \right)
        = \sum_{i=1}^3 \frac{d}{dt}(r_i s_i)
        = \sum_{i=1}^3 \left( \frac{d r_i}{dt} s_i + r_i \frac{d s_i}{dt} \right)
        = \frac{d \vec{r}}{dt} \cdot \vec{s} + \vec{r} \cdot \frac{d \vec{s}}{dt}.
    \]
\end{proof}


\begin{tcolorbox}[title=Problem 10, breakable]
    A particle moves in a circle (center $O$ and radius $R$)
    with constant angular velocity $\omega$ counterclockwise.
    The circle lies in the $xy$ plane and the particle is on the $x$
    axis at time $t = 0$. Show that the particle's position is given by 
    \[\vec{r}(t) = \hat{x} R \cos(\omega t) + \hat{y} R \sin(\omega t).\]
    Find the particle's velocity and acceleration. 
    What are the magnitude and direction of the acceleration?
    Relate your results to well-known properties of uniform circular motion.
\end{tcolorbox}

\begin{proof}
    We begin with the position of a point $P$ lying on the unit circle 
    \[
        P = (\cos x, \sin x).
    \]
    Now we scale the radius of the circle by $R$ such that the point $P$ lies $R$ away from $O$
    \[
        P = (R\cos x, R\sin x).
    \]
    We let $x = \omega t$ be the position at time $t$ for angular velocity $\omega$, giving 
    \[
        \vec{r}(t) = (R\cos(\omega t), R\sin(\omega t)) 
        = \hat{x} R \cos(\omega t) + \hat{y} R \sin(\omega t).
    \]
    The velocity vector is obtained by differentiating
    \[
        \vec{v}(t) = \frac{d\vec{r}}{dt}
        = (-R\omega \sin(\omega t), R\omega \cos(\omega t)).
    \]
    The acceleration vector is obtained by differentiating again
    \[
        \vec{a}(t) = \frac{d\vec{v}}{dt}
        = (-R\omega^2 \cos(\omega t), -R\omega^2 \sin(\omega t))
        = -\omega^2 \vec{r}(t).
    \]
    The force vector is pulling the point towards the center of the circle.
    The acceleration vector is in the same direction as the force vector,
    so it points toward the origin.
    Thus the magnitude is 
    \[
        \|\vec{a}(t)\| = \omega^2 R,
    \]
    and the direction is toward the center (opposite to the position vector $\vec{r}(t)$).
\end{proof}

\textbf{Solution:}
Imagine you have a string with a ball tied to the end.
As you increase the velocity of the ball you feel a greater force as the ball tries to escape its path.
This corresponds to the $\omega^2$ term in the force magnitude formula.
Now imagine you half the length of the string and spin with equivalent velocity.
You will feel less force corresponding to $\frac{1}{R}$ in the magnitude $\omega^2 R$.


\begin{tcolorbox}[title=Problem 11, breakable]
    The position of a moving particle is given as a function 
    of time $t$ to be 
    \[\vec{r}(t) = \hat{x}b \cos(\omega t) + \hat{y} c \sin(\omega t),\]
    where $b, c$ and $\omega$ are constants. Describe the particles orbit.
\end{tcolorbox}

\begin{proof}
    This is the standard form for an ellipse.
    At $\omega t = 0$ we have $r(t) = (b, 0)$
    and at $\omega t = \pi / 2$ we have $r(t) = (0, c)$.
    The following is the shape.
    \begin{center}
    \begin{tikzpicture}[scale=1.2]
        % Axes
        \draw[->] (-3,0) -- (3,0) node[right] {$x$};
        \draw[->] (0,-3) -- (0,3) node[above] {$y$};

        % Ellipse
        \draw[thick] (0,0) ellipse (2 and 1.5);

        % Points
        \fill (2,0) circle (2pt) node[below right] {$(b,0)$};
        \fill (0,1.5) circle (2pt) node[above left] {$(0,c)$};
    \end{tikzpicture}
    \end{center}
    The particles position changes with angular velocity $\omega$.
\end{proof}


\begin{tcolorbox}[title=Problem 12, breakable]
    The position of a moving particle given as a function of time $t$ to be 
    \[\vec{r}(t) = \hat{x} b \cos(\omega t) + \hat{y} c \sin (\omega t) + \hat{z} v_o t,\]
    where $b, c, v_o$ and $w$ are constants. Describe the particle's orbit.
\end{tcolorbox}

\begin{proof}
    When $v_0 = 0$ we have Problem 11.
    Therefore suppose $v_0 \ne 0$.
    Take $z$ to be the `height' axis.
    If $v_0 > 0$ ($v_0 < 0$) the particle continuously increases (decreases) in height over time.
    If we take two velocities equal but opposite in sign then the path traced is equivalent 
    but the direction they go in terms of height changes.
    The following is the shape.
    \begin{center}
    \begin{tikzpicture}[scale=1.1]
        % Axes
        \draw[->] (-3,0,0) -- (3,0,0) node[right] {$x$};
        \draw[->] (0,-3,0) -- (0,3,0) node[above] {$y$};
        \draw[->] (0,0,0) -- (0,0,4) node[above] {$z$};

        % Helix (projected ellipse + upward motion)
        \draw[domain=0:6*pi, samples=100, smooth, variable=\t]
            plot ({2*cos(\t r)}, {1.5*sin(\t r)}, {\t/3});

    \end{tikzpicture}
    \end{center}
\end{proof}


\begin{tcolorbox}[title=Problem 17, breakable]
    \begin{enumerate}
        \item Prove that the vector product $\vec{r} \times \vec{s}$ as defined by (1.9)
        is distributive, that is, that $\vec{r} \times (\vec{u} + \vec{v}) = (\vec{r} \times \vec{u}) + (\vec{r} \times \vec{v})$.
        \item Prove the product rule 
        \[\frac{d}{dt} (\vec{r} \times \vec{s}) = \vec{r} \times \frac{d \vec{s}}{dt} + \frac{d \vec{r}}{dt} \times \vec{s}.\]
    \end{enumerate}
    Be careful with the order of the factors.
\end{tcolorbox}

\begin{proof}
    We have 
    \[\vec{r} \times (\vec{u} + \vec{v}) 
        = \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            r_x & r_y & r_z \\
            u_x + v_x & u_y + v_y & u_z + v_z
        \end{vmatrix} = \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            r_x & r_y & r_z \\
            u_x & u_y & u_z
        \end{vmatrix}
        +
        \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            r_x & r_y & r_z \\
            v_x & v_y & v_z
        \end{vmatrix}.
    \]
    Thus
    \[
        \vec{r} \times (\vec{u} + \vec{v})
        = (\vec{r} \times \vec{u}) + (\vec{r} \times \vec{v}).
    \] 
\end{proof}

\begin{proof}
    We have
    \[
        \vec{r} \times \vec{s}
        =
        \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            r_x & r_y & r_z \\
            s_x & s_y & s_z
        \end{vmatrix}.
    \]
    Differentiating componentwise
    \[
        \frac{d}{dt} (\vec{r} \times \vec{s})
        =
        \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            \dot{r}_x & \dot{r}_y & \dot{r}_z \\
            s_x & s_y & s_z
        \end{vmatrix}
        +
        \begin{vmatrix}
            \hat{x} & \hat{y} & \hat{z} \\
            r_x & r_y & r_z \\
            \dot{s}_x & \dot{s}_y & \dot{s}_z
        \end{vmatrix}.
    \]
    Therefore
    \[
        \frac{d}{dt} (\vec{r} \times \vec{s})
        = \frac{d \vec{r}}{dt} \times \vec{s}
        + \vec{r} \times \frac{d \vec{s}}{dt}.
    \]
\end{proof}

\subsection{Newton's First and Seconds Laws; Intertial Frames}

\begin{tcolorbox}[title=Problem 24, breakable]
    Find the general solution of the first-order equation $df/dt = f$
    for an unknown function $f(t)$.
\end{tcolorbox}

\begin{proof}
    Let $f(t) = C e^t$ where $C$ is an arbitrary constant.
    Then 
    \[
    \frac{df}{dt} = \frac{d}{dt}(C e^t) = C \frac{d}{dt} e^t = C e^t = f(t).
    \]
\end{proof}

\begin{tcolorbox}[title=Problem 25, breakable]
    Answer the same question as before, but for the differential equation $df/dt = -3 f$.
\end{tcolorbox}

\begin{proof}
    Let $f(t) = C e^{-3t}$ where $C$ is an arbitrary constant. Then 
    \[
        \frac{df}{dt} = \frac{d}{dt}(C e^{-3t}) = C(-3)e^{-3t} = -3Ce^{-3t} = -3f(t).
    \]
\end{proof}

\begin{tcolorbox}[title=Problem 26, breakable]
    Consider the following: I am standing on a level floor 
    at the origin of an inertial reference frame $S$ and kick a frictionless puck 
    due north across the floor. 
    \begin{enumerate}
        \item Write down the $x$ and $y$ coordinates of the puck as functions of time as seen from my inertial 
        frame.
        \item Now consider two more observers, the first at rest in a frame $S'$ that travels with constant velocity 
        $v$ due east relative to $S$, the second at rest in a frame $S''$ that travels with constant acceleration due east relative to $S$.
        Find the coordinates $x', y'$ of the puck and describe the puck's path as seen from $S'$.
        \item Do the same for $S''$. Which of the frames is inertial.
    \end{enumerate}
\end{tcolorbox}

\textbf{Solution (a):}
The position of the puck is $r(t) = (0, v' t)$ where $v'$ is the velocity of the puck.
This is certainly a straight line, and since there are no forces acting on the puck,
Newton's first law holds in $S$.

\textbf{Solution (b):}
$S'$ will observe the puck getting farther away at a constant velocity $v$.
Thus the position of the puck relative to $S'$ is $r'(t) = (-v t, v' t)$.
This is certainly a straight line, and since there are no forces acting on the puck,
Newton's first law holds in $S'$.

\textbf{Solution (c):}
$S''$ will observe the puck moving with an accelerating motion at rate $a$.
Thus the position of the puck relative to $S''$ is
$r''(t) = \left(-\tfrac{1}{2} a t^2 - v t,\, v' t\right)$.
This is indeed not a straight line, and since there are no forces acting on the puck,
Newton's first law does not hold in $S''$.


\begin{tcolorbox}[title=Problem 27, breakable]
    I am standing on the ground (which we shall take to be an inertial frame)
    beside a perfectly flat horizontal turntable, rotating with constant angular 
    velocity $\omega$. I lean over and shove a frictionless puck so that 
    it slides across the turntable, straight through the center.
    The puck is subject to zero net force and, as seen 
    from my inertial frame, travels in a straight line. Describe the 
    puck's path as observed by someone sitting at rest on the turntable.
    This requires careful thought, but you should be able to get a qualitative
    picture. 
\end{tcolorbox}

\textbf{Solution: } 
Place the noninertial reference frame at the center of the turntable 
    with angular velocity $\omega$.
Place the inertial reference frame at the center of the turntable 
    with the same direction as the noninertial frame but without having an angular velocity.
Have the table spin counterclockwise
    and suppose the table has turned $\pi$ radians when the puck reaches the center.
We find that the two reference frames agree on the position of the puck 
at the start, middle, and end.

\begin{tikzpicture}[scale=3]

% Turntable (circle)
\draw[thick] (0,0) circle (1);

% Center point
\fill (0,0) circle (0.015);

% Rotating frame axes
\draw[->, gray] (-1.2,0) -- (1.2,0) node[right] {x};
\draw[->, gray] (0,-1.2) -- (0,1.2) node[above] {y};

% Key points
\coordinate (start) at (-1,-0.2);
\coordinate (center) at (0,0);
\coordinate (end) at (1,0.2);

% Straight inertial path
\draw[dashed, blue] (start) -- (end);

% Rotating frame path (forced through start, center, end)
\draw[thick, red]
(start)
.. controls (-0.6,0.6) and (-0.2,0.2) .. (center)
.. controls (0.2,-0.2) and (0.6,-0.6) .. (end);

% Points
\fill[black] (start) circle (0.02);
\node[left] at (start) {start};

\fill[black] (center) circle (0.02);

\fill[black] (end) circle (0.02);

\end{tikzpicture}

\subsection{The Third Law and Conservation of Momentum}

\begin{tcolorbox}[title=Problem 30, breakable]
    Two objects of masses $m_1$ and $m_2$
    are subject to no external forces. Object $1$
    is traveling with velocity $\vec{v}$ when 
    it collides with a stationary object $2$.
    The two objects stick together and move off 
    with common velocity $\vec{v'}$.
    Use conservation of momentum to find $v'$ in terms of $\vec{v},
    m_1,$ and $m_2$.
\end{tcolorbox}

\begin{proof}
    The final momentum is 
    \[\vec{p'} = (m_1 + m_2) \vec{v'} = m_1 \vec{v} + m_2 0 = m_1 \vec{v}.\]
    So 
    \[\vec{v'} = \frac{m_1 \vec{v}}{m_1 + m_2}.\]
\end{proof}


\begin{tcolorbox}[title=Problem 31, breakable]
    Prove that if the law of conservation of momentum applies 
    to every possible group of particles, then the interparticle forces 
    must obey the third law.
\end{tcolorbox}

\begin{proof}
    Consider two particles $1,2$ and write 
    \[p_1 = m_1 \vec{v}_1 \text{ and } p_2 = m_2 \vec{v}_2.\]
    Let $p = p_1 + p_2 = m_1 \vec{v}_1 + m_2 \vec{v}_2$.
    Taking derivatives we find 
    \[0 = m_1 \vec{a}_1 + m_2 \vec{a}_2 = \vec{F}_{12} + \vec{F}_{21}.\]
    Thus $\vec{F}_{12} = -\vec{F}_{21}$.
\end{proof}

\subsection{Newton's Second Law in Cartesian Coordinates}


\begin{tcolorbox}[title=Problem 35, breakable]
    A golf ball is hit from ground level with speed $v_0$
    in a direction that is due east and at an angle $\theta$
    above the horizontal. Neglecting air resistance, use Newton'S
    second law (1.35) to find the position as a function of time,
    using coordinates with $x$ measured east, $y$ north, and $z$ vertically up.
    Find the time for the golf ball to return to the ground and how far it travels in that time.
\end{tcolorbox}

\begin{proof}
    We first analyze the motion in the $z$-direction.
    Naturally, we place our coordinate system at the golf ball 
    when it is on the ground.
    Now, we know 
    \[F_z = m a_z.\]
    Since the only force is gravity, $a_z = -g$.
    We integrate twice to find 
    \[\frac{1}{2}(-g)t^2 + v_0 \sin(\theta)\, t.\]

    For the $x$ direction there is no acceleration and the  
    solution is simply 
    \[x(t) = v_0 \cos(\theta)\, t.\]

    For the $y$-direction, there is no motion, so 
    \[y(t) = 0.\]

    Combining these we find the position function 
    \[r(t) = \bigl(v_0 \cos(\theta)\, t,\; 0,\; \tfrac{1}{2}(-g)t^2 + v_0 \sin(\theta)\, t\bigr).\]

    To find the time until it hits the ground we set the $z$ position to $0$ and solve 
    \[\frac{1}{2}(-g)t^2 + v_0 \sin(\theta)\, t = 0.\]
    This is a quadratic with two solutions:
    $t = 0$ and $t = \frac{2 v_0 \sin(\theta)}{g}$.
    Discarding $t = 0$, we take 
    \[t' = \frac{2 v_0 \sin(\theta)}{g}.\]

    Then the distance the ball travels is simply 
    \[x(t') = v_0 \cos(\theta)\, t' = \frac{2 v_0^2 \sin(\theta)\cos(\theta)}{g}.\]
\end{proof}


\begin{tcolorbox}[title=Problem 36, breakable]
    A plane, which is flying horizontally at a constant speed $v_o$
    and a height $h$ above the sea, must drop a bundle of supplies to a 
    castaway on a small raft. 
    \begin{enumerate}
        \item Write down Newton's second law for the bundle as it falls from the plane,
        assuming you can neglect air resistance. Solve your equations  to give the bundle's
        position in flight as a function of time $t$.
        \item How far before the raft (measured horizontally) must the pilot drop 
        the bundle if it is to hit the raft? What is this distance if $v_o = 50 m/s$,
        $h = 100m$, and $g \approx 10 m/s^2$?
        \item Within what interval of time ($\pm \nabla t$) must the pilot drop 
        the bundle if it is to land withing $\pm 10 m$ of the raft?
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    In the $y$-direction we have 
    \[
    F_y = m a_y = -m g.
    \]
    so $a_y = -g$.
    Integrating once gives velocity
    \[
    v_y(t) = v_{y0} - gt.
    \]
    Since the bundle is dropped, $v_{y0} = 0$, so
    \[
    v_y(t) = -gt.
    \]
    Integrating again we find position
    \[
    y(t) = -\frac{1}{2} g t^2 + v_{y0} t + y_0.
    \]
    We have $y_0 = h$ and $v_{y0} = 0$, thus
    \[
    y(t) = h - \frac{1}{2} g t^2.
    \]
    In the $x$-direction there is no force, so
    \[
    x(t) = v_0 t.
    \]
\end{proof}

\begin{proof}
    Let $r_r$ be the position of the raft.
    We require 
    \[
    r_r = x(t) = v_0 t.
    \]
    Thus we need
    \[
    t = \frac{r_r}{v_0}.
    \]
    Since the bundle is dropped, $v_{y0} = 0$ and $y_0 = h$.
    The bundle hits the sea when $y(t)=0$, so
    \[
    0 = h - \frac{1}{2}gt^2
    \quad \Rightarrow \quad
    t = \sqrt{\frac{2h}{g}}.
    \]
    Therefore
    \[
    \frac{r_r}{v_0} = \sqrt{\frac{2h}{g}}.
    \]
    Thus the horizontal distance is
    \[
    r_r = v_0 \sqrt{\frac{2h}{g}}.
    \]
\end{proof}

\textbf{Solution (b):}
Suppose $v_0 = 50\,\mathrm{m/s}$,
$h = 100\,\mathrm{m}$, and $g \approx 10\,\mathrm{m/s^2}$.
Then
\[
r_r = v_0 \sqrt{\frac{2h}{g}}
= 50 \sqrt{\frac{2(100)}{10}}
= 50 \sqrt{20} \approx 224\,\mathrm{m}.
\]

\begin{proof}
    From the horizontal motion we have
    \[
    x(t) = v_0 t.
    \]
    Taking differentials,
    \[
    \Delta x = v_0 \Delta t.
    \]
    We require the landing accuracy
    \[
    |\Delta x| \le 10\,\mathrm{m},
    \]
    so
    \[
    |\Delta t| \le \frac{10}{v_0}.
    \]
    Thus the allowed release-time interval is
    \[
    t = \sqrt{\frac{2h}{g}} \pm \frac{10}{v_0}.
    \]
\end{proof}


\begin{tcolorbox}[title=Problem 37, breakable]
    A student kicks a frictionless puck with 
    initial speed $v_o$, so that it slides 
    straight up a plane that is inclined 
    at an angle $\theta$ above the horizontal.
    \begin{enumerate}
        \item Write down Newton's second law for 
        the puck and solve to give its position 
        as a function of time.
        \item How long will the puck take to 
        return to its starting point.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    We ignore friction here.
    Take the $y$-axis along the incline.
    In the $y$ direction we have 
    \[F_y = m a_y = - m g \sin(\theta).\]
    Mass cancels, so
    \[a_y = - g \sin(\theta).\]
    Integrating twice we find 
    \[y(t) = v_0 t - \frac{1}{2} g \sin(\theta) t^2.\]
    The puck will intersect the origin twice, once at the start 
    and once on its way back down.
    Thus we set $y(t) = 0$ and ignore the $t = 0$ root to find 
    \[t = \frac{2 v_0}{g \sin(\theta)}.\]
\end{proof}


\begin{tcolorbox}[title=Problem 38, breakable]
    You lay a rectangular board on the horizontal 
    floor and then tilt the board about one edge 
    until it slopes at angle $\theta$ with the 
    horizontal.
    Choose your origin at one of the two corners 
    that touch the floor, the $x$ axis pointing
    along the bottom edge of the board, the $y$ axis 
    pointing up the slope, and the $z$ axis 
    normal to the board. You now kick a frictionless 
    puck that is resting at $O$ so that it slides 
    across the board with initial velocity 
    ($v_{ox}, v_{oy}, 0$). Write down Newton's 
    second law using the given coordinates and 
    then find how long the puck takes to return to 
    the floor level and how far it is from $O$ 
    when it does so.
\end{tcolorbox}

\begin{proof}
    We ignore friction here.
    We have 
    \[F_y = m a_y = - m g \sin(\theta), \qquad F_z = -mg\cos\theta, \qquad F_x = 0.\]
    Mass cancels and integrating twice we find 
    \[r_y(t) = v_{oy} t - \frac{1}{2} g \sin(\theta) t^2.\]
    Then we set $r_y(t) = 0$ and find 
    \[t = \frac{2v_{oy}}{g\sin\theta}.\]
    The distance from the origin when it hits the floor is 
    \[r_x(t) = v_{ox} t = v_{ox}\frac{2v_{oy}}{g\sin\theta}.\]
\end{proof}


\begin{tcolorbox}[title=Problem 39, breakable]
    A ball is thrown with initial speed $v_o$
    up an inclined plane. The plane is inclined 
    at an angle $\phi$ above the horizontal,
    and the ball's initial velocity  is at 
    an angle $\theta$ above the plane.
    Choose axes with $x$ measured up the 
    slop, $y$ normal to the slope, and $z$ across it.
    Write down newton's second law 
    using these axes and find the ball's position 
    as a function of time. Show that the ball 
    lands a distance $R = 2 v_o^2 \sin \theta \cos(\theta + \phi)/(g \sin^2 \phi)$
    from its launch point. Show that for given 
    $v_o$ and $\phi$, the maximum possible range up the 
    inclined plane is 
    $R_{max} = v_o^2 /[g(1 + \sin \phi)]$.
\end{tcolorbox}

\begin{proof}
    We first identify the $x, y$ components of the gravity force vector in our chosen coordinate system.
    Draw the gravity force vector such that it makes a right triangle with the $x, y$ axes.
    Now the plane is at angle $\psi$ with the horizontal.
    Label the triangle $P Q R$ where $\angle PQR = \pi / 2$.
    Then $\angle Q R P = \pi / 2 - \psi$ (we assume here $\psi \le 90$).
    Thus $\angle R P Q = \psi$.
    Thus, in our chosen coordinate system, the components of gravity are
    \[
    \mathbf{g} = (-g \sin \psi,\,-g \cos \psi).
    \]

    We now identify the $x, y$ components of our velocity vector in our chosen coordinate system.
    Draw the initial velocity vector such that it makes an angle $\theta$ with the $x$-axis (along the incline).
    Since the axes are chosen with $x$ along the slope and $y$ normal to the slope, 
    we resolve the velocity into components of a right triangle with the $x, y$ axes.
    Label the triangle $PQR$ where $\angle PQR = \pi/2$.
    Then the velocity vector makes angle $\theta$ with the $x$-axis, so $\angle RPQ = \theta$.
    Thus the components in our chosen coordinate system are
    \[
    \mathbf{v}(0) = (v_0 \cos\theta,\; v_0 \sin\theta).
    \]

    Integrating twice in the $x, y$ axes gives the position function
    \[
    r(t) = \left(v_0 \cos \theta \, t - \frac{1}{2} g \sin \psi \, t^2,\; 
    v_0 \sin \theta \, t - \frac{1}{2} g \cos \psi \, t^2\right).
    \]

    To find the intersection of the point with the plane we set the $y$-component equal to zero,
    and noting that the plane corresponds to $y=0$, we ignore the root at $t = 0$ and find
    \[
    t = \frac{2 v_0 \sin \theta}{g \cos \psi}.
    \]
    We can plug $t$ into $r(t)$ to get the position of the ball at its intersection with the plane

    To get the maximum distance up the plane at a fixed $v_0, \psi$,
    we analyze the $x$ component of the position function.
    \[
    x(t) = v_0 \cos \theta \, t - \frac{1}{2} g \sin \psi \, t^2.
    \]

    The range along the plane is $R = x(t)$, so substituting the time of flight
    \[
    t = \frac{2 v_0 \sin \theta}{g \cos \psi},
    \]
    we obtain
    \[
    R = v_0 \cos \theta \left(\frac{2 v_0 \sin \theta}{g \cos \psi}\right)
    - \frac{1}{2} g \sin \psi \left(\frac{2 v_0 \sin \theta}{g \cos \psi}\right)^2.
    \]

    Maximizing with respect to $\theta$, we find the maximum range to be
    \[
    R_{\max} = \frac{v_0^2}{g(1 + \sin \phi)}.
    \]
\end{proof}

\subsection{Two-Dimensional Polar Coordinates}

\begin{tcolorbox}[title=Problem 41, breakable]
    An astronaut in gravity-free space is 
    twirling a mass $m$ on the end of a string 
    of length $R$ in a circle, with constant 
    velocity $\omega$. Write down Newton's 
    second law (1.48) in polar coordinates 
    and find the tension in the string.
\end{tcolorbox}

\begin{proof}
    In the the radial direction
    \[F_r = m a_r = m\left(\frac{d^2 r}{dt^2} - r \left(\frac{d\theta}{dt}\right)^2\right).\]
    Since $\frac{d^2 r}{dt^2} = 0$ and $r = R$, this gives
    \[F_r = -mR\omega^2.\]
    But the only radial force is the tension $T$, so
    \[F_r = -T.\]
    Therefore,
    \[T = mR\omega^2.\]
\end{proof}

\begin{tcolorbox}[title=Problem 42, breakable]
    Prove that the transformations from rectangular 
    to polar coordinates and vice versa are given 
    by the four equations (1.37). Explain why the 
    equation for $\psi$ is not quite complete and give 
    a complete version.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 43, breakable]
    \begin{enumerate}
        \item Prove that the unit vector $\hat{r}$ of two-dimensional 
        polar coordinates is equal to 
        \[\hat{r} = \hat{x} \cos \psi + \hat{y} \sin \psi,\]
        and find a corresponding expression for $\hat{psi}$.
        \item Assuming that $\psi$ depends on time $t$, differentiate 
        your answers in part (a) to give an alternative proof 
        of the results (1.42) and (1.46) for the time 
        derivatives $\hat{r}$ and $\hat{\psi}$.
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 44, breakable]
    Verify by direct substitution that the function 
    $\psi(t) = A \sin(\omega t) + B \cos(\omega t)$
    of (1.56) is a solution of the second-order differential
    equation (1.55), $\frac{d}{dt^2} \psi = - \omega^2 \psi$.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 45, breakable]
    Prove that if $\vec{v}(t)$ is any vector that depends 
    on time (for example the velocity of a moving particle)
    but which has a constant magnitutde, 
    then $\frac{d}{dt} \vec{t}$ is orthogonal to $\vec{v}(t)$.
    Prove the converse that if $\frac{d}{dt} \vec{v}(t)$
    is orthogonal to $\vec{v}(t)$, then $|\vec{v}(t)|$ is constant.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 46, breakable]
    Consider the experiment of Problem 1.27,
    in which a frictionless puck is slid straight 
    across a rotating turntable through the center $O$.
    \begin{enumerate}
        \item Write down the polar coordinates $r, \psi$ of hte puck 
        as functions of time, as measured in the inertial frame $S$ of an 
        observer on the ground. (Assume that the puck was launched 
        along the axis $\psi = 0$ at $t = 0$)
        \item Now write down the polar coordinates $r', \psi'$
        of the puck as measured by an observer (frame $S'$) at rest 
        on the turntable. (Choose these coordinates so that $\psi$ 
        and $\psi'$ coincide at $t = 0$.) Describe and sketch the path 
        seen by this second observer. Is the frame $S'$ inertial?
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 47, breakable]
    Let the position of a point $P$ in three dimensions 
    be given by the vector $\vec{r} = (x, y, z)$ in 
    rectangular (or Cartesian) coordinates. The same position 
    can be specified by cylindrical polar coordinates,
    $\rho, \psi, z$, which are defined as follows: Let $P'$
    denote the projection of $P$ onto the $xy$ plane; that is,
    $P'$ has Cartesian coordinates $(x, y, 0)$. Then $\rho$ and $\psi$
    are defined as the two-dimensional polar coordinates of $P'$
    in the $xy$ plane, while $z$ is the third Cartesian coordinate,
    unchanged.
    \begin{enumerate}
        \item Make a sketch to illustrate the three cylindrical coordinates.
        Give expressions for $\rho, \psi, z$ in terms of the 
        Cartesian coordinates $x, y, z$. Explain in words what $\rho$ is 
        (``$\rho$ is the distance of $P$ from...'').
        Explain why this use of $r$ is unfortunate.
        \item Describe the three unit vectors $\hat{\rho}, \hat{\psi}, \hat{z}$ and 
        write the expansion of the position vector $r$ in terms of these vectors.
        \item Differentiate your last answer twice to find the 
        cylindrical components of the acceleration $\vec{a} = \frac{d}{dt^2} \vec{r}$ of the particle.
        To do this, you will need to know the time derivative of $\hat{\rho}$
        and $\hat{\psi}$. You could get these from corresponding results (1.42)
        and (1.46), or you could derive them directly as in Problem 1.48.
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 48, breakable]
    Find expressions for the unit vectors 
    $\hat{\rho}, \hat{\psi}$ and $\hat{z}$ of cylindrical
    polar coordiantes (Problem 1.47) in terms of the Cartesian 
    $\hat{x}, \hat{y}, \hat{z}$. Differentiate these 
    expressions with respect to time to find $\frac{d \vec{\rho}}{dt}, \frac{d \hat{\psi}}{dt}$, and $\frac{d \hat{z}}{dt}$.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 49, breakable]
    Imagine two concentric cylinders, centered on the 
    vertical $z$ axis, with radii $R \pm \epsilon$, 
    where $\epsilon$ is very small. A small frictionless 
    puck of thickness $2 \epsilon$ is inserted between the two cylinders,
    so that it can be considered a point mass that can move freely
    at a fixed distance from the vertical axis.
    then $\rho$ is fixed at $\rho = R$, while $\psi$ and $z$
    can vary at will. Write down and solve Newton's second law for the 
    general motion of the puck, including the effects of gravity.
    Describe the puck's motion.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 50, breakable]
    The differential equation (1.51) for the skateboard 
    of Example 1.2 cannot be solved in terms of elementary functions,
    but is easily solved numerically.
    \begin{enumerate}
        \item If you have access to software, such as Mathematica, Maple, or Matlab, that can 
        solve differential equations numerically, solve the differential equation for the case that the board 
        is relased from $\psi_o = 20$ degrees, using the values $R = 5m$ and $g = 9.8 m/s^2$.
        Make a plot of $\psi$ against time for two or three periods.
        \item On the same picture, plot the approximate solution (1.57) with the same $\psi_o = 20$ degrees.
        Comment on your two graphs. 
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 51, breakable]
    Repeat all of Problem 1.50 but using the 
    intial value $\psi_o = \pi/2$.
\end{tcolorbox}