\subsection{Definition of a Function}

\begin{tcolorbox}[title=Problem 2, breakable]
    For what numbers could you define a function $f$
    by the formula
    \[f(x) = \frac{1}{x^2 - 2}\]
    What is the value of the function for $x = 5$.
\end{tcolorbox}

\textbf{Solution:}
$f$ is defined at all real numbers other than $\pm \sqrt{2}$.
\[f(5) = \frac{1}{5^2 - 2} = \frac{1}{23}\]

\begin{tcolorbox}[title=Problem 8, breakable]
    A function (defined for all numbers) is said to be 
    an \textbf{even} function if
    $f(x) = f(-x)$ for all numbers $x$. It is said to be 
    an \textbf{odd} function if $f(x) = -(f(-x))$ for all $x$.
    Determine which of the following functions are even or odd.

    (a) $f(x) = x$

    (b) $f(x) = x^2$

    (c) $f(x) = x^3$

    (d) $f(x) = \frac{1}{x} \text{ if } x \ne 0 \text{ and } f(0)=0$
\end{tcolorbox}

\textbf{Solution (a):} odd

\textbf{Solution (b):} even

\textbf{Solution (c):} odd

\textbf{Solution (d):} odd

\begin{tcolorbox}[title=Problem 9, breakable]
    Show that any function defined for all numbers 
    can be written as a sum of an even and an odd function.
    [Hint: The term 
    \[\frac{f(x) + f(-x)}{2}\]
    will be an even function.]
\end{tcolorbox}

\begin{proof}
    Let any function $f$ be defined for all numbers.
    \[
    g(x) = \frac{f(x) + f(-x)}{2}, \quad
    l(x) = \frac{f(x) - f(-x)}{2}.
    \]
    Then $g$ is even and $l$ is odd, and
    \[
    f(x) = g(x) + l(x).
    \]
\end{proof}

\begin{tcolorbox}[title=Problem 11, breakable]
    (a) Show that the sum of odd functions is odd.

    (b) Show that the sum of even functions is even.
\end{tcolorbox}

\begin{proof}
    Let $f, g$ be odd functions. Then
    \[
    (f + g)(x) = f(x) + g(x) = -f(-x) - g(-x) = -(f(-x) + g(-x)) = -(f + g)(-x),
    \]
    so the sum is odd.
    Let $f, g$ be even functions. Then
    \[
    (f + g)(x) = f(x) + g(x) = f(-x) + g(-x) = (f + g)(-x),
    \]
    so the sum is even.
\end{proof}

\begin{tcolorbox}[title=Problem 12, breakable]
    Determine whether the product of the following types of functions 
    is odd, even, or neither. Prove your assertions.

    (a) Product of odd function with odd function 

    (b) Product of even function with odd function 

    (c) Product of even function with even function
\end{tcolorbox}

\begin{proof} 
    If $f$ and $g$ are odd:
    \[
    (fg)(-x) = f(-x)g(-x) = (-f(x))(-g(x)) = f(x)g(x) = (fg)(x)
    \]
    The product is even.
    
    If $f$ is even and $g$ is odd:
    \[
    (fg)(-x) = f(-x)g(-x) = f(x)(-g(x)) = -f(x)g(x) = -(fg)(x)
    \]
    The product is odd.

    If $f$ and $g$ are even:
    \[
    (fg)(-x) = f(-x)g(-x) = f(x)g(x) = (fg)(x)
    \]
    The product is even.
\end{proof}

\subsection{Polynomial Functions}

\begin{tcolorbox}[title=Problem 1, breakable]
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 3, breakable]
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 4, breakable]
\end{tcolorbox}

\subsection{Graphs of Functions}

\begin{tcolorbox}[title=Problem 1, breakable]
\end{tcolorbox}

\subsection{Exponential Function}

\begin{tcolorbox}[title=Problem 7, breakable]
\end{tcolorbox}

\subsection{Logarithms}

\begin{tcolorbox}[title=Problem 3, breakable]
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 6, breakable]
\end{tcolorbox}