\subsection{Introduction}

\begin{tcolorbox}[title=Problem 4, breakable]
    Let $x_1, x_2, x_3, \ldots$  be an infinite collection of independent
    variables indexed by the natural numbers. A  polynomial with coefficients 
    in a field $k$ in the $x_i$  is a finite linear combination of (finite)
    monomials $x_{i_1}^{e_1} \ldots x_{i_n}^{e_n}$. Let $R$ detote the set of all 
    polynomials in $x_i$. Note that we an add and multiply elements of $R$ in the usual 
    way. Thus, $R$ is the polynomial ring, $k[x_1, x_2, \ldots]$ in infinitely many variables.
    \begin{enumerate}
        \item Let $I = \langle x_1, x_2, \ldots \rangle$ be the set of $f = \sum_{i = 1}^{\infty} A_i x_i$,
        where $A_i = 0$ for all $i$ sufficiently large. Show that $I$ is an ideal in the ring $R$.
        \item Show, arguing by contradiction, that $I$ has no finite generating set. Hint: note that 
        if $I = \langle g_1, \ldots, g_m \rangle$, then there must be some variable $x_l$ that is not contained
        in any of the $g_j$.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Let $p \in k[x_1, x_2, \ldots]$.
    Let $f, g \in I$ with $j, j'$ being sufficiently large such that $A_j = 0$ and $A_{j'} = 0$.
    Then $f + g = \sum_{i = 1}^{\infty} A_i x_i + \sum_{i = 1}^{\infty} B_i x_i = \sum_{i = 1}^{\infty} (A_i + B_i) x_i \in I$.
    Also, $p \cdot f = p \cdot \sum_{i = 1}^{\infty} A_i x_i \in I$ because it is a finite sum of monomials in the $x_i$.
    Thus $I$ is an ideal.
\end{proof}

\begin{proof}
    Suppose, for contradiction, that $I$ has a finite generating set $\langle g_1, \ldots, g_m \rangle$
        for some $m \in \mathbb{N}$.
    Then there exists some variable $x_l$ that does not appear in any of the $g_j$.
    Clearly, $x_l$ cannot be expressed as a linear combination of the other generators.
    Thus $x_l$ is not in the ideal generated by $g_1, \ldots, g_m$, contradicting that they generate $I$.
\end{proof}


\begin{tcolorbox}[title=Problem 5, breakable]
    In this problem you will show that all polynomial parametric curves in $k^2$ are contained
    in affine varieties.
    \begin{enumerate}
        \item Show that the number of distinct monomials $x^a y^b$ of total degree $\le m$
        in $k[x, y]$ is equal to $(m + 1)(m + 2) / 2$. [Note: This is the binomial coefficients 
        $\binom{m + 2}{2}$.]
        \item Show that if $f(t)$ and $g(t)$ are polynomials of degree $\le n$ in $t$, then for $m$ large enough,
        the ``monomials''
        \[[f(t)]^a [g(t)]^b,\]
        with $a + b \le m$ are linearly \emph{dependent}.
        \item Deduce form part (b) that if $C$ is a curve in $k^2$ given parametrically by $x = f(t), y = g(t)$
        for $f(t), g(t) \in k[t],$ then $C$ is contained in $\textbf{V}(F)$ for some nonzero $F \in k[x, y]$
        \item Generalize parts (a), (b), and (c) to show that any polynomial parametric surface 
        \[x = f(t, u), \quad y = g(t, u), \quad z = h(t, u),\]
        is contained in an algebraic surface $\textbf{V}(f)$, where $F \in k[x, y, z]$ is nonzero.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}[Part 1]
    The number of monomials $x^a y^b$ of total degree $\le m$ is the number of $(a,b)$ such that $a+b \le m$.
    For each $a = 0, 1, \dots, m$, $b$ can range from $0$ to $m-a$, giving $m-a+1$ choices.
    Thus
    \[
    \sum_{a=0}^{m} (m-a+1) = \sum_{a=0}^{m} (m+1) - \sum_{a=0}^{m} a = (m+1)(m+1) - \frac{m(m+1)}{2} = \frac{(m+1)(m+2)}{2}.
    \]
\end{proof}

\begin{proof}[Part 2]
    Suppose $f(t)$ and $g(t)$ are polynomials of degree $\le n$ in $t$.
    Then $\deg(f(t)^a) \le an$ and $\deg(g(t)^b) \le bn$, so
    \[
    \deg([f(t)]^a [g(t)]^b) = \deg(f(t)^a) + \deg(g(t)^b) \le an + bn = n(a+b) \le nm.
    \]
    There are $\frac{(m+1)(m+2)}{2}$ such polynomials. 
    For $m$ large enough, 
    \[
    \frac{(m+1)(m+2)}{2} > nm+1,
    \]
    so these polynomials are linearly dependent.
\end{proof}

\begin{proof}[Part 3]
    By part 2, for sufficiently large $m$ there is some linear combination
    \[
    a_1 x^0 y^0 + a_2 x^1 y^0 + a_3 x^0 y^1 + \cdots = 0,
    \]
    with at least one $a_i \ne 0$.
    Then taking $x = f(t)$ and $y = g(t)$, gives
    \[
    a_1 [f(t)]^0 [g(t)]^0 + a_2 [f(t)]^1 [g(t)]^0 + a_3 [f(t)]^0 [g(t)]^1 + \cdots = 0
    \]
    for all $t$. Let
    \[
    F(x,y) = a_1 x^0 y^0 + a_2 x^1 y^0 + a_3 x^0 y^1 + \cdots \in k[x,y].
    \]
    Then $F(f(t),g(t)) = 0$ for all $t$ thus $C \subset \textbf{V}(F)$.
\end{proof}

\begin{proof}[Part 4]
    Consider all monomials
    \[
    [f(t,u)]^a [g(t,u)]^b [h(t,u)]^c
    \]
    of total degree $\le m$.
    For $m$ large enough,
    the number of such monomials exceeds the dimension of the vector space of polynomials in $t,u$ of that degree. 
    Thus there exists a linear combination
    \[
    F(x,y,z) = \sum a_{a,b,c} x^a y^b z^c \in k[x,y,z]
    \]
    that vanishes when evaluated on the surface
    \[
    F(f(t,u), g(t,u), h(t,u)) = 0.
    \]
    Therefore, the surface is contained in $\textbf{V}(F)$.
\end{proof}

\subsection{Orderings on the Monomials in $k[x_1, \ldots, x_n]$}


\begin{tcolorbox}[title=Problem 1, breakable]
    Rewrite each of the following polynomials,
    ordering the terms using lex order,
    grlex order, and grevlex order,
    giving $LM(f), LT(f)$, and $multideg(f)$
    in each case.
    \begin{enumerate}
        \item $f_1(x, y, z) = 2x + 3y + z + x^2 - z^2 + x^3$.
        \item $f_2(x, y, z) = 2x^2 y^8 - 3x^5 y z^4 + x y z^3 - x y^4$.
    \end{enumerate}
\end{tcolorbox}

\textbf{Solution (lex order): }
For $f_1$, we have the following exponent vectors 
\[(1, 0, 0),\ (0, 1, 0),\ (0, 0, 1),\ (2, 0, 0),\ (0, 0, 2),\ (3, 0, 0).\]
Reordering in lex order ($x > y > z$) gives 
\[
x^3 + x^2 + 2x + 3y - z^2 + z.
\]
So
\[
LM(f_1) = x^3, \quad LT(f_1) = x^3, \quad multideg(f_1) = (3,0,0).
\]
For $f_2$, the exponent vectors are
\[(2, 8, 0),\ (5, 1, 4),\ (1, 1, 3),\ (1, 4, 0).\]
Reordering in lex order gives
\[
-3x^5 y z^4 + 2x^2 y^8 - x y^4 + x y z^3.
\]
So:
\[
LM(f_2) = x^5 y z^4, \quad LT(f_2) = -3x^5 y z^4, \quad multideg(f_2) = (5,1,4).
\]
\textbf{Solution (grlex order): }
For $f_1$, compute total degrees
\[
|2x| = 1,\ |3y| = 1,\ |z| = 1,\ |x^2| = 2,\ |-z^2| = 2,\ |x^3| = 3.
\]
Sort by total degree, breaking ties with lex order
\[
x^3 - x^2 - z^2 + 2x + 3y + z
\]
\[
LM(f_1) = x^3, \quad LT(f_1) = x^3, \quad multideg(f_1) = (3,0,0)
\]
For $f_2$, total degrees
\[
2x^2 y^8 = 10, \quad -3x^5 y z^4 = 10, \quad x y z^3 = 5, \quad -x y^4 = 5
\]
Sorting by total degree, then lex to break ties
\[
-3x^5 y z^4 + 2x^2 y^8 - x y^4 + x y z^3
\]
\[
LM(f_2) = x^5 y z^4, \quad LT(f_2) = -3x^5 y z^4, \quad multideg(f_2) = (5,1,4)
\]
\textbf{Solution (grevlex order): }
For $f_1$, total degrees as before: 1,1,1,2,2,3  
\[
x^3 + x^2 + 2x - z^2 + z + 3y
\]
\[
LM(f_1) = x^3, \quad LT(f_1) = x^3, \quad multideg(f_1) = (3,0,0)
\]
For $f_2$, total degrees as before: 10,10,5,5  
\[
 - 3x^5 y z^4 + 2x^2 y^8 + x y z^3 - x y^4
\]
\[
LM(f_2) = x^2 y^8, \quad LT(f_2) = 2x^2 y^8, \quad multideg(f_2) = (2,8,0)
\]


\begin{tcolorbox}[title=Problem 4, breakable]
    Show that grlex is a monomial order according to Definition 1.
\end{tcolorbox}

\begin{proof}
    We will first show that $>_{grlex}$ is a total order.
    This requires that we show $>_{grlex}$ is reflexive, antisymmetric, transitive, and total.

    Let $\alpha, \beta, \gamma \in \mathbb{Z}_{\ge 0}^n$.

    (\textbf{reflexive})  
    Suppose $\alpha = \beta$.  
    By the definition of grlex, we have $|\alpha| = |\beta|$, and the lexicographic comparison gives $\alpha = \beta$.  
    Thus $\alpha \ge_{grlex} \alpha$.

    (\textbf{antisymmetric})  
    Suppose $\alpha \ge_{grlex} \beta$ and $\beta \ge_{grlex} \alpha$.  
    If $|\alpha| > |\beta|$, then we cannot have $|\beta| \ge |\alpha|$.  
    Similarly, if $|\beta| > |\alpha|$, we cannot have $|\alpha| \ge |\beta|$.  
    Thus $|\alpha| = |\beta|$.  
    Since the total degrees are equal, the comparison is lexicographic.  
    Because lexicographic order is antisymmetric, we must have $\alpha = \beta$.

    (\textbf{transitive})  
    Suppose $\alpha >_{grlex} \beta$ and $\beta >_{grlex} \gamma$.  
    There are four cases:
    \begin{enumerate}
        \item If $|\alpha| > |\beta|$ and $|\beta| > |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grlex} \gamma$.
        \item If $|\alpha| > |\beta|$ and $|\beta| = |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grlex} \gamma$.
        \item If $|\alpha| = |\beta|$ and $|\beta| > |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grlex} \gamma$.
        \item If $|\alpha| = |\beta|$ and $|\beta| = |\gamma|$, then  
        the comparison is lexicographic.  
        Since lexicographic order is transitive, we have  
        $\alpha >_{lex} \gamma$, thus $\alpha >_{grlex} \gamma$.
    \end{enumerate}
    Thus $>_{grlex}$ is transitive.

    (\textbf{total})  
    Let $\alpha, \beta \in \mathbb{Z}_{\ge 0}^n$.  
    If $|\alpha| > |\beta|$, then $\alpha >_{grlex} \beta$.  
    If $|\alpha| < |\beta|$, then $\beta >_{grlex} \alpha$.  
    If $|\alpha| = |\beta|$, then lexicographic order applies.  
    Since lexicographic order is total, either $\alpha \ge_{lex} \beta$ or $\beta \ge_{lex} \alpha$.  
    Thus either $\alpha \ge_{grlex} \beta$ or $\beta \ge_{grlex} \alpha$.

    If $|\alpha| > |\beta|$, then  
    \[
    |\alpha + \gamma| = |\alpha| + |\gamma| > |\beta| + |\gamma| = |\beta + \gamma|.
    \]
    Thus $\alpha + \gamma >_{grlex} \beta + \gamma$.
    If $|\alpha| = |\beta|$, then $\alpha >_{lex} \beta$.  
    Adding $\gamma$ adds the same amount to each coordinate of $\alpha$ and $\beta$,  
        so the first index where they differ remains the same and the inequality is preserved.  
    Thus $\alpha + \gamma >_{lex} \beta + \gamma$, and therefore  
    $\alpha + \gamma >_{grlex} \beta + \gamma$.

    Finally, we show $>_{grlex}$ is a well-ordering.  
    Let $S \subseteq \mathbb{Z}_{\ge 0}^n$ be nonempty.  
    The set $\{|\alpha| : \alpha \in S\} \subseteq \mathbb{Z}_{\ge 0}$ has a minimum since $\mathbb{Z}_{\ge 0}$ is well-ordered.  
    Restricting to elements of minimal total degree, lexicographic order gives a smallest element.  
    Thus every nonempty subset has a minimal element.

    Thus $>_{grlex}$ is a monomial ordering.
\end{proof}


\begin{tcolorbox}[title=Problem 5, breakable]
    Show that grevlex is a monomial order according to Definition 1.
\end{tcolorbox}

\begin{proof}
    We will first show that $>_{grevlex}$ is a total order.
    This requires that we show $>_{grevlex}$ is reflexive, antisymmetric, transitive, and total.

    Let $\alpha, \beta, \gamma \in \mathbb{Z}_{\ge 0}^n$.

    (\textbf{reflexive})  
    Suppose $\alpha = \beta$.  
    Then $|\alpha| = |\beta|$.  
    Since the total degrees are equal, we compare by subtracting 
    $\alpha - \beta = 0$.  
    There is no nonzero entry, thus $\alpha = \beta$.  
    Thus $\alpha \ge_{grevlex} \alpha$.

    (\textbf{antisymmetric})  
    Suppose $\alpha \ge_{grevlex} \beta$ and $\beta \ge_{grevlex} \alpha$.  
    If $|\alpha| > |\beta|$, then we cannot have $|\beta| \ge |\alpha|$.  
    Similarly, if $|\beta| > |\alpha|$, we cannot have $|\alpha| \ge |\beta|$.  
    Thus $|\alpha| = |\beta|$.  

    Since the total degrees are equal, we compare using the rightmost nonzero
    entry of $\alpha - \beta$.  
    If $\alpha \ne \beta$, then the rightmost nonzero entry of 
    $\alpha - \beta$ is either positive or negative.  
    If it is negative, then $\alpha >_{grevlex} \beta$.  
    If it is positive, then $\beta >_{grevlex} \alpha$.  
    Thus we must have $\alpha = \beta$.

    (\textbf{transitive})  
    Suppose $\alpha >_{grevlex} \beta$ and $\beta >_{grevlex} \gamma$.  
    There are four cases:
    \begin{enumerate}
        \item If $|\alpha| > |\beta|$ and $|\beta| > |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grevlex} \gamma$.

        \item If $|\alpha| > |\beta|$ and $|\beta| = |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grevlex} \gamma$.

        \item If $|\alpha| = |\beta|$ and $|\beta| > |\gamma|$, then  
        $|\alpha| > |\gamma|$, so $\alpha >_{grevlex} \gamma$.

        \item If $|\alpha| = |\beta|$ and $|\beta| = |\gamma|$, then  
        the comparison is determined by the rightmost nonzero entry of 
        $\alpha - \beta$ and $\beta - \gamma$.  
        Since subtraction and comparison of the rightmost nonzero entry 
        is transitive, it follows that the rightmost nonzero entry of 
        $\alpha - \gamma$ is negative.  
        Thus $\alpha >_{grevlex} \gamma$.
    \end{enumerate}
    Thus $>_{grevlex}$ is transitive.

    (\textbf{total})  
    Let $\alpha, \beta \in \mathbb{Z}_{\ge 0}^n$.  
    If $|\alpha| > |\beta|$, then $\alpha >_{grevlex} \beta$.  
    If $|\alpha| < |\beta|$, then $\beta >_{grevlex} \alpha$.  
    If $|\alpha| = |\beta|$, then $\alpha - \beta$ has a rightmost nonzero entry
    unless $\alpha = \beta$.  
    If the rightmost nonzero entry is negative, then 
    $\alpha >_{grevlex} \beta$.  
    If it is positive, then $\beta >_{grevlex} \alpha$.  
    Thus either $\alpha \ge_{grevlex} \beta$ or 
    $\beta \ge_{grevlex} \alpha$.

    Now suppose $\alpha >_{grevlex} \beta$ and 
    $\gamma \in \mathbb{Z}_{\ge 0}^n$.  
    We must show $\alpha + \gamma >_{grevlex} \beta + \gamma$.
    If $|\alpha| > |\beta|$, then  
    \[
        |\alpha + \gamma| = |\alpha| + |\gamma| 
        > |\beta| + |\gamma| = |\beta + \gamma|.
    \]
    Thus $\alpha + \gamma >_{grevlex} \beta + \gamma$.
    If $|\alpha| = |\beta|$, then the rightmost nonzero entry of 
    $\alpha - \beta$ is negative.  
    Since 
    \[
        (\alpha + \gamma) - (\beta + \gamma) = \alpha - \beta,
    \]
    the rightmost nonzero entry is unchanged and remains negative.  
    Thus $\alpha + \gamma >_{grevlex} \beta + \gamma$.

    Finally, we show $>_{grevlex}$ is a well-ordering.  
    Let $S \subseteq \mathbb{Z}_{\ge 0}^n$ be nonempty.  
    The set $\{|\alpha| : \alpha \in S\} \subseteq \mathbb{Z}_{\ge 0}$ 
    has a minimum since $\mathbb{Z}_{\ge 0}$ is well-ordered.  
    Restricting to elements of minimal total degree, 
    the rightmost nonzero entry comparison gives a smallest element.  
    Thus every nonempty subset has a minimal element.

    Thus $>_{grevlex}$ is a monomial ordering.
\end{proof}


\begin{tcolorbox}[title=Problem 7, breakable]
    Let $>$ be any monomial order.
    \begin{enumerate}
        \item Show that $\alpha \ge 0$ for all $\alpha \in \mathbb{Z}_{\ge 0}^n$. Hint: Proof by contradiction.
        \item Show that if $x^\alpha$ divides $x^\beta$, then $\alpha \le \beta$. Is the converse true?
        \item Show that if $\alpha \in \mathbb{Z}_{\ge 0}^n$, then $\alpha$ is the smallest element of $\alpha + \mathbb{Z}_{\ge 0}^n = \{\alpha + \beta \mid \beta \in \mathbb{Z}_{\ge 0}^n\}$.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose, for contradiction, that there exists $\alpha \in \mathbb{Z}_{\ge 0}^n$ with $\alpha < 0$.  
    Since $>$ is a monomial order, it is compatible with addition, so adding $\alpha$ to both sides gives
    \[
    2\alpha < \alpha < 0.
    \]  
    Continuing this way produces an infinite descending chain
    \[
    \alpha > 2\alpha > 3\alpha > \cdots,
    \]
    contradicting the well-ordering property. 
\end{proof}

\begin{proof}
    Suppose $x^\alpha$ divides $x^\beta$. Then there exists $\gamma \in \mathbb{Z}_{\ge 0}^n$ such that
    \[
    x^\alpha \cdot x^\gamma = x^\beta.
    \]  
    Comparing exponents componentwise, we have $\alpha + \gamma = \beta$, so $\alpha \le \beta$.  
    The converse is also true.
\end{proof}

\begin{proof}
    Suppose $\alpha \in \mathbb{Z}_{\ge 0}^n$. Consider any $\beta \in \alpha + \mathbb{Z}_{\ge 0}^n$, so $\beta = \alpha + \gamma$ for some $\gamma \in \mathbb{Z}_{\ge 0}^n$.  
    Since $\gamma \ge 0$ componentwise and $>$ is a monomial order, we have
    \[
    \alpha \le \alpha + \gamma = \beta.
    \]  
    Thus $\alpha$ is the smallest element of $\alpha + \mathbb{Z}_{\ge 0}^n$.
\end{proof}

\begin{tcolorbox}[title=Problem 10, breakable]
    In $\mathbb{Z}_{\ge 0}$ with the usual order, between any two integers,
    there are only a finite number of other integers.
    Is this necessarily true in $\mathbb{Z}_{\ge 0}^n$ for a monomial order? Is it true for grlex?
\end{tcolorbox}

\begin{proof}
    Let $\alpha, \beta$ be elements in $\mathbb{Z}_{\ge 0}$
    such that there are an infinite number of elements between them.
    Suppose wlog we have the following 
    \[\alpha < \cdots < \beta.\]
    Now starting from $\beta$ we can find an infinitely decreasing 
        sequence contradicting that $<$ is well-ordered.
\end{proof}


\begin{tcolorbox}[title=Problem 11, breakable]
    Let $>$ be a monomial order on $k[x_1, \ldots, x_n]$.
    \begin{enumerate}
        \item Let $f \in k[x_1, \ldots, x_n]$ and let $m$ be a monomial. Show that $LT(m \cdot f) = m \cdot LT(f)$.
        \item Let $f, g \in k[x_1, \ldots, x_n]$. Is $LT(f \cdot g)$ necessarily the same as $LT(f) \cdot LT(g)$?
        \item If $f_i, g_i \in k[x_1, \ldots, x_n]$, $1 \le i \le s$, is $LM(\sum_{i=1}^{s} f_i g_i)$ necessarily equal to $LM(f_i) \cdot LM(g_i)$ for some $i$?
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Let $m = x^\gamma$ and $f = x^{\beta_1} + \cdots + x^{\beta_n}$ where 
    \[
    \beta_1 > \cdots > \beta_n.
    \]
    Then by part (2) of Definition 1 we have 
    \[
    \beta_1 + \gamma > \cdots > \beta_n + \gamma.
    \]
    So $LT(m \cdot f) = x^{\beta_1 + \gamma}$.
    Similarly, $m \cdot LT(f) = x^\gamma \cdot x^{\beta_1}
    = x^{\gamma + \beta_1} = x^{\beta_1 + \gamma}
    = LT(m \cdot f)$, as required.
\end{proof}

\textbf{Solution: } Since $LT$ uses the same monomial ordering,
it is clear that they are necessarily the same.

\textbf{Solution: } No, since the summation may cancel terms.


\begin{tcolorbox}[title=Problem 12, breakable]
    Lemma 8 gives two properties of the multidegree.
    \begin{enumerate}
        \item Prove Lemma 8. Hint: The arguments used in Exercise 11 may be relevant.
        \item Suppose that $multideg(f) = multideg(g)$ and $f + g \ne 0$.
        Give examples to show that $multideg(f + g)$ may or may not equal $max(multideg(f), multideg(g))$.
    \end{enumerate}
\end{tcolorbox}

\begin{theorem}
    Let $f, g \in k[x_1, \ldots, x_n]$ be nonzero polynomials.
    Then:
    \begin{enumerate}
        \item $multideg(fg) = multideg(f) + multideg(g)$.
        \item If $f + g \ne 0$, then $multideg(f + g) \le max(multideg(f), multideg(g))$.
        If, in addition, $multideg(f) \ne multideg(g)$, then equality occurs.
    \end{enumerate}
\end{theorem}

\begin{proof}
    Let $LT(f) = x^\alpha$, $LT(g) = x^\beta$, and $LT(fg) = x^\gamma$.
    By Problem 11 we have 
    \[
    LT(fg) = LT(f)LT(g) = x^\alpha x^\beta = x^{\alpha + \beta}.
    \]
    Thus $\gamma = \alpha + \beta$. Therefore
    \[
    multideg(fg) = \gamma = \alpha + \beta 
    = multideg(f) + multideg(g).
    \]
\end{proof}

\begin{proof}
    Suppose $f + g \ne 0$.
    It is clear that the addition of two polynomials will not increase the multidegree 
    of any monomial.
    However, some leading terms of $f$ and $g$ may cancel each other.
    Thus we have 
    \[
    multideg(f + g) \le \max(multideg(f), multideg(g)).
    \]

    Now suppose $f + g \ne 0$ and $multideg(f) \ne multideg(g)$.
    Suppose without loss of generality that $LT(f) > LT(g)$.
    Then $LT(f)$ cannot be cancelled by any monomial in $g$.
    Thus $LT(f+g) = LT(f)$ and therefore
    \[
    multideg(f+g) = multideg(f) 
    = \max(multideg(f), multideg(g)).
    \]
\end{proof}

\textbf{Solution (2):}
Example where equality occurs.
\[
f = x^2 + y,\quad g = x^2 + 1
\]
Example where they are not equal.
\[
f = x^2 + y,\quad g = -x^2 + 1
\]

\begin{tcolorbox}[title=Problem 13, breakable]
    Prove that $1 < x < x^2 < x^3 < \cdots$ is the unique monimial order on $k[x]$.
\end{tcolorbox}

\begin{proof}
    Suppose for some $i$ we have $x^i > x^{i+1}$.
    Multiplying by $x$ repeatedly gives
    \[
    x^i > x^{i+1} > x^{i+2} > \cdots,
    \]
    an infinite strictly decreasing chain, contradicting that a monomial order
    is a well-order. 
\end{proof}

\subsection{A Division Algorithm in $k[x_1, \ldots, x_n]$}

\begin{tcolorbox}[title=Problem 1, breakable]
    Compute the remainder on division of the given polynomial $f$ 
    by the ordered set $F$ (by hand). Use grlex order,
    then the lex order in each case.
    \begin{enumerate}
        \item $f = x^7 y^2 - y + 1, F = (x y^2 - x, x - y^3)$.
        \item Repeat part (a) with the order of the pair $F$ revsersed.
    \end{enumerate}
\end{tcolorbox}

\begin{enumerate}
    \item Original order $F = (xy^2 - x,\; x - y^3)$
    \begin{itemize}
        \item Grlex order
        \[
        \text{remainder} = x^7 - y + 1
        \]
        \item Lex order 
        \[
        \text{remainder} = x^7 - y + 1
        \]
    \end{itemize}

    \item Reversed order $F = (x - y^3,\; xy^2 - x)$
    \begin{itemize}
        \item Grlex order
        \[
        \text{remainder} = x^7 - y + 1
        \]
        \item Lex order
        \[
        \text{remainder} = y^{21} - y + 1
        \]
    \end{itemize}
\end{enumerate}

\begin{tcolorbox}[title=Problem 4, breakable]
    Let $f = q_1 f_1 + \cdots q_s f_s + r$ be the output of the division algorithm.
    \begin{enumerate}
        \item Complete the proof begun in the text that $multideg(f) \ge multideg(q_i f_i)$
        provided that $q_i f_i \ne 0$.
        \item Prove that $multideg(f) \ge multideg(r)$ when $r \ne 0$.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    The text showed that during the course of the algorithm,
        the multidegree of $p$ decreases.
    At this point we have $LT(p) \le LT(f)$.
    Now $q_i$ is of the form $\frac{LT(p)}{LT(f_i)}$ for some term in $p$.
    So $q_i \cdot LT(f_i) = LT(p)$ and by Lemma 8 we have 
    \[
        LT(p) = LT(q_i) \cdot LT(f_i) \le LT(f)
    \]
    which implies
    \[
        multideg(q_i f_i) \le multideg(f).
    \]
\end{proof}

\begin{proof}
    Suppose $r \ne 0$.
    $r$ is modified only via the addition of monomials from $p$.
    Thus
    \[
        multideg(r) \le multideg(p) \le multideg(f),
    \]
    as desired.
\end{proof}

\begin{tcolorbox}[title=Problem 5, breakable]
    We will study the division of $f = x^3 - x^2 y - x^2 z + x$
    by $f_1 = x^2 y - z$ and $f_2 = xy - 1$.
    \begin{enumerate}
        \item Compute using grlex order 
        \[r_1 = \text{remainder of $f$ on division by $(f_1, f_2)$}.\]
        \[r_2 = \text{remainder of $f$ on division by $(f_2, f_1)$}.\]
        Your results should be different. Where in the division algorithm did 
        the difference occur? 
        \item Is $r = r_1 - r_2$ in the ideal $\langle f_1, f_2 \rangle$?
        If so, find an explicit expression $r = A f_1 + B f_2$.
        If not, say why not.
        \item Compute the remainder of $r$ on division of $(f_1, f_2)$.
        Why could you have predicted your answer before doing the division?
        \item Find another product $g \in \langle f_1, f_2 \rangle$ such that the remainder on division 
        by $g$ by $(f_1, f_2)$ is nonzero. Hint: $(xy + 1) \cdot f_2 = x^2 y^2 - 1$, whereas $y \cdot f_1 = x^2 y^2 - yz$.
        \item Does the division algorithm give us a solution for the ideal membership problem for the ideal $\langle f_1, f_2 \rangle$?
        Explain your answer.
    \end{enumerate}
\end{tcolorbox}

\textbf{Solution (2):} The remainder is 
\[
r = x - 2z
\]
since no term of $r$ is divisible by any leading term of the divisors.

\begin{proof} 
    We have \[r = r_1 - r_2 = (x^3 - x^2 z + x - z) - (x^3 - x^2z + z) = x - 2z.\] 
    Now suppose $x - 2z = h(x^2 y - z) + g(xy - 1)$ where $h, g \in k[x, y, z]$. 
    But then $deg_x(x - 2z) = 1$ and $deg_x(rhs) \ge 2$ which is a contradiction. 
\end{proof}

\textbf{Solution (3):} The remainder of $r$ on division by $(f_1, f_2)$ is
\[
r = x - 2z,
\]
because the leading term of $r$ is not divisible by any leading term of $f_1$ or $f_2$.
We could have predicted this since the division algorithm stops immediately when no LT of $r$ is divisible.

\textbf{Solution (4):}
One example is
\[
g = (xy + 1) f_2 = x^2 y^2 - 1,
\]
or
\[
g = y f_1 = x^2 y^2 - yz.
\]
Both belong to $\langle f_1, f_2 \rangle$, yet the remainder on division by $(f_1,f_2)$ is nonzero.

\textbf{Solution (5):} No, the division algorithm does not in general solve the ideal membership problem. 
A nonzero remainder may occur depending on the order of divisor, even if the polynomial is in the ideal. 

\begin{tcolorbox}[title=Problem 8, breakable]
    Try to formulate a general pattern that fits the examples in 
    Exercises 5(c)(d), 6, and 7.
    What condition on the leading term of the polynomial 
    $g = A_1 f_1  + \cdots A_s f_s$ would guarantee that there was 
    a nonzero remainder on division by $(f_1, \ldots, f_2)$?
    What does your condition imply about the ideal membership problem?
\end{tcolorbox}

\textbf{Solution: }
If for all $i \in \{1, \ldots, s\}$ the leading term of $A_i f_i$ is not divisible by the leading term of any $f_j$ in $(f_1, \ldots, f_s)$, 
then the division by $(f_1, \ldots, f_s)$ produces a nonzero remainder.  
This means the division algorithm does not guarantee a solution to the ideal membership problem.

\begin{tcolorbox}[title=Problem 9, breakable]
    The discussion around equation (2) of Chapter 1, 4 shows that every
    polynomial $f \in \mathbb{R}[x, y, z]$ can be written as 
    \[f = h_1(y - x^2) + h_2(z - x^3) + r,\]
    where $r$ is a polynomial in $x$ alone and $\textbf{V}(y - x^2, z - x^3)$ is the twisted cubic curve in $\mathbb{R}^3$.
    \begin{enumerate}
        \item Give a proof of this fact using the division algorithm.
        Hint: You need to specify carefully the monomial order to be used.
        \item Use the parametrization of the twisted cube to show that $z^2 - x^4 y$
        vanishes at every point of the twisted cube.
        \item Find an explicit representation
        \[z^2 - x^4 y = h_1(y - x^2) + h_2(z - x^3),\]
        using the division algorithm.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Let $f \in \mathbb{R}[x, y, z]$.
    Furthermore let $F = (y - x^2, z - x^3)$.
    Now, we apply the division algorithm using reverse lex order to obtain $h_1, h_2, r$
    \[f = h_1(y - x^2) + h_2(z - x^3) + r.\]
    We know that $r \nmid y$ and $r \nmid z$ because $LT(y - x^2) = y$
        and $LT(z - x^3) = z$. 
    Thus, $r$ must be a polynomial in $x$ alone.
\end{proof}

\begin{proof}
    We use the parametrization $(t, t^2, t^3)$ and see 
    \[z^2 - x^4 y = (t^3)^2 - t^4 t^2 = t^6 - t^6 = 0.\]
\end{proof}

\begin{proof}
    Applying the division algorithm with the same monomial order as above, we obtain
    \[
    z^2 - x^4 y
    =
    (-x^4)(y - x^2)
    +
    (z + x^3)(z - x^3).
    \]
\end{proof}


\begin{tcolorbox}[title=Problem 11, breakable]
    In this exercise, we will characterize completely the expression 
    \[f = q_1 f_1 + \cdots + q_s f_s + r,\]
    that is produced by the division algorithm (among all the possible 
    expressions for $f$ of this form). Let $LM(f_i) = x^{\alpha(i)}$ and define 
    \begin{align*}
        \nabla_1 &= \alpha(1) + \mathbb{Z}_{\ge 0}^n, \\
        \nabla_2 &= (\alpha(2) + \mathbb{Z}_{\ge 0}^n) \setminus \nabla_1, \\
        &\vdots \\
        \nabla_s &= (\alpha(s) + \mathbb{Z}_{\ge 0}^n) \setminus \left(\bigcup_{i = 1}^s \nabla_i\right), \\
        \overline{\nabla} &= \mathbb{Z}_{\ge 0}^n \setminus \left(\bigcup_{i = 1}^s \nabla_i\right).
    \end{align*}
    (Note that $\mathbb{Z}_{\ge 0}^n$ is the disjoint union of the $\nabla_i$ and $\overline{\nabla}$.)
    \begin{enumerate}
        \item Show that $\beta \in \nabla_i$ if and only if $x^{\alpha(i)}$ divides $x^\beta$ and no $x^{\alpha(j)}$ with $j < i$ divides $x^\beta$.
        \item Show that $\gamma \in \overline{\nabla}$ if and only if no $x^{\alpha(i)}$ divides $x^\gamma$.
        \item Show that in the expression$f = q_1 f_1 + \cdots + q_s f_s + r$ computed by the division algorithm,
        for every $i$, every monomial $x^\beta$ in $q_i$ satisfies $\beta + \alpha(i) \in \nabla_i$, and every 
        monomial $x^\gamma$ in $r$ satisfies $\overline{\nabla}$.
        \item Show that there is exactly one expression $f = q_1 f_1 + \cdots + q_s f_s + r$ satisfying
        the properties given in part (3).
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose $\beta \in \nabla_i$.
    Then $\beta = \alpha(i) + \gamma$ for some $\gamma \in \mathbb{Z}_{\ge 0}^n$.
    Clearly, $x^{\alpha(i)} \mid x^\beta$.
    Now, suppose there exists $x^{\alpha(j)}$ such that $j < i$ and $x^{\alpha(j)} \mid x^\beta$.
    So $\beta = \alpha(j) + \mu$ for some $\mu \in \mathbb{Z}_{\ge 0}^n$.
    But then $\beta \in \left(\bigcup_{j = 1}^{i-1} \nabla_j\right)$ which is a contradiction.

    Conversely, suppose $x^{\alpha(i)}$ divides $x^\beta$ and no $x^{\alpha(j)}$ with $j < i$ divides $x^\beta$.
    Then $\beta = \alpha(i) + \gamma$ for some $\gamma \in \mathbb{Z}_{\ge 0}^n$.
    Furthermore, since no $x^{\alpha(j)}$ with $j < i$ divides $x^\beta$,
        we have $\beta \notin \left(\bigcup_{j = 1}^{i-1} \nabla_j\right)$.
    Thus we have $\beta \in \nabla_i$.
\end{proof}

\begin{proof}
    Suppose $\gamma \in \overline{\nabla}$.
    Furthermore, suppose there exists $i$ such that $x^{\alpha(i)} \mid x^\gamma$.
    Then $\gamma = \alpha(i) + \mu$ for some $\mu \in \mathbb{Z}_{\ge 0}^n$.
    Now, let $i$ be the smallest such index with this property.
    Clearly, $\gamma \in \nabla_i$, which contradicts $\gamma \in \overline{\nabla}$.

    Conversely, suppose no $x^{\alpha(i)}$ divides $x^\gamma$.
    Clearly $x^\gamma \notin \nabla_i$ for any $i$, thus 
        $x^\gamma \in \overline{\nabla}$.
\end{proof}

\begin{proof}
    Let $x^\beta$ be a monomial in $q_i$ for some $i$.
    Now, $q_i$ is produced via the division algorithm, thus 
        there was some $p'$ such that $LT(f_i) x^\beta$ is a term in $p'$.
    Thus $\beta \in \nabla_i$.

    Now let $x^\gamma$ be a monomial in $r$.
    Since $x^\gamma \nmid LT(f_i)$ for any $i$,
    we must have $x^\gamma \not= \alpha(i) + \beta$ for any $\beta \in \mathbb{Z}_{\ge 0}^n$.
    Thus we have $\gamma \in \overline{\nabla}$.
\end{proof}

\begin{proof}
    Suppose there are two expressions $f, f'$ satisfying
        the properties given in part (3).
    Clearly the division algorithm is deterministic under the same monomial ordering.
    Thus we must have $f = f'$.
\end{proof}


\begin{tcolorbox}[title=Problem 12, breakable]
    Show that the operation of computing remainders on division by $F = (f_1, \ldots, f_s)$
    is linear over $k$. That is, if the remainder on division 
    of $g_i$ by $F$ is $r_i, i = 1, 2$ then, for any 
    $c_1, c_2 \in k$, the remainder of the division of $c_1 g_1
    + c_2 g_2$ is $c_1 r_1  + c_2 r_2$. Hint: Use Exercise 11.
\end{tcolorbox}

\begin{proof}
    We apply the division algorithm and find
    \begin{align*}
        c_1 g_1 + c_2 g_2 
        &= c_1(q_{11} f_1 + \cdots + q_{1s} f_s + r_1)
         + c_2(q_{21} f_1 + \cdots + q_{2s} f_s + r_2) \\
        &= (c_1 q_{11} + c_2 q_{21}) f_1 + \cdots + (c_1 q_{1s} + c_2 q_{2s}) f_s
         + (c_1 r_1 + c_2 r_2).
    \end{align*}
    Now, by Exercise 11, every monomial in $q_{ij}$ satisfies 
    $\beta + \alpha(j) \in \nabla_j$, and every monomial in $r_i$ satisfies 
    $\gamma \in \overline{\nabla}$. Multiplying by $c_1, c_2$ does not change which 
    monomials appear, so $(c_1 q_{1j} + c_2 q_{2j})$ still satisfies 
    $\beta + \alpha(j) \in \nabla_j$ and $c_1 r_1 + c_2 r_2$ still satisfies 
    $\gamma \in \overline{\nabla}$.
    By Exercise 11 part (4), this uniquely determines the remainder. 
    Therefore, the remainder on division of $c_1 g_1 + c_2 g_2$ by $F$ is
    \[
        c_1 r_1 + c_2 r_2.
    \]
\end{proof}

\subsection{Monomials Ideals and Dickson's Lemma}

\begin{tcolorbox}[title=Problem 1, breakable]
    Let $I \subseteq k[x_1, \ldots, x_n]$ be an ideal with the property 
    that for every $f = \sum c_\alpha x^\alpha$, every monomial $x^\alpha$,
    appearing in $f$ is also in $I$. Show that $I$ is a monomial ideal.
\end{tcolorbox}


\begin{proof}
    Let $J = \langle \{x^\alpha \in k[x_1, \ldots, x_n] \mid x^\alpha \in I\} \rangle$.
    Now, $J$ is clearly a monomial ideal and $J \subseteq I$.
    Now, let $f \in I$ with $f = \sum c_\alpha x^\alpha$.
    For each monomial $x^\alpha \in I$, we have $x^\alpha \in J$.
    Since $J$ is closed under addition and scalar multiplication, it follows that $f \in J$.
    Therefore $I \subseteq J$.
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
    Complete the proof of Lemma 3 begun in the text.
\end{tcolorbox}

\begin{theorem}
    Let $I$ be a monomial ideal, and let $f \in k[x_1, \ldots, x_n]$.
    Then the following are equivalent:
    \begin{enumerate}
        \item $f \in I$.
        \item Every term of $f$ lies in $I$.
        \item $f$ is a $k$-linear combination of monomials in $I$.
    \end{enumerate}
\end{theorem}

\begin{proof}
    As the book states, we only need to show $(1) \implies (2)$.
    Suppose $f \in I$ such that $f = \sum c_\alpha x^\alpha$.
    Let $c_\alpha x^\alpha$ be any term in $f$. 
    Since $I$ is a monomial ideal, it contains every monomial divisible by its generators
        thus $x^\alpha \in I$. 
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 5, breakable]
    Suppose that $I = \langle x^\alpha \mid \alpha \in A \rangle$
    is a monomial ideal, and let $S$ be the set of all exponents 
    that occur as monomials of $I$. For any monomial order $>$,
    prove that the smallest element of $S$ with respect to $>$
    must lie in $A$.
\end{tcolorbox}

\begin{proof}
    Let $\alpha$ be the minimal vector in $S$ with respect to $>$.
    Suppose, for contradiction, that $\alpha \notin A$.
    Since $I$ is a monomial ideal, $x^\alpha \in I$ can be written as
    $x^\alpha = \sum_i c_i x^{\gamma_i}$ with $x^{\gamma_i} \in I$ and $\gamma_i \in A$.
    But by minimality of $\alpha$, each $\gamma_i \ge \alpha$, thus one of them must equal $\alpha$.
    This contradicts $\alpha \notin A$ thus $\alpha \in A$.
\end{proof}

\begin{tcolorbox}[title=Problem 6, breakable]
    Let $I = \langle x^\alpha \mid \alpha \in A \rangle$ be a monomial ideal,
    and assume that we have a finite basis
    $I = \langle x^{\beta(1)}, \ldots, x^{\beta(s)} \rangle$.
    In the proof of Dickson's Lemma, we observed that each 
    $x^{\beta(i)}$ is divisible by $x^{\alpha(i)}$ for some 
    $\alpha(i)$ for some $\alpha(i) \in A$. Prove that 
    $I = \langle x^{\alpha(i)}, \ldots, x^{\alpha(s)} \rangle$.
\end{tcolorbox}

\begin{proof}
    Let $f \in I$. Since $I$ is a monomial ideal we have 
    $f = \sum_{i = 1}^n h_i x^{\alpha_i}$ where $\alpha_i \in A$ and $h_i \in k[x_1, \ldots, x_n]$.
    We can write 
    \[f = \sum_{i=1}^n x^{\alpha_i} h_i,\]
    so $x^{\alpha_i} \mid f$ for each $i$.
    Thus $f \in \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$,
    so $I \subseteq \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$.
    
    Now, let $f \in \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$.
    Then 
    \[f = h_1 x^{\alpha(1)} + \cdots + h_s x^{\alpha(s)}\]
    for some $h_i \in k[x_1, \ldots, x_n]$.
    Since each $\alpha(i) \in I$ and $I$ is closed under multiplication and addition,
    we have $f \in I$.
    Therefore $I = \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 7, breakable]
    Prove that Dickson's Lemma (Theorem 5) is equivalent to the 
    following statement: given a nonempty subset $A \subseteq \mathbb{Z}_{\ge 0}^n$,
    there are finitely many elements $\alpha(1), \ldots, \alpha(s) \in A$ such 
    that for every $\alpha \in A$, there exists some $i$ and some $\gamma \in \mathbb{Z}_{\ge 0}^n$
    such that $\alpha = \alpha(i) + \gamma$.
\end{tcolorbox}

\begin{proof}
    Suppose Dickson's Lemma holds. Let $A \subseteq \mathbb{Z}_{\ge 0}^n$ be given, 
        and consider the monomial ideal
    \[
        I = \langle x^\alpha \mid \alpha \in A \rangle \subseteq k[x_1, \dots, x_n].
    \]
    By Dickson's Lemma, $I$ has a finite generating set, say
    \[
        I = \langle x^{\alpha(1)}, \dots, x^{\alpha(s)} \rangle,
    \]
    with each $\alpha(i) \in A$. 
    Then for any $\alpha \in A$, the monomial $x^\alpha \in I$,
    so it is divisible by some $x^{\alpha(i)}$, 
        meaning $x^\alpha = x^{\alpha(i)} x^\gamma$ for 
    some $\gamma \in \mathbb{Z}_{\ge 0}^n$. 
    Thus $\alpha = \alpha(i) + \gamma$.

    Conversely, suppose the statement about the $\alpha(i)$ holds. 
    Let $I = \langle x^\alpha \mid \alpha \in A \rangle$.
    Then every $x^\alpha$ with $\alpha \in A$ is divisible by some $x^{\alpha(i)}$ thus 
    \[
        I = \langle x^{\alpha(1)}, \dots, x^{\alpha(s)} \rangle
    \]
    is finitely generated.
\end{proof}

\begin{tcolorbox}[title=Problem 8, breakable]
    If $I = \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$ is a monomial ideal,
    prove that a polynomial $f$ is in $I$ if and only if the remainder of $f$ on 
    division by $x^{\alpha(1)}, \ldots, x^{\alpha(s)}$ is zero.
    Hint: Use Lemma 2 and Lemma 3.
\end{tcolorbox}

\begin{proof}
    Suppose $I = \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$
        is a monomial ideal.
    Now let $f$ be an arbitrary element in $I$.
    By Lemma 2, for each term $t \in f$ there exists some $x^{\alpha(i)}$ such that $x^{\alpha(i)} \mid t$.
    Thus, no term of $f$ remains in the remainder, so the remainder $r = 0$.

    Conversely, suppose the remainder of $f$ on 
    division by $x^{\alpha(1)}, \ldots, x^{\alpha(s)}$ is zero.
    Then every term of $f$ is divisible by some $x^{\alpha(i)}$, 
    and by Lemma 3 this implies $f \in I$.
\end{proof}

\subsection{The Hilbert Basis Theorem and Grobner Bases}

\begin{tcolorbox}[title=Problem 1, breakable]
    Let $I = \langle g_1, g_2, g_3 \rangle \subseteq \mathbb{R}[x, y, z]$,
        where $g_1 = x y^2 - xz + y$, $g_2 = xy - z^2$
        and $g_3 = x - y z^4$.
    Using the lex order, give an example of $g \in I$
    such that $LT(g) \notin \langle LT(g_1), LT(g_2), LT(g_3) \rangle$.
\end{tcolorbox}

\begin{proof}
    Notice $y(x - yz^4) - (xy - z^2) = z^2 - y^2 z^4 \in I$.
    But clearly
    \begin{align*}
        LT(g_1) &= LT(x y^2 - xz + y) = x y^2 \nmid LT(y^2 z^4 - z^2) = y^2 z^4, \\
        LT(g_2) &= LT(xy - z^2) = xy \nmid LT(y^2 z^4 - z^2) = y^2 z^4, \\
        LT(g_3) &= LT(x - yz^4) = x \nmid LT(y^2 z^4 - z^2) = y^2 z^4.
    \end{align*}
    Thus $LT(g) \notin \langle LT(g_1), LT(g_2), LT(g_3) \rangle$.
\end{proof}

\begin{tcolorbox}[title=Problem 3, breakable]
    To generalize the situation of the previous two 
        exercises, suppose $I = \langle f_1, \ldots, f_s \rangle$
        is an ideal such that $\langle LT(f_1), \ldots, LT(f_s) \rangle$ is 
        strictly smaller than $\langle LT(I) \rangle$.
    \begin{enumerate}
        \item Prove that there is some $f \in I$ whose remainder 
        on division by $f_1, \ldots, f_s$ is nonzero.
        Hint: First show that $LT(f) \notin \langle LT(f_1), \ldots, LT(f_s) \rangle$
        for some $f \in I$. Then use Lemma 2 of 4.
        \item What does part (a) say about the ideal membership problem?
        \item How does part (a) relate to the conjecture you were asked to make in Exercise 8 of 3.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Since $\langle LT(f_1), \ldots, LT(f_s) \rangle$ is 
        strictly smaller than $\langle LT(I) \rangle$, we have 
        $\langle LT(f_1), \ldots, LT(f_s) \rangle \subseteq \langle LT(I) \rangle$.
    Suppose $LT(f) \in \langle LT(f_1), \ldots, LT(f_s) \rangle$ for all $f \in I$.
    Then 
    \[
        \langle LT(I) \rangle \subseteq \langle LT(f_1), \ldots, LT(f_s) \rangle \subseteq \langle LT(I) \rangle,
    \]
    contradicting that $\langle LT(f_1), \ldots, LT(f_s) \rangle$ is 
        strictly smaller than $\langle LT(I) \rangle$.
    Thus there is some $f \in I$ such that $LT(f) \notin \langle LT(f_1), \ldots, LT(f_s) \rangle$.
    Then by Lemma 2 there is some $f_i$ such that $LT(f_i) \nmid LT(f)$.
    It then follows that the remainder of $f$ on division by $f_1, \ldots, f_s$ is nonzero.
\end{proof}

\textbf{Solution (2):} It says that if there exists $f \in I$ such that $LT(f) \notin \langle LT(f_1), \ldots, LT(f_s) \rangle$, 
    then $f$ may have a nonzero remainder on division by $f_1, \ldots, f_s$. 
    So solving the ideal membership problem requires a generating set whose leading terms generate $\langle LT(I) \rangle$.

\textbf{Solution (3):} 
If $LT(f) \notin \langle LT(f_1), \ldots, LT(f_s) \rangle$ for some $f \in I$, 
then division by $f_1, \ldots, f_s$ gives a nonzero remainder. 
This shows that the generators must form a Grobner basis for the division algorithm to behave ``nicely''.

\begin{tcolorbox}[title=Problem 4, breakable]
    If $I \subseteq k[x_1, \ldots, x_n]$ is an ideal,
    prove that $\langle LT(g) \mid g \in I \setminus \{0\} \rangle = \langle LM(g) \mid g \in I \setminus \{0\} \rangle$.
\end{tcolorbox}

\begin{proof}
    Let $x \in \langle LT(g) \mid g \in I \setminus \{0\} \rangle$.
    Then $g = c x^\alpha$ for some $c \in k$, $\alpha \in \mathbb{Z}_{\ge 0}^n$.
    Since $c \ne 0$, we have $\frac{1}{c} \in k$.
    Then $\frac{1}{c} (c x^\alpha) = x^\alpha \in \langle LM(g) \mid g \in I \setminus \{0\} \rangle$.

    Conversely, let $x \in \langle LM(g) \mid g \in I \setminus \{0\} \rangle$.
    Then $g = x^\alpha$ for some $\alpha \in \mathbb{Z}_{\ge 0}^n$.
    Let $c \in k$ be the coefficient of $x^\alpha$ in some $h \in I$ with $LT(h) = c x^\alpha$.
    Then $c x^\alpha = LT(h) \in \langle LT(g) \mid g \in I \setminus \{0\} \rangle$,
        and multiplying by a nonzero scalar does not change the ideal.
    Thus $x \in \langle LT(g) \mid g \in I \setminus \{0\} \rangle$.
\end{proof}

\begin{tcolorbox}[title=Problem 5, breakable]
    Let $I$ be an ideal of $k[x_1, \ldots, x_n]$.
    Show that $G = \{g_1, \ldots, g_t\} \subseteq I$
    is a Grobner basis of $I$ if and only if
    the leading term of any element of $I$ is divisible 
    by one of the $LT(g_i)$.
\end{tcolorbox}

\begin{proof}
    Suppose $G = \{g_1, \ldots, g_t\} \subseteq I$ is a Grobner basis of $I$.
    If there exists $f \in I$ such that $LT(f)$ is not divisible by any $LT(g_i)$, 
    then division of $f$ on $G$ would produce a nonzero remainder, 
    contradicting that $G$ is a Grobner basis.

    Conversely, suppose the leading term of any element of $I$ is divisible 
        by one of the $LT(g_i)$. 
    Then for any $f \in I$, division by all $g_i$ gives a zero remainder.
    Thus $G$ is a Grobner basis.
\end{proof}

\begin{tcolorbox}[title=Problem 10, breakable]
    Let $I \subseteq k[x_1, \ldots, x_n]$ be a principle 
    ideal domain (that is, $I$ is generated by a single $f \in I$ -
    see 5 of chapter 1). Show that any finite subset of $I$ 
    containing a generator for $I$ is a grobner basis for $I$.
\end{tcolorbox}

\begin{proof}
    Let $G \subseteq I$ be a finite set containing $f \in I$, where     
        $f$ is a generator of $I$.
    Let $f' \in I$ be arbitrary. Then $f \mid f'$,
        so $G$ is a Grobner basis of $I$.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 12, breakable]
    Show that if we take as hypothesis that 
    every ascending chain of ideals in $k[x_1, \ldots, x_n]$
    stabilizes, then the conclusion of the Hilbert Basis 
    Theorem is a consequence. Hint: Argue by contradiction,
    assuming that some ideal $I \subseteq k[x_1, \ldots, x_n]$
    has no finite generating set. Also, the argument
    given should not make any special use of properties 
    of polynomials. Indeed it is true that 
    in any commutative ring $R$, the following two 
    statements are equivalent:
    \begin{enumerate}
        \item Every ideal $I \subseteq R$ is finitely generated.
        \item Every ascending chain of ideals of $R$ stabilizes.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose every ascending chain of ideals in $k[x_1, \ldots, x_n]$ stabilizes.
    Assume, for contradiction, that some ideal $I \subseteq k[x_1, \ldots, x_n]$ 
        has no finite generating set.
    Suppose $\langle f_1, \ldots, f_s \rangle \subseteq I$ for some $s \in \mathbb{N}$.
    There must exist $g_1 \in I$ not in $\langle f_1, \ldots, f_s \rangle$, 
        otherwise $I$ would be finitely generated by the $f_i$. 
    Appending $g_1$ to the list gives a strictly larger ideal.
    Repeating this process, we choose $g_2, g_3, \dots \in I$ 
        each not in the previous ideal, producing an ascending chain
    \[
        \langle f_1, \ldots, f_s \rangle \subsetneq 
        \langle f_1, \ldots, f_s, g_1 \rangle \subsetneq 
        \langle f_1, \ldots, f_s, g_1, g_2 \rangle \subsetneq \cdots
    \]
    This contradicts the assumption that every ascending chain of ideals in 
        $k[x_1, \ldots, x_n]$ stabilizes.
\end{proof}

\begin{tcolorbox}[title=Problem 13, breakable]
    Let
    \[V_1 \supseteq V_2 \supseteq V_3 \supseteq \cdots\]
    be a descending chain of affine varieties. Show 
    that there is some $N \ge 1$ such that
    $V_N = V_{N + 1} = V_{N = 2} + \cdots$.
\end{tcolorbox}

\begin{proof}
    By Proposition 8, since 
    \[V_1 \supseteq V_2 \supseteq V_3 \supseteq \cdots\]
    we have 
    \[\mathbf{I}(V_1) \subseteq \mathbf{I}(V_2) \subseteq \mathbf{I}(V_3) \subseteq \cdots,\]
    which stabilizes by the ACC. Thus, there exists $N$ such that
    \[\mathbf{I}(V_N) = \mathbf{I}(V_{N+1}) = \mathbf{I}(V_{N+2}) = \cdots,\]
    and therefore
    \[V_N = V_{N+1} = V_{N+2} = \cdots.\]
\end{proof}

\begin{tcolorbox}[title=Problem 14, breakable]
    Let $f_1, f_2, \ldots \in k[x_1, \ldots, x_n]$ be 
    an infinite collection of polynomials. Prove that 
    there is an integer $N$ such that 
    $f_i \in \langle f_1, \ldots, f_N \rangle$ for all 
    $i \ge N + 1$. Hint: Use $f_1, f_2, \ldots$ to create 
    an ascending chain of ideals.
\end{tcolorbox}

\begin{proof}
    If not, the corresponding ascending chain of ideals
    in $k[x_1,\dots,x_n]$ would not stabilize, 
    contradicting that every ideal has a finite generating set.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 15, breakable]
    Given polynomials $f_1, f_2, \ldots \in k[x_1, \ldots, x_n]$,
    let $\textbf{V}(f_1, f_2, \ldots) \subseteq k^n$ be the 
    solutions of the infinite system of equations 
    $f_1 = f_2 = 0$. Show that there is some $N$ such 
    that $\textbf{V}(f_1, f_2, \ldots) = \textbf{V}(f_1, \ldots, f_N)$.
\end{tcolorbox}

\begin{proof}
    Let $I = \langle f_1, f_2, \dots \rangle \subseteq k[x_1, \dots, x_n]$ 
        be the ideal generated by all the $f_i$. 
    By the Hilbert Basis Theorem, 
        $I$ is finitely generated, say $I = \langle f_1, \dots, f_N \rangle$. 
    Then by Proposition 9
    \[\textbf{V}(f_1, f_2, \dots) = \textbf{V}(I) = \textbf{V}(f_1, \dots, f_N).\]
\end{proof}

\begin{tcolorbox}[title=Problem 16, breakable]
    In Chapter 1, 4 we defined the ideal $\textbf{I}(V)$
    of a variety $V \subseteq k^n$. In this section,
    we defined the variety of an ideal (see Definition 8).
    In particular, this means that $\textbf{V}(\textbf{I}(V))$
    is a variety. Prove that $\textbf{V}(\textbf{I}(V)) = V$.
    Hint: See the proof of Lemma 7 of Chapter 1, 4.
\end{tcolorbox}

\begin{proof}
    Let $x$ be an arbitrary element in $\mathbf{V}(\mathbf{I}(V))$.
    Then by definition, for all $f \in \mathbf{I}(V)$ we have $f(x) = 0$.
    Since $\mathbf{I}(V)$ consists of all polynomials vanishing on $V$,
    it follows that $x \in V$. Thus
    \[\mathbf{V}(\mathbf{I}(V)) \subseteq V.\]

    Conversely, let $x \in V$. Since
        every polynomial in $\mathbf{I}(V)$ vanishes on $V$ we have
        $f(x) = 0$ for all $f \in \mathbf{I}(V)$. Thus
    \[x \in \mathbf{V}(\mathbf{I}(V)) \implies V \subseteq \mathbf{V}(\mathbf{I}(V)).\]
\end{proof}

\begin{tcolorbox}[title=Problem 18, breakable]
    When an ideal has a basis where some of the elements 
    can be factored we use the factorization to help 
    understand the variety.
    \begin{enumerate}
        \item Show that if $g \in k[x_1, \ldots, x_n]$ factors 
        as $g = g_1 g_2$, then for any $f$, we have $\textbf{V}(f, g) = \textbf{V}(f, g_1) \cup \textbf{V}(f, g_2)$.
        \item Show that in $\mathbb{R}^3$, $\textbf{V}(y - x^2, xz - y^2) = \textbf{V}(y - x^2, xz - x^4)$.
        \item Use part (a) to describe and/or sketch the variety from part (b).
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose $g \in k[x_1, \ldots, x_n]$ factors as $g = g_1 g_2$,
    and let $f$ be any polynomial in $k[x_1, \ldots, x_n]$.
    If $x \in \mathbf{V}(f, g)$, then 
    \[f(x) = 0 \quad \text{and} \quad g(x) = g_1(x) g_2(x) = 0,\] 
    so either $g_1(x) = 0$ or $g_2(x) = 0$. Thus
    \[x \in \mathbf{V}(f, g_1) \cup \mathbf{V}(f, g_2).\]

    Conversely, if $x \in \mathbf{V}(f, g_1) \cup \mathbf{V}(f, g_2)$,
    then wlog $x \in \mathbf{V}(f, g_2)$. 
    Thus $f(x) = 0$ and $g_2(x) = 0$ therefore
    \[g(x) = g_1(x) g_2(x) = g_1(x) \cdot 0 = 0,\] 
    and thus $x \in \mathbf{V}(f, g)$.
\end{proof}

\textbf{Solution (2):}
Substituting $y = x^2$ into $xz - y^2$ gives 
$xz - (x^2)^2 = xz - x^4$ thus
\[\mathbf{V}(y - x^2, xz - y^2) = \mathbf{V}(y - x^2, xz - x^4).\]

\textbf{Solution (3):}
Using part (a), we can factor $xz - x^4 = x(z - x^3)$ thus the variety 
is the union of 
\[\mathbf{V}(y - x^2, x) \cup \mathbf{V}(y - x^2, z - x^3).\] 
Thus geometrically we have
\begin{enumerate}
    \item the parabola $y = x^2$.
    \item the curve $y = x^2$, $z = x^3$.
\end{enumerate}

\subsection{Properties of Grobner Bases}

\begin{tcolorbox}[title=Problem 1, breakable]
    Show that Proposition 1 can be strengthened slightly as follows.
    Fix a monomial order and let $I \subseteq k[x_1, \ldots, x_n]$ be an ideal.
    Suppose that $f \in k[x_1, \ldots, x_n]$.
    \begin{enumerate}
        \item Show that $f$ can be written in the form $f = g + r$, where $g \in I$ and no 
        term of $r$ is divisible by any element of $LT(I)$.
        \item Given two expressions $f = g + r = g' + r'$ as in part (1), prove that $r = r'$.
        thus, $r$ and $g$ are uniquely determined.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    By Corollary 6, $I$ has a Grobner basis.
    Then by Proposition 1 we obtain $g, r$ such that $f = g + r$ and $g \in I$.
    Additionally, as shown in the text, $r$ is unique.
    Thus, if $f = g + r = g' + r'$, since $r = r'$ we have $g = g'$ as required.
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
    In 5, we showed that $G = \{x + z, y - z\}$ is a Grobner basis for lex order.
    Let us use this basis to study the uniqueness of the division algorithm.
    \begin{enumerate}
        \item Divide $xy$ by $x + z, y - z$.
        \item Now interchange the polynomials and divide $xy$ by $y - z, x + z$.
    \end{enumerate}
\end{tcolorbox}

\textbf{Solution (1):}
\begin{align*}
xy &= y(x+z) - z(y-z) - z^2.
\end{align*}
\textbf{Solution (2):}
\begin{align*}
xy &= x(y - z) + z(x + z) - z^2.
\end{align*}

\newpage
\begin{tcolorbox}[title=Problem 3, breakable]
    In Corollary 2, we showed that if $I = \langle g_1, \ldots, g_t \rangle$ and if 
    $G = \{g_1, \ldots, g_t\}$ is a Grobner basis for $I$, then $\overline{f}^G = 0$
    for all $f \in I$. Prove the converse of this statement. Namely,
    show that if $G$ is a basis for $I$ with the property that $\overline{f}^G = 0$
    for all $f \in I$, then $G$ is a grobner basis for $I$. 
\end{tcolorbox}

\begin{proof}
    Suppose $G$ is a basis for $I$ with the property that $\overline{f}^G = 0$
    for all $f \in I$. We must show $\langle LT(I) \rangle = \langle LT(g_1), \ldots, LT(g_t) \rangle$.

    Let $LT(f) \in \langle LT(I) \rangle$ for some $f \in I$.
    Since $\overline{f}^G = 0$, the division algorithm gives
    $f = h_1 g_1 + \cdots + h_t g_t$ for some $h_1, \ldots, h_t \in k[x_1,\ldots,x_n]$.
    Thus the leading term $LT(f)$ must be divisible by $LT(g_i)$ for some $i$.
    Thus $LT(f) \in \langle LT(g_1), \ldots, LT(g_t) \rangle$ so
    \[
    \langle LT(I) \rangle \subseteq \langle LT(g_1), \ldots, LT(g_t) \rangle.
    \]
    Conversely, since $g_i \in I$ for each $i$, we have $LT(g_i) \in \langle LT(I) \rangle$.
    Thus
    \[
    \langle LT(g_1), \ldots, LT(g_t) \rangle \subseteq \langle LT(I) \rangle.
    \]
\end{proof}

\begin{tcolorbox}[title=Problem 4, breakable]
    Let $G$ and $G'$ be Grobner bases for an ideal $I$ with respect to the 
    same monomial order in $k[x_1, \ldots, x_n]$. Show that 
    $\overline{f}^G = \overline{f}^{G'}$ for all $f \in k[x_1, \ldots, x_n]$.
    Hence, the remainder on division by a Grobner basis is even independent of 
    which Grobner basis we use, as long as we use one particular monomial order.
    Hint: See Exercise 1.
\end{tcolorbox}

\begin{proof}
    We can first fix a monomial order.
    Then by Exercise 1 we can divide $f$ by $G, G'$ to get  
        two expressions $f = g + r$ and $f = g' + r'$.
    But since $r$ is unique we have $r = r'$.
    Thus $\overline{f}^G = \overline{f}^{G'}$.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 7, breakable]
    Prove that $multideg(S(f, g)) < \gamma$, where $x^\gamma = lcm(LM(f), LM(g))$.
    Explain why this inequality is a precise version of the claim that S-polynomials 
    are designed to produce cancellation.
\end{tcolorbox}


\begin{proof}
    We can write 
    \[
    S(f, g) = \frac{x^\gamma}{LT(f)} \cdot \left(LT(f) + \text{ other terms }\right) 
             - \frac{x^\gamma}{LT(g)} \cdot \left(LT(g) + \text{ other terms}\right).
    \]
    When distributed it is clear that $\frac{x^\gamma}{LT(f)} \cdot LT(f)$ and 
    $\frac{x^\gamma}{LT(g)} \cdot LT(g)$ both produce the term $x^\gamma$.
    So when $\frac{x^\gamma}{LT(f)}$ is distributed the $multideg(\textsl{other terms}) < multideg(LM(f))$.
    Then distributing we get 
    \[
    x^\gamma + \frac{x^\gamma}{LT(f)}\left(\text{ other terms}\right) 
    - \left(x^\gamma + \frac{x^\gamma}{LT(g)}\left(\text{ other terms}\right)\right)
    \]
    and cancelling we find 
    \[
    \frac{x^\gamma}{LT(f)}\left(\text{other terms}\right) 
    - \frac{x^\gamma}{LT(g)}\left(\text{other terms}\right).
    \]
    Since the other terms of $f$ and $g$ have multidegree strictly less than 
    $multideg(LM(f))$ and $multideg(LM(g))$, multiplying by 
    $\frac{x^\gamma}{LT(f)}$ or $\frac{x^\gamma}{LT(g)}$ gives terms of multidegree strictly less than $\gamma$.
    Thus we have 
    \[
    multideg(S(f, g)) < \gamma.
    \]
    Clearly this construction cancels the leading term.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 8, breakable]
    As in the proof of Theorem 6, suppose that 
    $c_i x^{\alpha(i)} g_i$ and $c_j x^{\alpha(j)} g_j$ have multidegree $\delta$.
    Prove that 
    \[S(x^{\alpha(i)} g_i, x^{\alpha (j)} g_j) = x^{\delta  - \gamma_{i j}} S(g_i, g_j),\]
    where $x^{\gamma_{i, j}} = lcm(LM(g_I), LM(g_j))$.
\end{tcolorbox}

\begin{proof}
    Let $f = c_i x^{\alpha(i)} g_i$ and $g = c_j x^{\alpha(j)} g_j$.
    Then 
    \[
    S(f, g) = \frac{x^\gamma}{LT(f)} \cdot f - \frac{x^\gamma}{LT(g)} \cdot g 
    = \frac{x^\gamma}{LT(c_i x^{\alpha(i)} g_i)} \cdot (c_i x^{\alpha(i)} g_i) 
    - \frac{x^\gamma}{LT(c_j x^{\alpha(j)} g_j)} \cdot (c_j x^{\alpha(j)} g_j).
    \]
    Now since $c_i x^{\alpha(i)} g_i$ and $c_j x^{\alpha(j)} g_j$ have multidegree $\delta$ we have 
    $x^\gamma = x^\delta$. Also,
    \[
    LT(c_i x^{\alpha(i)} g_i) = c_i x^{\alpha(i)} LT(g_i), \qquad
    LT(c_j x^{\alpha(j)} g_j) = c_j x^{\alpha(j)} LT(g_j).
    \]
    Substituting gives
    \[
    S(f,g)
    =
    \frac{x^\delta}{c_i x^{\alpha(i)} LT(g_i)} (c_i x^{\alpha(i)} g_i)
    -
    \frac{x^\delta}{c_j x^{\alpha(j)} LT(g_j)} (c_j x^{\alpha(j)} g_j)
    =
    \frac{x^\delta}{LT(g_i)} g_i
    -
    \frac{x^\delta}{LT(g_j)} g_j.
    \]
    Since $x^{\gamma_{ij}} = lcm(LM(g_i), LM(g_j))$, we can write
    $x^\delta = x^{\delta - \gamma_{ij}} x^{\gamma_{ij}}$. Thus
    \[
    S(f,g)
    =
    x^{\delta - \gamma_{ij}}
    \left(
    \frac{x^{\gamma_{ij}}}{LT(g_i)} g_i
    -
    \frac{x^{\gamma_{ij}}}{LT(g_j)} g_j
    \right)
    =
    x^{\delta - \gamma_{ij}} S(g_i,g_j)\].
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 9, breakable]
    Show that $\{y - x^2, z - x^3\}$ is not a Grobner basis for a lex order with $x > y > z$.
\end{tcolorbox}

\textbf{Solution: }
\[
S(g_1,g_2)
=
\frac{x^3}{x^2}(y-x^2)-\frac{x^3}{x^3}(z-x^3)
=
x(y-x^2)-(z-x^3)
=
xy-z
\]
\[
\overline{S(g_1,g_2)}^{\{g_1,g_2\}} = xy - z \neq 0
\]

\newpage
\begin{tcolorbox}[title=Problem 11, breakable]
    Let $f, g \in k[x_1, \ldots, x_n]$ be polynomials such that $LM(f)$ and $LM(g)$ are 
    relatively prime monomials and $LC(f) = LC(g) = 1$. 
    Assume that $f$ or $g$ has at least two terms.
    \begin{enumerate}
        \item Show that $S(f, g) = -(g - LT(g))f + (f - LT(f))g$.
        \item Deduce that $S(f, g) \ne 0$ and that the leading monomial of $S(f, g)$
        is a multiple of either $LM(f)$ and $LM(g)$ in this case.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    We have 
    \[S(f, g) 
        = \frac{x^\gamma}{LT(f)} \cdot f - \frac{x^\gamma}{LT(g)} \cdot g 
        = \frac{x^\gamma}{LC(f) LM(f)} \cdot f - \frac{x^\gamma}{LC(g) LM(g)} \cdot g.\]
    Then $LC(f) = LC(g) = 1$ so $LT(f) = LM(f)$ and $LT(g) = LM(g)$. Also, since 
        $gcd(LM(f), LM(g)) = 1$ we have $x^\gamma = LM(f) LM(g)$. 
    Thus 
    \[\frac{x^\gamma}{LC(f) LM(f)} \cdot f - \frac{x^\gamma}{LC(g) LM(g)} \cdot g 
        = \frac{LM(f) LM(g)}{LT(f)} \cdot f - \frac{LM(f) LM(g)}{LT(g)} \cdot g = LT(g) \cdot f - LT(f) \cdot g.\]

    Now write $f = LT(f) + (f - LT(f))$ and $g = LT(g) + (g - LT(g))$. Substituting gives
    \[
    S(f,g) = LT(g)(LT(f) + (f-LT(f))) - LT(f)(LT(g) + (g-LT(g))).
    \]
    Expanding and canceling $LT(g)LT(f)$ gives
    \[
    S(f,g) = LT(g)(f-LT(f)) - LT(f)(g-LT(g))
           = -(g-LT(g))f + (f-LT(f))g.
    \]
\end{proof}

\begin{proof}
    Suppose wlog $f$ has more than one term.
    Then $f - LT(f) \ne 0$ so 
    \[
    S(f,g) = -(g-LT(g))f + (f-LT(f))g \ne 0.
    \]
    Also every term of $(f-LT(f))g$ is divisible by $LM(g)$, 
        and every term of $(g-LT(g))f$ is divisible by $LM(f)$.
    Therefore the leading monomial of $S(f,g)$ is a multiple of either $LM(f)$ or $LM(g)$.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 12, breakable]
    Let $f, g \in k[x_1, \ldots, x_n]$ be a nonzero and $x^\alpha, x^\beta$ be monomials.
    Verify that 
    \[S(x^\alpha f, x^\beta g) = x^\gamma S(f, g),\]
    where 
    \[x^\gamma = \frac{lcm(x^\gamma LM(f), x^\beta LM(g))}{lcm(LM(f), LM(g))}.\]
    Be sure to prove that $x^\gamma$ is a monomial. 
\end{tcolorbox}

\begin{proof}
    We have 
    \[
        S(x^\alpha f, x^\beta g) = \frac{x^\gamma}{LT(x^\alpha f)} \cdot (x^\alpha f) - \frac{x^\gamma}{LT(x^\beta g)} \cdot (x^\beta g),
    \]
    where $x^\gamma = lcm(x^\alpha LM(f), x^\beta LM(g))$.  
    Then 
    \[
        \frac{x^\gamma}{LT(x^\alpha f)} \cdot (x^\alpha f) = x^\gamma \frac{f}{LT(f)}, \quad 
        \frac{x^\gamma}{LT(x^\beta g)} \cdot (x^\beta g) = x^\gamma \frac{g}{LT(g)}.
    \]
    Therefore,
    \[
        S(x^\alpha f, x^\beta g) = x^\gamma \left(\frac{f}{LT(f)} - \frac{g}{LT(g)}\right) = x^\gamma S(f, g),
    \]
    showing that $x^\gamma$ is a monomial.  
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 13, breakable]
    Let $I \subseteq k[x_1, \ldots, x_n]$ be an ideal,
    and let $G$ be a grobner basis of $I$.
    \begin{enumerate}
        \item Show that $\overline{f}^G = \overline{g}^G$ if and only if $f - g \in I$. Hint: See Exercise 1.
        \item Use Exercise 1 to show that 
        \[\overline{f + g}^G = \overline{f}^G + \overline{g}^G.\]
        \item Deduce that 
        \[\overline{fg}^G = \overline{\overline{f}^G \cdot \overline{g}^G}^G.\]
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose $\overline{f}^G = \overline{g}^G$.  
    By Exercise 1, write $f = t + r$ and $g = t' + r$.
    with $t, t' \in I$ and $r = \overline{f}^G = \overline{g}^G$.  
    Then $f - g = (t + r) - (t' + r) = t - t' \in I$.

    Conversely, suppose $f - g \in I$. Then by Exercise 1 
    we can write $f = t + r$ and $g = t' + r'$ where $t, t' \in I$ and $r, r' \in k[x_1, \ldots, x_n]$.
    Then $f - g = (t - t') + (r - r') \in I$.
    Then we see  $(f - g) - (t - t') = r - r' \in I$.
    Now since $LT(g_i) \nmid r, r'$ for any $i$,
        we must have $r - r' = 0$, thus $r = r'$.
    Thus $\overline{f}^G = \overline{g}^G$.
\end{proof}

\begin{proof}
    By Exercise 1, we have $f = t_1 + r_1$ and $g = t_2 + r_2$
    where $t_1, t_2 \in I$ and $r_1 = \overline{f}^G, \quad r_2 = \overline{g}^G$.
    Then $f + g = (t_1 + r_1) + (t_2 + r_2) 
              = (t_1 + t_2) + (r_1 + r_2)$.
    Since $I$ is an ideal and $t_1, t_2 \in I$, we have $t_1 + t_2 \in I$.
    Thus $f + g = t + (r_1 + r_2)$
    for some $t \in I$. Therefore by Exercise 1, $\overline{f+g}^G = r_1 + r_2 = \overline{f}^G + \overline{g}^G$.
\end{proof}

\begin{proof}
    By Exercise 1, $f = t_1 + r_1$ and $g = t_2 + r_2$
    where $t_1, t_2 \in I$ and  $r_1 = \overline{f}^G$ and $r_2 = \overline{g}^G$.
    Then $fg = (t_1 + r_1)(t_2 + r_2)
           = t_1t_2 + t_1r_2 + t_2r_1 + r_1r_2$.
    Since $I$ is an ideal, $t_1t_2 + t_1r_2 + t_2r_1 \in I$.
    Thus $fg = t + r_1r_2$.
    for some $t \in I$. 
    Therefore $\overline{fg}^G = \overline{r_1r_2}^G$.
    Substituting $r_1 = \overline{f}^G$ and $r_2 = \overline{g}^G$, 
        we obtain $\overline{fg}^G = \overline{\overline{f}^G \cdot \overline{g}^G}^G$.
\end{proof}

\subsection{Buchberger's Algorithm}

\newpage
\begin{tcolorbox}[title=Problem 4, breakable]
    Use the result of Exercise 7 of 4
    to give an alternate proof that 
    Buchberger's algorithm will always terminate after 
    a finite number of steps.
\end{tcolorbox}

\begin{theorem}[Exercise 7]
    Dickson's Lemma is equivalent to the following statement: given a 
    nonempty subset $A \subseteq \mathbb{Z}_{\ge 0}^n$, there are finitely many 
    elements $\alpha(1), \ldots, \alpha(s) \in A$ such that 
    for every $\alpha \in A$, there exists some $i$ and some $\gamma \in \mathbb{Z}_{\ge 0}^n$ such that $\alpha = \alpha(i) + \gamma$.
\end{theorem}

\begin{theorem}[Dickson's Lemma]
    Let $I = \langle x^\alpha \mid \alpha \in A \rangle \subseteq k[x_1, \ldots, x_n]$
    be a monomial ideal. Then I can be written in the form 
    $I = \langle x^{\alpha(1)}, \ldots, x^{\alpha(s)} \rangle$, where 
    $\alpha(1), \ldots, \alpha(s) \in A$. In particular $I$ has a finite basis.
\end{theorem}

\begin{proof}
    For contradiction, suppose Buchberger's algorithm does not terminate.
    Let $G = \{x^{\beta(1)}, x^{\beta(2)}, \ldots\}$ be the set of generated remainders.
    Take an arbitrary element $x^{\beta(i)} \in G$.
    By the construction of the algorithm, for all $x^{\beta(j)} \in G$ such that $i \ne j$,
        $x^{\beta(j)} \nmid x^{\beta(i)}$.
    Thus there does not exist $\gamma \in \mathbb{Z}_{\ge 0}^n$ such that 
        $\beta(i) = \beta(j) + \gamma$,
        contradicting the statement of Exercise 7 (Dickson's Lemma).
\end{proof}

\begin{tcolorbox}[title=Problem 5, breakable]
    Let $G$ be a Grobner basis of an ideal $I$
    with the property that $LC(g) = 1$ for all $g \in G$.
    Prove that $G$ is a minimal Grobner basis if and only if
    no proper subset of $G$ is a grobner basis of $I$.
\end{tcolorbox}

\begin{proof}
    Suppose $G$ is a minimal Grobner basis.
    For contradiction, suppose there exists a Grobner basis $G'$ such that $G' \subset G$.
    Since $G \setminus G' \ne \emptyset$, let $x \in G \setminus G'$. 
    We must have $x = \sum_{i = 1}^{n} h_i g_i$ where $g_i \in G'$ and $h_i \in k[x_1, \ldots, x_n]$,
        contradicting that $G$ is a minimal Grobner basis.

    Conversely, suppose no proper subset of $G$ is a Grobner basis of $I$.
    For contradiction, suppose $G$ is not a minimal Grobner basis.
    Then there exists $p \in G$ such that $LT(p) \in \langle LT(G \setminus \{p\}) \rangle$.
    Let $G' = G \setminus \{p\}$. By Lemma 3, $G'$ is a Grobner basis and $G' \subset G$, which is a contradiction.
\end{proof}

\begin{tcolorbox}[title=Problem 6, breakable]
    The minimal basis of a monomial ideal was introduced 
    in Proposition 7 of 4. Show that a Grobner basis 
    of $I$ is minimal if and only if $LC(g) = 1$ for all 
    $g$ in $G$ and $LT(G)$ is the minimal basis of the 
    monomial ideal $\langle LT(I) \rangle$.
\end{tcolorbox}

\begin{proof}
    Suppose $G$ is a minimal Grobner basis.
    By definition, for all $g \in G$, $LC(g) = 1$.
    For contradiction, suppose $LT(G)$ is not the minimal basis of the monomial ideal $\langle LT(I) \rangle$.
    Then there exist $g_i, g_j \in G$ with $i \ne j$ such that $LT(g_i) \mid LT(g_j)$, contradicting the minimality of $G$.

    Conversely, suppose $LC(g) = 1$ for all $g \in G$ and $LT(G)$ is the minimal basis of the monomial ideal 
        $\langle LT(I) \rangle$.
    For contradiction, suppose $G$ is not a minimal Grobner basis.
    Then there exist $g_i, g_j \in G$ where $i \ne j$ such that $LT(g_i) \mid LT(g_j)$.
    But since $LT(g_i), LT(g_j) \in LT(G)$ we have $LT(g_i) \mid LT(g_j)$, contradicting that $LT(G)$ is the minimal basis of the monomial ideal 
        $\langle LT(I) \rangle$.
\end{proof}

\newpage
\begin{tcolorbox}[title=Problem 7, breakable]
    Fix a monomial order, and let $G$ and $\tilde{G}$
    be minimal Grobner bases for the ideal $I$.
    \begin{enumerate}
        \item Prove that $LT(G) = LT(\tilde{G})$.
        \item Conclude that $G$ and $\tilde{G}$ have the same number of elements.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
\end{proof}

\begin{tcolorbox}[title=Problem 8, breakable]
    Develop an algorithm that produces a reduced Grobner 
    basis (see Definition 4) for an ideal $I$,
    given as input an arbitrary Grobner basis for $I$.
    Prove that your algorithm works.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 10, breakable]
    Let $A = (a_{i j})$ be an $n \times m$ matrix with entries in $k$
    and let $f_i = a_{i 1} x_1 + \cdots + a_{i m} x_m$ be the linear 
    polynomials in $k[x_1, \ldots, x_m]$ determined by the rows of $A$.
    Then we get the ideal $I = \langle f_1, \ldots, f_n \rangle$. We 
    will use lex order with $x_1 > \cdots > x_m$. Now let 
    $B = (b_{i j})$ be the reduced row echelon matrix determined by $A$ and let 
    $g_1, \ldots g_t$ be the linear polynomials coming from the nonzero 
    rows of $B$ (so that $t \le n$). We want to prove that $g_1, \ldots, g_t$
    form the reduced Grobner basis of $I$.
    \begin{enumerate}
        \item Show that $I = \langle g_1, \ldots, g_t \rangle$.
        Hint: Show that the result of applying a row operation to 
        $A$ gives a matrix whose rows generate teh same ideal.
        \item Use Theorem 6 to show that $g_1, \ldots, g_t$ form a Grobner basis of $I$.
        Hint: If the leading $1$ in the $i$th row of $B$ is in the $s$th column,
        we can write $g_i = x_s + C$, where $C$ is a linear polynomial involving 
        none of the variables corresponding to leading $1$'s.
        If $g_j = x_l + D$ is written similiarly, then you need to divide 
        $S(g_i, g_j) = x_l C - x_s D$ by $g_1, \ldots, g_t$. Note that you 
        will use only $g_i$ and $g_j$ in the division.
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 12, breakable]
    Fix $F = \{f_1, \ldots, f_s\}$ and let $r = \overline{f}^F$.
    Since dividing $f$ by $F$ gives $r$ as remainder, adding $r$
    to the polynomials we divide by should reduce the remainder 
    to zero. In other words, we should have 
    $\overline{f}^{F \cup \{r\}} = 0$ when $r$ comes last. Prove this as follows.
    \begin{enumerate}
        \item When you divide $f$ by $F \cup \{r\}$, consider the first place 
        in the division algorithm where the intermediate dividend $p$ has leading 
        term not divisible by any $LT(f_i)$. Explain why $LT(p) = LT(r)$ and 
        why the next intermediate dividend is $p - r$.
        \item From here on in the division algorithm, explain why the leading term 
        of the intermediate dividend is always divisible by one of the 
        $LT(f_i)$. Hint: If this were false, consider the first time it fails.
        Remember that the terms of $r$ are not divisible by any $LT(f_i)$.
        \item Conclude that the remainder is zero, as desired.
        \item Given an alternate proof of $\overline{f}^{F \cup \{r\}} = 0$ using 
        Exercise 11 of 3.
    \end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 13, breakable]
    In the discussion following the proof of Theorem 2, we commented that 
    if $\overline{S(f, g)}^{G'} = 0$, then remainder stays zero when we enlarge $G'$.
    More generally, if $\overline{f}^F = 0$ and $F'$ is obtained from $F$
    by adding elements at the end, then $\overline{f}^{F'} = 0$. Prove this.
\end{tcolorbox}

\begin{tcolorbox}[title=Problem 14, breakable]
    Suppose we have $n$ points $V = \{(a_1, b_1), \cdots, (a_n, b_n)\} \subseteq k^2$
    where $a_1, \ldots, a_n$ are distinct. This exercise will study the 
    Langrange interpolation polynomial defined by 
    \[h(x) = \sum_{i = 1}^{n} b_i \prod_{j \ne 1} \frac{x - a_j}{a_i - a_j} \in k[x].\]
    We will also explain how $h(x)$ related to the reduced Grobner basis of 
    $\textbf{I}(V) \subseteq k[x, y]$.
    \begin{enumerate}
        \item Show that $h(a_i) = b_i$ for $i = 1, \ldots, n$ and explain why $h$ has degree $\le n - 1$.
        \item Prove that $h(x)$ is the unique polynomial of degree $\le n - 1$ satisfying $h(a_i) = b_i$ for $i = 1, \ldots, n$.
        \item Prove that $\textbf{I}(V) = \langle f(x), y - h(x) \rangle$, where $f(x) = \prod_{i = 1}^{n} (x - a_i)$. Hint: Divide $g \in \textbf{I}(V)$ by $f(x)$, $y - h(x)$ using lex order with $y > x$.
        \item Prove that $\{f(x), y - h(x)\}$ is the reduced Grobner basis for $\textbf{I}(V) \subseteq k[x, y]$ for lex order with $y > x$. 
    \end{enumerate}
\end{tcolorbox}