\begin{tcolorbox}[title=Problem 1, breakable]
    Prove Theorem $5.1$: A polynomial in $\mathbb{Q}[x]$
    of degree greater than zero is either irreducible
    or the product of irreducibles.
\end{tcolorbox}

\begin{proof}
    Let $f$ be a polynomial with degree greater than $0$.
    We proceed by induction on the degree of $f$.

    (\textbf{Base Case}) A polynomial of degree one is irreducible.

    (\textbf{Induction Step}) 
    Suppose the theorem holds for all polynomials of degree $m < n$.
    If $f$ of degree $n$ is irreducible, we are done.
    Suppose $f$ is not irreducible; then $f = l \cdot g$ where $l, g \in \mathbb{Q}[x]$ 
    and $\deg(l), \deg(g) < \deg(f)$.
    By the induction hypothesis, $l$ and $g$ can be expressed as a product of irreducible polynomials.
    Therefore, $f$ can also be expressed as a product of irreducibles.
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
    Prove Theorem $5.2$: A polynomial in $\mathbb{Q}[x]$
    is irreducible if and only if it is prime.
\end{tcolorbox}

\begin{proof}
    Let $f$ be an arbitrary polynomial in $\mathbb{Q}[x]$.

    ($\rightarrow$) Suppose $f$ is irreducible and $f \mid l g$.
    Furthermore, suppose $f$ does not divide $l$.
    We must show that $f \mid g$.
    Suppose that $d$ is a common divisor of $f$ and $l$.
    Then, because $f$ is irreducible, $d$ must 
        be equal to $f$ or a unit.
    Because $f$ does not divide $l$, it must be that    
        $\gcd(f, l) = 1$.
    So by the GCD identity there exist $x, y \in \mathbb{Q}[x]$
        such that $1 = l x + f y$. 
    Multiplying both sides by $g$ gives
        \[ g = l g x + f g y. \]
    Since $f$ divides both terms on the right-hand side,
        it follows that $f \mid g$, as required.

    ($\leftarrow$) Suppose $f$ is prime.
    Furthermore, suppose $f$ has been factored as $f = l g$.
    Then $f \mid l g$, and so, without loss of generality,
        $f \mid l$.
    Thus, $l = f x$, and so $f = f x g$. 
    Cancelling $f$ gives $1 = x g$, and so both $x$ and $g$
        must be degree $0$ polynomials.
    This shows that the factorization $f = l g$
        is trivial, as required.
\end{proof}

\begin{tcolorbox}[title=Problem 3, breakable]
    Prove Corollary $5.3$: If an irreducible polynomial
    in $\mathbb{Q}[x]$ divides a product $f_1 f_2 f_3 \ldots f_n$,
    then it divides one of $f_i$.
\end{tcolorbox}

\begin{proof}
    Let $f$ be an irreducible polynomial in $\mathbb{Q}[x]$.
    Furthermore, suppose $f \mid f_1 f_2 f_3 \ldots f_n$.
    We proceed by induction on $n$.

    (\textbf{Base Case})  
    If $f \mid f_1 f_2$, then by the definition of being prime, 
    $f \mid f_1$ or $f \mid f_2$.

    (\textbf{Induction Step})  
    Assume the statement holds for $n - 1$; that is, 
    if $f \mid f_1 f_2 \cdots f_{n-1}$, then $f \mid f_i$ for some $i < n$.  
    Now suppose $f \mid f_1 f_2 \cdots f_{n-1} f_n$.  
    Let $c = f_1 f_2 \cdots f_{n-1}$, so $f \mid c f_n$.  
    By the definition of being prime, $f \mid c$ or $f \mid f_n$.  
    By the induction hypothesis, if $f \mid c$, then $f \mid f_i$ for some $i < n$.  
    Thus, in either case, $f$ divides one of the $f_i$.
\end{proof}

\begin{tcolorbox}[title=Problem 4, breakable]
    Use Gauss's Lemma to determine which of the following 
    are irreducible in $Q[x]$:
    \[4x^3 + x - 2, 3x^3 - 6x^2 + x - 2, x^3 + x^2 + x - 1\]
\end{tcolorbox}

\begin{proof}
    If $f(x) = 4x^3 + x - 2$ can be factored then one of 
        the factors is of the form $(ax + b)$
        where $a, b \in \mathbb{Z}$.
    The only possible factors are 
        $(4x \pm 1)$, $(4x \pm 2)$, $(2x \pm 2)$, $(2x \pm 1)$, $(x \pm 2)$, $(x \pm 1)$.
    This implies roots of $\pm \frac{1}{4}$, $\pm \frac{1}{2}$, $\pm 2$, $\pm 1$.
    By inspection this is not the case.
    Since $f$ is irreducible in $\mathbb{Z}[x]$ by Gauss's Lemma $f$ is irreducible in $Q[x]$.
\end{proof}

\begin{proof}
    Let $f(x) =  3x^3 - 6x^2 + x - 2$.
    By inspection $x = 2$ is a root thus by the Root Theorem 
        $f$ is not irreducible in $\mathbb{Q}[x]$.
\end{proof}

\begin{proof}
    If $f(x) =  x^3 + x^2 + x - 1$ can be factored then one of 
        the factors is of the form $ax + b$.
    The only possible factor is $(x \pm 1)$.
    By inspection this is not the case.
    Since $f$ is irreducible in $\mathbb{Z}[x]$ by Gauss's Lemma $f$ is irreducible in $Q[x]$.
\end{proof}

\begin{tcolorbox}[title=Problem 6, breakable]
    Prove the Rational Root Theorem $5.6$.
\end{tcolorbox}

\begin{theorem}[Ration Root Theorem $5.6$]
    Suppose that $f = a_0 + a_1 x + \cdots + a_n x^n$
    is a polynomial in $\mathbb{Z}[x]$, and $\frac{p}{q}$ is 
    a rational root; that is, $p$ and $q$ are integers, $q \ne 0$,
    and $f\left(\frac{p}{q}\right) = 0$. We may as well assume also that 
    $gcd(p, q) = 1$. Then $q$ divides the integer $a_n$, and 
    $p$ divides $a_0$.
\end{theorem}

\begin{proof}
    We first show $q \mid a_n$.
    Plugging in $\frac{p}{q}$ shows 
    \[f\left(\frac{p}{q}\right) = a_0 + a_1 \frac{p}{q} + \cdots + a_n \left(\frac{p}{q}\right)^n = 0.\]
    Then multiplying through by $q^n$ shows 
    \[a_0 q^n + a_1 p q^{n - 1} + a_2 p^2 q^{n-2} + \cdots + a_n p^n = 0\]
    Solving for $a_n p^n$ shows 
    \[a_n p^n = - a_0 q^n - a_1 p q^{n - 1} - a_2 p^2 q^{n-2} - \cdots - a_{n - 1} p^{n-1} q\]
    Then factoring out $q$ shows 
    \[a_n p^n = -q(a_0 q^{n-1} + a_1 p q^{n - 2} + \cdots + a_{n - 1} p^{n-2})\]
    Since $\gcd(p, q) = 1$, it follows that $q \not \mid p^n$.
    Thus $q \mid a_n$.
    We now show $p \mid a_0$.
    In the previous part it was shown that 
    \[a_0 q^n + a_1 p q^{n - 1} + a_2 p^2 q^{n-2} + \cdots + a_n p^n = 0\]
    Solving for $a_0 q^n$ shows 
    \[a_0 q^n = -(a_1 p q^{n - 1} + a_2 p^2 q^{n-2} + \cdots + a_n p^n)\]
    We can then factor out $p$ so 
    \[a_0 q^n = -p(a_1 q^{n - 1} + a_2 p q^{n-2} + \cdots + a_n p^{n - 1})\]
    Since $\gcd(p, q) = 1$, it follows that $p \not \mid q^n$.
    Thus $p \mid a_0$.
\end{proof}

\begin{tcolorbox}[title=Problem 7, breakable]
    Use the Rational Root Theorem $5.6$ to factor 
    \[2x^3 - 17x^2 - 10x + 9\]
\end{tcolorbox}

\textbf{Solution:}

Using the Root Theorem we find the following possible roots
\[\text{Candidates = } \{\pm \frac{9}{1},\pm \frac{9}{2},\pm \frac{3}{1},\pm \frac{3}{2},\pm \frac{1}{1},\pm \frac{1}{2}\}\]
Inspection shows that $9$ and $\frac{1}{2}$ are roots.
Dividing $2x^3 - 17x^2 - 10x + 9$ by $(x - 9)(x - \frac{1}{2})$ gives us $(2x + 2)$. Thus 
\[2x^3 - 17x^2 - 10x + 9 = (x - 9)(x - \frac{1}{2})(2x + 2)\]

\begin{tcolorbox}[title=Problem 9, breakable]
    Use the Rational Root Theorem $5.6$ (applied to $x^3 - 2$)
    to argue that $\sqrt[3]{2}$ is irrational.
\end{tcolorbox}

\begin{proof}
    For contradiction, suppose $\sqrt[3]{2}$ is a rational root 
        for $x^3 - 2$.
    Since $\sqrt[3]{2}$ is rational it can be expressed as $\frac{a}{b}$
        where $a, b \in \mathbb{Z}$ and $\gcd(a, b) = 1$.
    By the Rational Root Theorem $5.6$
        it follows that $a \mid -2$ and $b \mid 1$.
    There exists $k_1, k_2 \in \mathbb{Z}$ such that 
        $-2 = a k_1$ and $1 = b k_2$.
    Then 
    \[\sqrt[3]{2} = \frac{\frac{-2}{k_1}}{\frac{1}{k_2}} = \frac{-2 k_2}{k_1}\]
    It follows that $2 = \frac{-8 k_2^3}{k_1^3}$. Multiplying by $k_1^3$
    and dividing by $2$ shows that $k_1$ is even.
    Rewriting $k_1 = 2 k_3$ where $k_3 \in \mathbb{Z}$  
        we get 
        \[2 = \frac{-8 k_2^3}{(2k_3)^3} 
            \iff 2 (2 k_3)^3 = -8 k_2^3
            \iff 16 k_3^3 = -8 k_2^3.\]
    Dividing by $8$ shows that $k_2$ is even, contradicting 
        that $\gcd(a, b) = 1$.
\end{proof}

\begin{proof}
    For contradiction, suppose $\sqrt[3]{2}$ is a rational root 
    of $x^3 - 2$. Then we can write $\sqrt[3]{2} = \frac{a}{b}$, 
    where $a, b \in \mathbb{Z}$, $\gcd(a, b) = 1$.  
    By the Rational Root Theorem $5.6$ any rational root $\frac{a}{b}$ 
        must satisfy $a \mid -2$ and $b \mid 1$.  
    Thus the only possible rational roots are 
    \[
        \pm 1, \quad \pm 2.
    \]  
    Inspection shows that no combination works.
    Thus  $\sqrt[3]{2}$ is irrational.
\end{proof}

\begin{tcolorbox}[title=Problem 10, breakable]
    Suppose that $\alpha$ is a real number (which might 
    not be rational), and suppose that it is a root of a 
    polynomial $p \in \mathbb{Q}[x]$; that is,
    $p(\alpha) = 0$. Suppose further that $p$ is irreducible
    in $\mathbb{Q}[x]$. Prove that $p$ has a minimal degree in the 
    set 
    \[\mathcal{F} = \{f \in \mathbb{Q}[x] : f(\alpha) = 0 \text{ and } f \ne 0\}\]
\end{tcolorbox}

\begin{proof}
    Suppose there exists $g \in \mathbb{Q}[x]$
        such that $\deg(g) < \deg(p)$.
    By the Division Theorem there exists $q, r \in \mathbb{Q}[x]$
        such that $p = g q + r$ and $\deg(r) < \deg(g)$.
    Then 
    \[0 = p(\alpha) = g(\alpha)q(\alpha) + r(\alpha) = 0 + r(\alpha) = r(\alpha),\]
    thus $r(\alpha) = 0$. 

    Either $\deg(r) = 0$ or $\deg(r) > 0$.
    Suppose $\deg(r) = 0$, then since $r(\alpha) = 0$, $r$ is the zero polynomial.
    Since $\deg(p) = \deg(g) + \deg(q)$ and $\deg(g) < \deg(p)$,
        it follows that $\deg(q) > 0$.
    Thus $p$ has been factored into two polynomials with degree 
        greater than $0$, contradicting the irreducibility of $p$.

    Now, suppose $\deg(r) > 0$. We can repeatedly apply the Division Theorem
        to form a sequence of decreasing remainders by their degrees.

    For example, continuing where we left off, we divide $p$ by $r$
        and by the Division Theorem obtain $r_1, q_1 \in \mathbb{Q}[x]$
        such that 
    \[p = rq_1 + r_1.\]
    Then $\deg(r_1) < \deg(r) < \deg(g)$.

    If at any point a remainder $r$ is a scalar, it must be the 
        zero polynomial and we contradict the irreducibility of $p$.
    On the other hand, if the sequence never ends, then we contradict the finiteness of
        the degree of $p$.
\end{proof}

\begin{tcolorbox}[title=Problem 12, breakable]
    Construct polynomials of arbitrarily large degree,
        which are irreducible in $\mathbb{Q}[x]$.
\end{tcolorbox}

\textbf{Solution}
\[\mathcal{F} = \{f \mid f = x^n - 2\}\]
By Eisenstein's Cirterion all $f \in \mathcal{F}$
    are irreducible in $\mathbb{Z}[x]$.
By Gauss's Lemma they are irreducible in $\mathbb{Q}[x]$.

\begin{tcolorbox}[title=Problem 13, breakable]
    (a) Prove that the equation $a^2 = 2$ has no ration solutions;
        that is, prove that $\sqrt{2}$ is irrational. (This part is a 
        repeat of exercise $2.14$.)

    (b) Generalize part $a$,k by proving that $a^n = 2$ has no rational 
        solutions, for all positive integers $n \ge 2$.
\end{tcolorbox}

\begin{proof}
    Let $p = 2$ and apply Eisenstein's Criterion to $a^2 - 2 = 0$.
    Clearly $2$ is prime, $2 \mid -2$, $2 \nmid 1$, and $2^2 \nmid -2$.
    Thus there is no rational root.
\end{proof}

\begin{proof}
    Same logic as before.
\end{proof}

\begin{tcolorbox}[title=Problem 14, breakable]
    Let $f \in \mathbb{Z}[x]$ and $n$ an integer.
    Let $g$ be the polynomial defined by $g(x) = f(x + n)$.
    Prove that $f$ is irreducible in $\mathbb{Z}[x]$ if and 
    only if $g$ is irreducible in $\mathbb{Z}[x]$.
\end{tcolorbox}

\begin{proof}
    Let $y = x - n$, so that $f(x + n) = g(y) = g(x - n)$.

    ($\rightarrow$) Suppose $f$ is irreducible in $\mathbb{Z}[x]$.
    For contradiction suppose $g$ is reducible: $g = p l$ where $p, l \in \mathbb{Z}[x]$.
    Then
    \[
        f(x) = g(x - n) = p(x - n) l(x - n),
    \]
    contradicting the irreducibility of $f$.
    Thus $g$ is irreducible in $\mathbb{Z}[x]$.

    ($\leftarrow$) Suppose $g$ is irreducible in $\mathbb{Z}[x]$.
    For contradiction suppose $f$ is reducible: $f = p l$ where $p, l \in \mathbb{Z}[x]$.
    Then
    \[
        g(x) = f(x + n) = p(x + n) l(x + n),
    \]
    contradicting the irreducibility of $g$.
    Thus $f$ is irreducible in $\mathbb{Z}[x]$.
\end{proof}

\begin{tcolorbox}[title=Problem 15, breakable]
    (a) Apply Eisenstein's criterion $5.7$ to check that the 
        following polynomials are irreducible
        \[5x^3 - 6x^2 + 2x - 14 \text{ and } 4x^5 + 5x^3 - 15x + 20\]

    (b) Make the substition $x = y + 1$ to the polynomial $x^5 + 5x + 4$
        that appears in Example $5.1$. Show that the resulting polynomial
        is irreducible.

    (c) Use the same technique as in part b to find a substitution 
        $x = y + m$ so you can conclude the polynomial
        \[x^4 + 6x^3 + 12x^2 + 10x + 5\]
        is irreducible.

    (d) Show that this technique works in general: Prove that if 
        $f(x) \in \mathbb{Z}[x]$, then $f(x)$ is irreducible if 
        and only if $f(y + m)$ is.
\end{tcolorbox}

\textbf{Solution (a):}
Consider $2 \nmid 5$. Also $2 \mid -6,  2, -14$.
Finally $2^2 = 4 \nmid -14$ satisfying parts a, b, c of 
Eisenstein's criterion respectively. Thus $5x^3 - 6x^2 + 2x - 14$
is irreducible in $\mathbb{Z}[x]$.

Consider $5 \nmid 4$. Also $5 \mid 5,  -15, 20$.
Finally $5^2 = 25 \nmid 20$ satisfying parts a, b, c of 
Eisenstein's criterion respectively. Thus $4x^5 + 5x^3 - 15x + 20$
is irreducible in $\mathbb{Z}[x]$.

\textbf{Solution (b):}
Substituting $x = y + 1$ into $x^5 + 5x + 4$ gives
\[
(y + 1)^5 + 5(y + 1) + 4 = y^5 + 5y^4 + 10y^3 + 10y^2 + 10y + 10.
\]
Consider $5 \nmid 1$. Also $5 \mid 5, 10, 10, 10, 10$. 
Finally $5^2 = 25 \nmid 10$ satisfying parts a, b, c of 
Eisenstein's criterion respectively. 
Thus the polynomial is irreducible in $\mathbb{Z}[y]$, 
    and so $x^5 + 5x + 4$ is irreducible in $\mathbb{Z}[x]$.

\textbf{Solution (c):}
Substituting $x = y + 1$ into $x^4 + 6x^3 + 12x^2 + 10x + 5$ gives
\[
(y + 1)^4 + 6(y + 1)^3 + 12(y + 1)^2 + 10(y + 1) + 5 = y^4 + 10y^3 + 36y^2 + 56y + 34.
\]
Consider $2 \nmid 1$. 
Also $2 \mid 10, 36, 56, 34$. 
Finally $2^2 = 4 \nmid 34$ satisfying parts a, b, c of Eisenstein's criterion respectively. 
Thus $y^4 + 10y^3 + 36y^2 + 56y + 34$ is irreducible in $\mathbb{Z}[y]$.

\begin{proof}
    ($\longrightarrow$) Let $x = y + m$.  
    Suppose $f(x)$ is irreducible.  
    For contradiction, suppose $f(y + m)$ is reducible.  
    Thus $f(y + m) = g(y) \, l(y)$ for some 
    $g(y), l(y) \in \mathbb{Z}[y]$.  
    But $x = y + m$, so $f(x) = g(x - m) \, l(x - m)$.  
    Thus $f(x)$ is reducible, which is a contradiction.

    ($\longleftarrow$) Let $x = y + m$.  
    Suppose $f(y + m)$ is irreducible.  
    For contradiction, suppose $f(x)$ is reducible.  
    Thus $f(x) = g(x) \, l(x)$ for some $g(x), l(x) \in \mathbb{Z}[x]$.  
    But $x = y + m$, so $f(y + m) = g(y + m) \, l(y + m)$.  
    Thus $f(y + m)$ is reducible, which is a contradiction.
\end{proof}

\begin{tcolorbox}[title=Problem 16, breakable]
    Prove Theorem $5.7$ (Eisenstein's criterion).
\end{tcolorbox}

\begin{theorem}[Eisenstein's Criterion]
    Suppose that $f \in \mathbb{Z}[x]$,
        and 
    \[f = a_0 + a_1 x + a_2 x^2 + \cdots +  a_n x^n\]
    Let $p$ be a prime integer, and suppose that
    \begin{enumerate}
        \item $p$ divides $a_k$, for $0 \le k < n$,
        \item $p$ does not divide $a_n$, and 
        \item $p^2$ does not divide $a_0$
    \end{enumerate}
    Then $f$ is irreducible in $\mathbb{Z}[x]$.
\end{theorem}

\begin{proof}
    Suppose for contradiction that $f$ is reducible. Then there exist 
    polynomials $g, l \in \mathbb{Z}[x]$ such that 
    $f = g l$:
    \[
    f = a_0 + a_1 x + a_2 x^2 + \cdots +  a_n x^n = g l.
    \]
    Now $p$ either divides the constant term of $g$ or $l$;
    otherwise it would not divide the constant term of $f$.  
    Furthermore, if $p$ divides the constant term of both, then   
    $p^2$ would divide the constant term of $f$, which is impossible.  
    Suppose w.l.o.g. that $p$ divides the constant term of $g$ 
    and $p$ does not divide the constant term of $l$.  
    The constant term of $l$ cannot be zero; otherwise the constant term of $f$ would be zero.

    Now consider the first coefficient $b_j$ of $g$ with $j>0$ that is 
    not divisible by $p$. This term exists since coefficientof 
    largest degree term of $g$ is not divisible by $p$.
    Let $c$ be the constant term of $l$, so $p \nmid c$. 
    Then the product $b_j c$ contributes to the coefficient $a_j$ of $f$. 
    Since $p \nmid b_j$ and $p \nmid c$, it follows that $p \nmid b_j c$. 

    Any other contributions to $a_j$ come from products of terms of $g$ and $l$ 
        where at least one factor is divisible by $p$, so those terms are divisible by $p$. 
    Thus the coefficient $a_j$ of $f$ is
    \[
    a_j = b_j c + (\text{terms divisible by } p),
    \]
    which is not divisible by $p$, contradicting the assumption that $p$ divides $a_k$ for all $0 \le k < n$.
\end{proof}

\begin{tcolorbox}[title=Problem 17, breakable]
    Let $p$ be a positive prime integer. Then the polynomial
    \[\phi_p = \frac{x^p - 1}{x - 1}\]
    is called a \textbf{cyclotomic polynomial}.

    (a) Write out, in the usual form for a polynomial, the cyclotomic
        polynomials for the first three primes.

    (b) Prove that all cyclotomic polynomials $\phi_p$ are irreducible
        over $\mathbb{Z}[x]$, using Eisenstein's criterion $5.7$ 
        and Exercise $15d$ for $m = 1$.
\end{tcolorbox}

\textbf{Solution (a):}
\[p = 2, \frac{x^2 - 1}{x - 1} = \frac{(x - 1)(x + 1)}{x - 1} = x + 1\]
\[p = 3, \frac{x^3 - 1}{x - 1} = \frac{(x - 1)(x^2 + x + 1)}{x - 1} = x^2 + x + 1\]
\[p = 5, \frac{x^5 - 1}{x - 1} = \frac{(x - 1)(x^4 + x^3 + x^2 + x + 1)}{x - 1} = x^4 + x^3 + x^2 + x + 1\]

\begin{proof}
    Let $x = y + 1$. Let $p$ be an arbitrary prime. Then consider 
    \[
        \frac{(y + 1)^p - 1}{(y + 1) - 1} = \frac{(y + 1)^p - 1}{y}
    \]
    We can re-express the numerator using the binomial theorem
    \[
        (y + 1)^p = \sum_{k = 0}^p \binom{p}{k} y^{p - k} 1^k = \sum_{k = 0}^p \binom{p}{k} y^{p - k}
    \]
    Substituting into the fraction gives 
    \[
        \frac{(y + 1)^p - 1}{y} = \frac{\sum_{k=0}^p \binom{p}{k} y^{p-k} - 1}{y}
    \]
    Multiplying numerator and denominator by $y^{-1}/y^{-1}$ gives
    \[
        \frac{\sum_{k=0}^p \binom{p}{k} y^{p-k} - 1}{y} \cdot \frac{y^{-1}}{y^{-1}} 
            = \sum_{k=0}^p \binom{p}{k} y^{p - k - 1} - y^{-1}
    \]
    Now we re-express this summation and extract the cases $k = 0, p-1, p$ to show
    \[
        \sum_{k = 0}^p \binom{p}{k} y^{p - k - 1} - y^{-1} 
            = y^{p - 1} + \sum_{k = 1}^{p-2} \binom{p}{k} y^{p - k - 1} + \binom{p}{p-1} y^0 + \binom{p}{p} y^{-1} - y^{-1} 
            = y^{p - 1} + \sum_{k = 1}^{p-2} \binom{p}{k} y^{p - k - 1} + \binom{p}{p-1}
    \]
    Now $y^{p - 1}$ is the term with the highest degree and its coefficient is $1$.
    Clearly $p \nmid 1$, satisfying part (a) of Eisenstein's criterion.
    Furthermore, by Chapter 2 Problem 19, since $p$ is a positive prime integer 
    and $k$ is an integer with $1 \le k \le p - 1$, we have $p \mid \binom{p}{k}$.
    Additionally, $p \mid \binom{p}{p-1} = p$. Thus part (b) of Eisenstein's criterion is satisfied.
    Now, the constant term of \(\frac{(y+1)^p - 1}{y}\) is $p$.  
    Since \(a_0 = p < p^2\), we have $p^2 \nmid a_0$, satisfying part (c) of Eisenstein's criterion.
    By Problem 15 part d, it follows that all cyclotomic polynomials $\phi_p$ are irreducible
        over $\mathbb{Z}[x]$.
\end{proof}


