\subsection{Alternate Multilinear Forms}

\begin{tcolorbox}[title=Problem 1, breakable]
    Let $f \in \mathcal{A}(V)$ then $f(x_1, \ldots, x_n) = 0$
    whenever $x_1, \ldots, x_n$ are linearly dependent.
\end{tcolorbox}

\begin{proof}
    Suppose $x_1, \ldots, x_n$ are linearly dependent.
    There exists scalars $c_1, \ldots, c_n$, not all zero, such that 
    $\sum c_i x_i = 0$. Suppose WLOG $c_j \ne 0$ then 
    \[x_j = -\sum_{i \ne j} \frac{c_i}{c_j} x_i.\]
    Then 
    \[
    f(x_1, \ldots, x_j, \ldots, x_n)
    =
    f\left(x_1, \ldots, -\sum_{i \ne j} \frac{c_i}{c_j} x_i, \ldots, x_n\right).
    \]
    By multilinearity,
    \[
    f(x_1, \ldots, x_n)
    =
    -\sum_{i \ne j} \frac{c_i}{c_j}
    f(x_1, \ldots, x_i, \ldots, x_n),
    \]
    where in each term $x_i$ appears in both the $i$th and $j$th positions.
    Since $f$ is alternating, each such term is $0$. Thus
    \[
    f(x_1, \ldots, x_n)=0.
    \]
\end{proof}


\begin{tcolorbox}[title=Problem 2, breakable]
\begin{enumerate}[(i)]
    \item If $f_1, \ldots, f_n$ are linear forms on $V$, then the function $f: V^n \to F$ defined by
    \[
        f(x_1, \ldots, x_n) = f_1(x_1) \cdots f_n(x_n)
    \]
    is multilinear.

    \item If $n = 2$ and $f_1, f_2$ are nonzero linear forms on $V$, then the bilinear form $f$ of (i) is not alternate. 
    \{Hint: \S1.6, Exercise 18.\}

    \item If $n = 2$ and $f_1, f_2$ are linearly independent linear forms on $V$, then the bilinear form $f$ defined by
    \[
        f(x_1, x_2) = f_1(x_1)f_2(x_2) - f_1(x_2)f_2(x_1)
    \]
    is alternate and not identically zero. \{Hint: $\ker f_1$ is not contained in $\ker f_2$.\}

    \item If $x_1, \ldots, x_n$ is a basis of $V$, and $f_1, \ldots, f_n$ is the dual basis of $V'$, then the function $f$ defined by the formula
    \[
        (*) \qquad f(y_1, \ldots, y_n) = \sum_{\sigma \in S_n} (\operatorname{sgn} \sigma) f_{\sigma(1)}(y_1) \cdots f_{\sigma(n)}(y_n)
    \]
    is the nonzero alternate multilinear form constructed in Lemma 7.1.13.
\end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose $f_1, \ldots, f_n$ are linear forms on $V$.
    Multilinearity follows from the linearity of each $f_i$.
\end{proof}

\begin{proof}
    Suppose $n = 2$ and $f_1, f_2$ are nonzero linear forms on $V$.
    Since $f_1, f_2 \ne 0$ there exist $x, y \in V$ such that
    $f_1(x) \ne 0$ and $f_2(y) \ne 0$.
    Let $v = x + y$. Then
    \[
        f(v, v) = f_1(v)f_2(v) \ne 0,
    \]
    which contradicts $f$ being alternate.
\end{proof}

\begin{proof}
    Suppose $n = 2$ and $f_1, f_2$ are linearly independent linear forms on $V$.
    If $\ker f_1 \subseteq \ker f_2$ then $f_2$ is a scalar multiple of $f_1$,
        contradicting linear independence.
    Thus there exists $x \in \ker f_1 \setminus \ker f_2$.
    Similarly there exists $y \in \ker f_2 \setminus \ker f_1$.
    Then
    \[f(x, y) = f_1(x)f_2(y) - f_1(y)f_2(x) = -f_1(y)f_2(x) \ne 0,\]
    so $f$ is not identically zero. For any $x \in V$,
    \[f(x, x) = f_1(x)f_2(x) - f_1(x)f_2(x) = 0,\]
    so $f$ is alternate.
\end{proof}

\begin{proof}
    Suppose $x_1, \ldots, x_n$ is a basis of $V$
        and $f_1, \ldots, f_n$ is the dual basis of $V'$.
    We show $f(x_1, \ldots, x_n) = 1$, after which Lemma 7.1.12 guarantees uniqueness.
    Since $f_i(x_j) = \delta_{ij}$, the only permutation $\sigma$ for which
    $f_{\sigma(1)}(x_1) \cdots f_{\sigma(n)}(x_n) \ne 0$ is $\sigma = \iota$,
    giving $(\operatorname{sgn} \iota) \cdot 1 \cdots 1 = 1$.
\end{proof}


\begin{tcolorbox}[title=Problem 3, breakable]
    Let $V_1, V_2, W$ be vector spaces over $F$.
    \begin{enumerate}
        \item Extend the concept of bilinearity to mappings $f : V_1 \times V_2 \longrightarrow W$ and
        prove that the set $\mathcal{N} = \mathcal{N}(V_1, V_2; W)$ of all such $f$ is a vector space
        over $F$ for the pointwise linear operations.
        \item Suppose $V_1, V_2, W$ are finite-dimensional; choose bases of the three spaces.
        A bilinear mapping $f : V_1 \times V_2 \longrightarrow W$ is determined by the
        vectors $f(x, y)$, where $x$ and $y$ are members of the chosen bases of $V_1$ and $V_2$;
        in turn, $f(x, y)$ is determined by its coordinates relative to the chosen basis of $W$. Determine
        the dimension of $\mathcal{N} = \mathcal{N}(V_1, V_2; W)$.
        \item Extend the preceding discussion to multilinear mappings $V_1 \times \cdots \times V_r \longrightarrow W$.
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    We immediately extend to multilinear mappings $V_1 \times \cdots \times V_r \longrightarrow W$.
    A mapping $f : V_1 \times \cdots \times V_r \longrightarrow W$ is \textit{multilinear} if for each
    fixed $(Y_1, \ldots, Y_r) \in V_1 \times \cdots \times V_r$ and each index $i$, the function
    \[X_i \mapsto f(Y_1, \ldots, Y_{i-1}, X_i, Y_{i+1}, \ldots, Y_r), \quad X_i \in V_i,\]
    is linear. We write $\mathcal{MN}(V_1, \ldots, V_r; W)$ for the set of all such mappings.

    This set is a vector space under pointwise operations. 
    For $f, g \in \mathcal{MN}$ and $c \in F$,
    the maps $f + g$ and $c f$ are again multilinear,
    and the zero map gives the additive identity. Setting $r = 2$ gives the bilinear case,
    solving (i) and (iii).

    For (ii), let $\dim V_1 = m$, $\dim V_2 = n$, $\dim W = p$ We have
    \[\dim \mathcal{N}(V_1, V_2; W) = mnp = (\dim V_1)(\dim V_2)(\dim W).\]
    Generally, $\dim \mathcal{MN}(V_1, \ldots, V_r; W) = (\dim V_1) \cdots (\dim V_r)(\dim W)$.
\end{proof}


\begin{tcolorbox}[title=Problem 4, breakable]
    As assumed at the outset of the chapter, $\dim V = n \geq 2$. Let $r$ be any positive integer
    $\geq 2$ and consider the vector space of multilinear forms $f : V^r \longrightarrow F$
    (cf.\ Exercise 3). Call such an $f$ \textit{alternate} if $f(x) = 0$ whenever
    $x = (x_1, \ldots, x_r)$ with $x_i = x_{i+1}$ for some $i$. The set $\mathcal{A}_r(V)$ of all
    alternate multilinear forms is a vector space for the pointwise linear operations; in particular,
    $\mathcal{A}_n(V)$ is the space $\mathcal{A}(V)$ of Theorem 7.1.3.
    \begin{enumerate}
        \item[(i)] If $r > n$ then $\mathcal{A}_r(V) = \{0\}$.
        \item[(ii)] Determine the dimension of $\mathcal{A}_r(V)$ for $r < n$.
    \end{enumerate}
    \textit{Hint}: (ii) If $x_1, \ldots, x_n$ is a basis of $V$, then an alternate form $f$ is
    determined by its values on the $r$-ples $(x_{i_1}, x_{i_2}, \ldots, x_{i_r})$ with
    $i_1 < i_2 < \cdots < i_r$.
\end{tcolorbox}

\begin{proof}
    Suppose $r > n$.
    Let $x = (x_1, \ldots, x_r)$ be any $r$-tuple of vectors in $V$.
    Since $r > n = \dim V$, the vectors $x_1, \ldots, x_r$ are linearly dependent.
    There exist scalars $c_1, \ldots, c_r$, not all zero, such that
    $\sum_{i=1}^r c_i x_i = 0$. Suppose WLOG $c_j \ne 0$; then
    \[x_j = -\sum_{i \ne j} \frac{c_i}{c_j} x_i.\]
    By multilinearity,
    \[
    f(x_1, \ldots, x_r)
    =
    -\sum_{i \ne j} \frac{c_i}{c_j}
    f(x_1, \ldots, x_i, \ldots, x_r),
    \]
    where in each term $x_i$ appears in both the $i$th and $j$th positions.
    Since $f$ is alternate, each such term is $0$. Thus $f(x_1, \ldots, x_r) = 0$.
    Since $x$ was arbitrary, $f = 0$, so $\mathcal{A}_r(V) = \{0\}$.
\end{proof}

\begin{proof}
    Suppose $x_1, \ldots, x_n$ is a basis of $V$.
    Since an alternate form $f$ is
    determined by its values on the $r$-tuples $(x_{i_1}, x_{i_2}, \ldots, x_{i_r})$ with
    $i_1 < i_2 < \cdots < i_r$, and these values may be chosen freely,
    we have $\dim \mathcal{A}_r(V) = \binom{n}{r}$.
\end{proof}

\subsection{Determinant of a Linear Mapping}


\begin{tcolorbox}[title=Problem 1, breakable]
    \begin{enumerate}
        \item For every $g \in V'$ and $y \in V$, the linear mapping 
        $g \otimes y \in \mathcal{L}(V)$ defined in Example 2.3.4 has determinant $0$.
        \item Every $T \in \mathcal{L}(V)$ is a sum $T = T_1 + \cdots + T_n$ with $det T_1 = \cdots = det T_n = 0$,
        where $n = \dim V$. (Hint: 3.8 Exercise 9).
        \item Express the identity mapping $I \in \mathcal{L}(V)$ as a sum $I = T_1 + \cdots + T_n$
        as in (ii), and describe explicitly the mappings $T_i$. (Hint: Dual basis.)
    \end{enumerate}
\end{tcolorbox}

\begin{proof}
    Let $T = f \otimes y \in \mathcal{L}(V, V)$.
    For all $x \in V$ we have $(f \otimes y)(x) = f(x)y$.
    Let $g \in \mathcal{A}(V)$ and $x_1, \ldots, x_n$ a basis of $V$, then 
    \[\hat{T}g(x_1, \ldots, x_n) = g(Tx_1, \ldots, Tx_n) = g(f(x_1)y, \ldots, f(x_n)y).\]
    Since each $f(x_i)y$ is a scalar multiple of $y$, the vectors $f(x_1)y, \ldots, f(x_n)y$
    are linearly dependent (since $n \ge 2$), so by Corollary 7.2.7 $\hat{T}g = 0$.
    Thus $\det T = 0$.
\end{proof}

\begin{proof}
    Let $x_1, \ldots, x_n$ be a basis of $V$.
    By Section 3.8 Exercise 9, every $T \in \mathcal{L}(V)$ can be written as
    $T = \sum_{i=1}^n f_i \otimes y_i$
    where $f_i \in V'$ and $y_i \in V$.
    By the previous part, each $f_i \otimes y_i$ has determinant $0$.
    Thus $T = T_1 + \cdots + T_n$ with $T_i = f_i \otimes y_i$ and $\det T_1 = \cdots = \det T_n = 0$.
\end{proof}

\begin{proof}
    Let $x_1, \ldots, x_n$ be a basis of $V$ and $f_1, \ldots, f_n$ the dual basis of $V'$,
    so that $f_i(x_j) = \delta_{ij}$.
    Define $T_i = f_i \otimes x_i$, so that $T_i(x) = f_i(x)x_i$ for all $x \in V$.
    Then
    \[\sum_{i=1}^n T_i(x) = \sum_{i=1}^n f_i(x) x_i = x\]
    for all $x \in V$, thus $I = T_1 + \cdots + T_n$.
    Each $T_i = f_i \otimes x_i$ has determinant $0$ by part (i).
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
    Let $x_1, \ldots, x_n$ be a basis of $V$, $T \in \mathcal{L}(V)$
    a linear mapping such that $T x_k \in [\{x_1, \ldots, x_k\}]$
    for $k = 1, \ldots, n$. Show that if $A = (a_{ij})$ is the matrix of 
    $T$ relative to this basis, then $det T = a_{11} a_{22} \ldots a_{nn}$.
\end{tcolorbox}

\begin{proof}
    Suppose $A = (a_{ij})$ is the matrix of $T$ relative to this basis.
    Since $Tx_k \in [\{x_1, \ldots, x_k\}]$ we have
    \[Tx_k = \sum_{j=1}^k a_{jk} x_j.\]
    Then for all $g \in \mathcal{A}(V)$
    \[\hat{T}g(x_1, \ldots, x_n) = g(Tx_1, \ldots, Tx_n) = g\!\left(\sum_{j=1}^1 a_{j1}x_j, \ldots, \sum_{j=1}^n a_{jn}x_j\right).\]
    By multilinearity, this expands into a sum of terms of the form
    \[a_{i_1 1} a_{i_2 2} \cdots a_{i_n n}\, g(x_{i_1}, \ldots, x_{i_n})\]
    where $i_k \le k$ for each $k$. Since $g$ is alternate, $g(x_{i_1}, \ldots, x_{i_n}) \ne 0$
    only if $i_1, \ldots, i_n$ are all distinct. But since $i_k \le k$ for all $k$,
    the only such choice is $i_k = k$ for all $k$. Thus
    \[\hat{T}g(x_1, \ldots, x_n) = a_{11} a_{22} \cdots a_{nn}\, g(x_1, \ldots, x_n)\]
    so $\det T = a_{11} a_{22} \cdots a_{nn}$.
\end{proof}

\begin{tcolorbox}[title=Problem 3, breakable]
    Let $V$ be the ($n$-dimensional) vector space of real polynomials of degree 
    $\le n - 1$ (1.3.6) and let $D \in \mathcal{L}(V)$ be the differentiation mapping 
    $Dp = p'$ (cf. 2.1.4). Show that $det D = 0$ and $det (I + D) = 1$.
    (Hint: Look at Exercise 2 in the light of the basis $1, t, t^2, \ldots, t^{n - 1}$ of $V$.)
\end{tcolorbox}

\begin{proof}
    Consider the basis $1, t, t^2, \ldots, t^{n-1}$ of $V$.
    We have $D(t^k) = kt^{k-1} \in [\{1, t, \ldots, t^{k-1}\}] \subseteq [\{1, t, \ldots, t^k\}]$
    for each $k$, so by Problem 2 $\det D = a_{11} a_{22} \cdots a_{nn}$
    where $a_{kk}$ is the coefficient of $t^{k-1}$ in $D(t^{k-1}) = (k-1)t^{k-2}$,
    which is $0$ for $k = 1$. Thus $\det D = 0$.
    Similarly, $(I + D)(t^k) = t^k + kt^{k-1} \in [\{1, t, \ldots, t^k\}]$,
    and the coefficient of $t^k$ in $(I+D)(t^k)$ is $1$ for each $k$,
    so $\det(I + D) = 1^n = 1$.
\end{proof}

\begin{tcolorbox}[title=Problem 4, breakable]
    Let $V \subset \mathcal{F}(R)$ be the 2-dimensional vector space assumed by the functions
    $\sin, \cos$, and let $T \in \mathcal{L}(V)$ be the differentiation mapping. Show that $det T = 1$.
\end{tcolorbox}

\begin{proof}
    Consider the basis $\sin, \cos$ of $V$.
    We have $T(\sin) = \cos$ and $T(\cos) = -\sin$.
    The matrix of $T$ relative to this basis is
    \[A = \begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix}\]
    so $\det T = (0)(0) - (-1)(1) = 1$.
\end{proof}

\subsection{Determinant of a Square Matrix}

\begin{tcolorbox}[title=Problem 1, breakable]
    If $A \in M_n(F)$ is a triangular matrix (say with $0$'s below the main diagnol),
    then $|A|$ is the product of the diagnol elements.
\end{tcolorbox}

\begin{proof}
    Suppose $A \in M_n(F)$ is upper triangular, so $a_{ij} = 0$ for $i > j$.
    Then for each $k$, the $k$-th column of $A$ has nonzero entries only in rows $1, \ldots, k$,
    so $A x_k \in [\{x_1, \ldots, x_k\}]$ for $k = 1, \ldots, n$.
    Thus, by Section 7.2 Exercise 2, $\det A = a_{11} a_{22} \cdots a_{nn}$.
\end{proof}


\begin{tcolorbox}[title=Problem 2, breakable]
    The theory of determinants can be extended to matrices $A \in M_n(S)$,
    where $S$ is any commutative ring. Here is an informal way of seeing why this 
    is so.
    \begin{enumerate}
        \item Construct an integral domain $\mathbb{R}$ by adjoining $n^2$ indeterminates $t_{ij}$
        to the ring $\mathbb{Z}$ of integers.
        \item Let $F$ be the field of fraction of $\mathbb{R}$ and let $T$ be the $n \times n$ matrix 
        whose $(i, j)$ entry is $t_{ij}$; thus $T = (t_{ij}) \in M_n(\mathbb{R}) \subset M_n(F)$.
        Then $|T|$ makes sense and is an element of $\mathbb{R}$, that is, a polynomial in the $t_{ij}$
        with integral coefficients.
        \item With $A \in M_n(S)$ as above, define $|A|$ to be the result of substituting $a_{ij}$ with $t_{ij}$
        in the formula of $|T|$.
        \item To see that $|AB| = |A| \cdot |B|$ for all $A, B \in M_n(S)$, adjoin instead $2n^2$ indeterminates
        $t_{ij}, u_{ij}$ and make the appropriate substitutions in the equation $|TU| = |T| \cdot |U|$.
    \end{enumerate}
\end{tcolorbox}

\textbf{Solution: } Alrighty Then.

\begin{tcolorbox}[title=Problem 3, breakable]
    State and prove the analogue of Theorem 7.3.9 for row vectors.
\end{tcolorbox}

\begin{theorem}[7.3.9]
    Identify the set $M_n(F)$ with the product $F^n \times \cdots \times F^n$ 
    of $n$ copies of $F^n$, by identifying an $n \times n$ matrix with its $n$-tuple of column vectors. 
    The determinant function $A \mapsto \det A$ is the unique function $M_n(F) \to F$ that is 
    an alternating multilinear function of column vectors and has the value $1$ for the identity matrix $I$.
\end{theorem}

\begin{theorem}[7.3.9 Restated]
    Identify the set $M_n(F)$ with the product $F^n \times \cdots \times F^n$ of $n$ copies of $F^n$, 
    by identifying an $n \times n$ matrix with its $n$-tuple of row vectors. 
    The determinant function $A \mapsto \det A$ is the unique function $M_n(F) \to F$ 
    that is an alternating multilinear function of row vectors and has the value $1$ for the identity matrix $I$.
\end{theorem}

\begin{proof}
    Let $e_1, \ldots, e_n$ be the canonical basis of $F^n$ and let $f$ 
    be the unique alternate multilinear form on $F^n \times \cdots \times F^n$ ($n$ factors) such that 
    $f(e_1, \ldots, e_n) = 1$ (7.1.13). If $A \in M_n(F)$ and $x_1, \ldots, x_n$ are the row vectors of $A$,
     the problem is to show that $\det A = f(x_1, \ldots, x_n)$.

    Since $\det A = \det A^T$ and the row vectors of $A$ are the column vectors of $A^T$, by Theorem 7.3.9 applied to $A^T$,
    \[
        \det A = \det A^T = f(x_1, \ldots, x_n). \qedhere
    \]
\end{proof}

\subsection{Cofactors}


\begin{tcolorbox}[title=Problem 1, breakable]
Let $A \in M_n(\mathbb{Z})$. In order that $A$ have an inverse in $M_n(\mathbb{Z})$, it is necessary and sufficient that $|A| = \pm 1$.
\end{tcolorbox}

\begin{proof}
    Suppose $|A| = \pm 1$.
    By Corollary 7.4.5, $A$ is invertible.
    Now, suppose $A$ is invertible.
    Then $AB = I$ for some $B \in M_n(\mathbb{Z})$, so $|A||B| = 1$ in $\mathbb{Z}$.
    Since $|A|, |B| \in \mathbb{Z}$, both must be units in $\mathbb{Z}$, so $|A| = \pm 1$.
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
Let $F$ be any field, $R$ a subring of $F$ containing the unity element $1$. 
Let $A \in M_n(R)$. Prove that $A$ has an inverse in $M_n(R)$ if and only if $|A|$ has an inverse in $R$.
\end{tcolorbox}

\begin{proof}
    Suppose $A$ has an inverse in $M_n(R)$.
    There exists $B \in M_n(R)$ such that $AB = I$ and $BA = I$.
    So $|A||B| = 1$ and $|B||A| = 1$, and since $|B| \in R$
    (as the entries of $B$ lie in $R$ and $R$ is closed under addition and multiplication),
    $|A|$ has an inverse in $R$.

    Suppose $|A|$ has an inverse in $R$.
    Then $|A| \ne 0$, so by Corollary 7.4.5, $A^{-1} = |A|^{-1}(\mathrm{adj}\, A)$.
    Since $|A|^{-1} \in R$ and the entries of $\mathrm{adj}(A)$ lie in $R$,
    we have $A^{-1} \in M_n(R)$.
\end{proof}


\begin{tcolorbox}[title=Problem 3, breakable]
Let $A = (a_{ij}) \in M_n(F)$ be an invertible matrix, $\text{adj}\, A = (A_{ij})'$ the adjoint matrix, and
\[
\gamma = \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix}
\]
a column vector with entries in $F$. Show that for each $j = 1, \ldots, n$, the $j$'th coordinate of the column vector $(\text{adj}\, A)\gamma$ is
\[
\sum_{i=1}^{n} c_i A_{ij};
\]
this expression is the expansion, by the $j$'th column, of the determinant of the matrix obtained by replacing the $j$'th column of $A$ by the column vector $\gamma$.
\end{tcolorbox}

\begin{proof}
    We have 
    \[adj(A) = 
        \begin{bmatrix}
            A_{1,1} & A_{1,2} & \cdots & A_{1,n} \\
            A_{2,1} & A_{2,2} & \cdots & A_{2,n} \\
            \vdots  & \vdots  & \ddots & \vdots  \\
            A_{n,1} & A_{n,2} & \cdots & A_{n,n}
        \end{bmatrix},
    \]
    so 
    \[adj(A) \gamma = 
    \begin{bmatrix}
        A_{1,1} & A_{1,2} & \cdots & A_{1,n} \\
        A_{2,1} & A_{2,2} & \cdots & A_{2,n} \\
        \vdots  & \vdots  & \ddots & \vdots  \\
        A_{n,1} & A_{n,2} & \cdots & A_{n,n}
    \end{bmatrix}
    \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix}
    = 
    \begin{bmatrix}
        \sum_{i=1}^n A_{i,1} c_i \\
        \sum_{i=1}^n A_{i,2} c_i \\
        \vdots \\
        \sum_{i=1}^n A_{i,n} c_i
    \end{bmatrix},
    \]
    so the $j$'th coordinate is $\sum_{i=1}^n c_i A_{ij}$.
    This is precisely the cofactor expansion along the $j$'th column of the matrix obtained
    by replacing the $j$'th column of $A$ with $\gamma$, since the cofactors $A_{ij}$ are
    unchanged by this column replacement.
\end{proof}


\begin{tcolorbox}[title=Problem 4, breakable]
Given a system of linear equations
\[
(*) \quad \begin{cases}
a_{11}x_1 + a_{12}x_2 + \cdots + a_{1n}x_n = c_1 \\
a_{21}x_1 + a_{22}x_2 + \cdots + a_{2n}x_n = c_2 \\
\quad \cdots \\
a_{n1}x_1 + a_{n2}x_2 + \cdots + a_{nn}x_n = c_n
\end{cases}
\]
whose coefficient matrix $A = (a_{ij}) \in M_n(F)$ is invertible. Prove that the system $(*)$ has a unique solution vector $(x_1, \ldots, x_n)$, where $x_j = |A|^{-1}|B_j|$ and $B_j$ is the matrix obtained by replacing the $j$'th column of $A$ by the column of constants $c_1, \ldots, c_n$. (These formulas for the solution are known as \emph{Cramer's rule}.)

\{Hint: Solve the matrix equation
\[
A \begin{bmatrix} x_1 \\ x_2 \\ \vdots \\ x_n \end{bmatrix} = \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix}
\]
for the column vector on the left, and cite Exercise 3.\}
\end{tcolorbox}

\begin{proof}
    Since $A$ is invertible, $A^{-1} = |A|^{-1}(\mathrm{adj}\, A)$, and so
    \begin{align*}
        A \begin{bmatrix} x_1 \\ x_2 \\ \vdots \\ x_n \end{bmatrix} = \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix} 
        &\iff  \begin{bmatrix} x_1 \\ x_2 \\ \vdots \\ x_n \end{bmatrix} = A^{-1} \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix} \\
        &\iff \begin{bmatrix} x_1 \\ x_2 \\ \vdots \\ x_n \end{bmatrix} = |A|^{-1}(\mathrm{adj}\, A) \begin{bmatrix} c_1 \\ c_2 \\ \vdots \\ c_n \end{bmatrix} \\
        &\iff \begin{bmatrix} x_1 \\ x_2 \\ \vdots \\ x_n \end{bmatrix} = |A|^{-1}    
        \begin{bmatrix}
        \sum_{i=1}^n A_{i,1} c_i \\
        \sum_{i=1}^n A_{i,2} c_i \\
        \vdots \\
        \sum_{i=1}^n A_{i,n} c_i
    \end{bmatrix}.
    \end{align*}
    By Problem 3, $\sum_{i=1}^n c_i A_{ij}$ is the expansion by the $j$'th column of the determinant
    of $B_j$, so the $j$'th coordinate gives $x_j = |A|^{-1}|B_j|$, which is unique since
    $A^{-1}$ is unique.
\end{proof}


\begin{tcolorbox}[title=Problem 5, breakable]
Let $A \in M_n(F)$. Prove:
\begin{enumerate}[(i)]
    \item $A$ is invertible if and only if $\text{adj}\, A$ is invertible, in which case $(\text{adj}\, A)^{-1} = |A|^{-1}A$.
    \item $|\text{adj}\, A| = |A|^{n-1}$.
    \item If $|A| = 1$ then $\text{adj}(\text{adj}\, A) = A$.
\end{enumerate}
\end{tcolorbox}

\begin{proof}
    Suppose $A$ is invertible.
    Since $A^{-1} = |A|^{-1}(\text{adj}\, A)$, we can multiply by $A$ on the left to find
    \[I = A \cdot |A|^{-1}(\text{adj}\, A),\]
    so $\text{adj}\, A$ is invertible with $(\text{adj}\, A)^{-1} = |A|^{-1}A$.
    Conversely, suppose $\text{adj}\, A$ is invertible.
    Since $A(\text{adj}\, A) = |A|I$, taking determinants gives $|A||\text{adj}\, A| = |A|^n$, so $|A| \neq 0$, and $A$ is invertible.

    Taking determinants of $A(\text{adj}\, A) = |A|I$ gives $|A||\text{adj}\, A| = |A|^n$.
    Noting that $|A|I = diag(|A|_1, \ldots, |A|_n)$ so $det(|A|I) = |A|^n$.
    If $A$ is invertible, then $|\text{adj}\, A| = |A|^{n-1}$.
    If $A$ is not invertible then $|A| = 0$, and $A(\text{adj}\, A) = 0$ forces $\text{adj}\, A$ 
    to not be invertible by part (i), so $|\text{adj}\, A| = 0 = |A|^{n-1}$.

    Suppose $|A| = 1$.
    By part (ii) we have $|\text{adj}\, A| = |A|^{n-1} = 1$, so $\text{adj}\, A$ is invertible.
    Applying the identity $B(\text{adj}\, B) = |B|I$ with $B = \text{adj}\, A$ gives
    \[(\text{adj}\, A)(\text{adj}(\text{adj}\, A)) = |\text{adj}\, A| I = I.\]
    By part (i), $(\text{adj}\, A)^{-1} = |A|^{-1}A = A$, so multiplying on the left by $A$ gives $\text{adj}(\text{adj}\, A) = A$.
\end{proof}


\begin{tcolorbox}[title=Problem 6, breakable]
Write $\rho(A)$ for the rank of a matrix $A \in M_n(F)$. We are assuming that $n \geq 2$.
\begin{enumerate}[(i)]
    \item If $|A| \neq 0$ then $\rho(A) = \rho(\text{adj}\, A) = n$.
    \item If $|A| = 0$ then $\rho(A) + \rho(\text{adj}\, A) \leq n$.
    \item If $\rho(A) = n - 1$ then $\rho(\text{adj}\, A) = 1$.
    \item If $\rho(A) \leq n - 2$ then $\text{adj}\, A = 0$.
    \item If $n = 2$ then $\text{adj}(\text{adj}\, A) = A$.
    \item If $n \geq 3$ and $\rho(A) = n - 1$, then $\text{adj}(\text{adj}\, A) = 0$.
    \item $\text{adj}(\text{adj}\, A) = |A|^{n-2}A$ (with the convention that $0^{n-2} = 1$ when $n = 2$).
\end{enumerate}

\{Hint: (ii) Call $\nu(A) = n - \rho(A)$ the \emph{nullity} of $A$. From $A(\text{adj}\, A) = 0$ infer that $\rho(\text{adj}\, A) \leq \nu(A)$. The inequality of (ii) can be strict for a nonzero matrix (\S11.4, Exercise 3).

(iii) By \S10.4, Exercise 6, $\text{adj}\, A \neq 0$.

(iv) By \S10.4, Exercise 6, all $(n-1) \times (n-1)$ subdeterminants of $A$ are $0$.

(vi) Cite (iii) and (iv).

(vii) For $n = 2$, cite (v). For $n \geq 3$, cite (i), (iv) or (vi).\}
\end{tcolorbox}

\begin{proof}
    Suppose $|A| \ne 0$.
    It follows that the $n$ columns of $A$ are linearly independent.
    Thus $\rho(A) = n$.
    Since $|A| \ne 0$, $|A|^{n - 1} = |\text{adj}\, A| \ne 0$ (Problem 5), and since $|\text{adj}\, A| \ne 0$,
        similarly, the $n$ columns of $\text{adj}\, A$ are linearly independent,
        thus $\rho(\text{adj}\, A) = n$.
    So $\rho(A) = \rho(\text{adj}\, A) = n$.
\end{proof}

\begin{proof}
    Suppose $|A| = 0$.
    By rank-nullity we have $\nu(A) = n - \rho(A)$.
    Since $A(\operatorname{adj} A) = 0$, every column of $\operatorname{adj} A$ lies in $\ker A$,
    so $\rho(\operatorname{adj} A) \le \nu(A)$.
    Then
    \[
    \rho(A) + \rho(\operatorname{adj} A) \le \rho(A) + \nu(A) = \rho(A) + (n - \rho(A)) = n.
    \]
\end{proof}

\begin{proof}
    Suppose $\rho(A) = n - 1$.
    By (ii), $\rho(\text{adj}\, A) \le n - \rho(A) = 1$.
    Since $\rho(A) = n - 1$, some $(n-1) \times (n-1)$ subdeterminant of $A$ is nonzero
    (\S10.4, Exercise 6), so $\text{adj}\, A \ne 0$ and thus $\rho(\text{adj}\, A) \ge 1$.
    Therefore $\rho(\text{adj}\, A) = 1$.
\end{proof}

\begin{proof}
    Suppose $\rho(A) \le n - 2$.
    Then all $(n-1) \times (n-1)$ subdeterminants of $A$ are $0$ (\S10.4, Exercise 6),
    so every cofactor of $A$ is $0$, thus $\text{adj}\, A = 0$.
\end{proof}

\begin{proof}
    Suppose $n = 2$.
    Then $\text{adj}\, A = \begin{bmatrix} a_{22} & -a_{12} \\ -a_{21} & a_{11} \end{bmatrix}$,
    and applying the adjoint again gives
    $\text{adj}(\text{adj}\, A) = \begin{bmatrix} a_{11} & a_{12} \\ a_{21} & a_{22} \end{bmatrix} = A$.
\end{proof}

\begin{proof}
    Suppose $n \ge 3$ and $\rho(A) = n - 1$.
    By (iii), $\rho(\text{adj}\, A) = 1 \le n - 2$, so by (iv) applied to $\text{adj}\, A$,
    $\text{adj}(\text{adj}\, A) = 0$.
\end{proof}

\begin{proof}
    If $|A| \ne 0$, then $A$ is invertible and $\text{adj}\, A = |A|\, A^{-1}$, so
    \[
    \text{adj}(\text{adj}\, A) = |\text{adj}\, A|\,(\text{adj}\, A)^{-1}
    = |A|^{n-1}\,\big(|A|\,A^{-1}\big)^{-1}
    = |A|^{n-1}\,|A|^{-1} A = |A|^{n-2} A.
    \]
    If $|A| = 0$, then $|A|^{n-2} A = 0$ for $n \ge 3$, and $\text{adj}(\text{adj}\, A) = 0$.
    If $\rho(A) = n-1$ this is (vi), and if $\rho(A) \le n-2$ we have $\text{adj}\, A = 0$ by (iv),
    thus $\text{adj}(\text{adj}\, A) = 0$. For $n = 2$, the convention $0^{n-2} = 1$ gives
    $|A|^{n-2} A = A = \text{adj}(\text{adj}\, A)$ by (v).
\end{proof}


\begin{tcolorbox}[title=Problem 7, breakable]
Let $A, B \in M_n(F)$.
\begin{enumerate}[(i)]
    \item $\text{adj}(AB) = (\text{adj}\, B)(\text{adj}\, A)$.
    \item If $B$ is invertible, then $\text{adj}(B^{-1}AB) = B^{-1}(\text{adj}\, A)B$.
\end{enumerate}

\{Hint: (i) If $A$ and $B$ are both invertible, the formula is easily deduced from $(AB)^{-1} = B^{-1}A^{-1}$. In the general case, apply the preceding argument to the matrices $A - tI$, $B - tI$ in the context of the field of rational forms $F(t)$, then substitute $t = 0$.\}
\end{tcolorbox}

\begin{proof}
    Suppose $A$ and $B$ are both invertible.
    Then $\text{adj}\, A$ and $\text{adj}\, B$ are both invertible, and so is $AB$, thus $\text{adj}(AB)$.
    For any invertible $C$, $\text{adj}\, C = |C|\, C^{-1}$. Thus
    \begin{align*}
        \text{adj}(AB) &= |AB|\,(AB)^{-1} = |A||B|\, B^{-1}A^{-1} \\
            &= \big(|B|\, B^{-1}\big)\big(|A|\, A^{-1}\big) = (\text{adj}\, B)(\text{adj}\, A).
    \end{align*}
    For the general case, consider $A - tI$ and $B - tI$ over the field $F(t)$ of rational forms.
    Since $\ \det(A - tI)$ and $\det(B - tI)$ are nonzero polynomials in $F(t)$, both matrices are invertible over $F(t)$, so by the above
    \[
        \text{adj}\big((A - tI)(B - tI)\big) = \text{adj}(B - tI)\,\text{adj}(A - tI).
    \]
    Substituting $t = 0$ gives
    \[
        \text{adj}(AB) = (\text{adj}\, B)(\text{adj}\, A).
    \]
    For (ii), since $B$ is invertible, $\text{adj}\, B = |B|\, B^{-1}$ and 
    $\text{adj}(B^{-1}) = |B^{-1}|\,(B^{-1})^{-1} = |B|^{-1} B$. Using (i),
    \begin{align*}
        \text{adj}(B^{-1}AB) &= \text{adj}(B)\,\text{adj}(A)\,\text{adj}(B^{-1}) \\
            &= \big(|B|\, B^{-1}\big)(\text{adj}\, A)\big(|B|^{-1} B\big) = B^{-1}(\text{adj}\, A)B.
    \end{align*}
\end{proof}