\subsection{Determinant of a $2 \times 2$ matrix}


\begin{tcolorbox}[title=Problem 3, breakable]
    If 
    \[A = 
    \begin{bmatrix}
        a & c \\ b & d
    \end{bmatrix}, \text{define } B = 
    \begin{bmatrix}
        d & -c \\
        -b & a
    \end{bmatrix}.\]
    Show that $AB = |A| \cdot I$. If $A$ is invertible,
        deduce a formula for $A^{-1}$.
\end{tcolorbox}

\begin{proof}
    We have
    \[AB =
    \begin{bmatrix}
        ad - bc & -ac + ca \\
        bd - db & -bc + ad
    \end{bmatrix} =
    \begin{bmatrix}
        ad - bc & 0 \\
        0 & ad - bc
    \end{bmatrix} = |A|I.\]
    Now suppose $A$ is invertible. Then $|A| \ne 0$, and from $AB = |A|I$ we get
    \[A \cdot \frac{1}{|A|}B = I,\]
    so $A^{-1} = \dfrac{1}{|A|}B$.
\end{proof}

\subsection{Cross Product of Vectors in $\mathbb{R}^3$}

\begin{tcolorbox}[title=Problem 1, breakable]
    Show that $\|x \times y\|^2 = \|x\|^2 \|y\|^2 - (x \mid y)^2$
    for all vectors $x, y$ in $\mathbb{R}^3$.
\end{tcolorbox}

\begin{proof}
Let $x = (x_1, x_2, x_3),\ y = (y_1, y_2, y_3) \in \mathbb{R}^3$. We have
\begin{align*}
\|x\|^2\|y\|^2 - (x\mid y)^2
    &= (x_1^2+x_2^2+x_3^2)(y_1^2+y_2^2+y_3^2) - (x_1 y_1 + x_2 y_2 + x_3 y_3)^2 \\
    &= x_1^2 y_2^2 - 2x_1 x_2 y_1 y_2 + x_2^2 y_1^2 \\
    &\quad + x_1^2 y_3^2 - 2x_1 x_3 y_1 y_3 + x_3^2 y_1^2 \\
    &\quad + x_2^2 y_3^2 - 2x_2 x_3 y_2 y_3 + x_3^2 y_2^2 \\
    &= (x_1 y_2 - x_2 y_1)^2 + (x_1 y_3 - x_3 y_1)^2 + (x_2 y_3 - x_3 y_2)^2 \\
    &= \|x \times y\|^2. \qedhere
\end{align*}
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
    If $u_1, u_2$ are orthonormal vectors in $\mathbb{R}^3$
    (5.2.13), prove that $u_1, u_2$, $u_1 \times u_2$ is an orthonormal 
    basis of $\mathbb{R}^3$.
\end{tcolorbox}

\begin{proof}
    Suppose $u_1, u_2$ are orthonormal vectors in $\mathbb{R}^3$.
    Since $u_1, u_2$ are are linearly independent,
        by Corollary 6.2.6 $u_1, u_2, u_1 \times u_2$ form a basis of $\mathbb{R}^3$.
    By Theorem 6.2.5, $u_1, u_2$ are both orthogonal to $u_1 \times u_2$.
    It follows that $u_1, u_2, u_1 \times u_2$ is an orthonormal basis of $\mathbb{R}^3$.
\end{proof}


\begin{tcolorbox}[title=Problem 3, breakable]
    Calculate $9$ vectors $e_1 \times e_2$, where $e_1, e_2, e_3$
    is the canonical basis of $\mathbb{R}^3$. 
    (For example, $e_1 \times e_2 = e_3$.)
\end{tcolorbox}

\begin{proof}
    We have
\begin{enumerate}
    \item $e_1 \times e_1 = 0$
    \item $e_1 \times e_2 = e_3$
    \item $e_1 \times e_3 = -e_2$
    \item $e_2 \times e_1 = -e_3$
    \item $e_2 \times e_2 = 0$
    \item $e_2 \times e_3 = e_1$
    \item $e_3 \times e_1 = e_2$
    \item $e_3 \times e_2 = -e_1$
    \item $e_3 \times e_3 = 0$
\end{enumerate}
\end{proof}

\begin{tcolorbox}[title=Problem 4, breakable]
    If $x, y \in \mathbb{R}^3$ are linearly dependent,
    show that $[\{x, y\}]^\perp \ne [\{x \times y\}]$ (cf. 6.2.7).
    Conclude that $[\{x, y\}]^\perp = [\{x \times y\}]$ if and only if 
    $x, y$ are independent.
\end{tcolorbox}

\begin{proof}
    Suppose $x, y \in \mathbb{R}^3$ are linearly dependent.
    Then $x \times y = \theta$, so $[\{x \times y\}] = \{\theta\}$.
    If $x = y = \theta$, then $[\{x, y\}]^\perp = \mathbb{R}^3 \ne \{\theta\} = [\{x \times y\}]$.
    Otherwise, WLOG $x \ne \theta$, so $[\{x, y\}]$ is a nonzero subspace,
    thus $[\{x, y\}]^\perp \ne \mathbb{R}^3$, and thus
    $[\{x, y\}]^\perp \ne \{\theta\} = [\{x \times y\}]$.

    Conversely, suppose $x, y$ are linearly independent.
    Then by Corollary 6.2.7, $[\{x, y\}]^\perp = [\{x \times y\}]$.

    Therefore $[\{x, y\}]^\perp = [\{x \times y\}]$ if and only if $x, y$ are linearly independent.
\end{proof}

\begin{tcolorbox}[title=Problem 5, breakable]
    Vectors $x, y$ in an inner product space are linearly dependent
    if and only if $|(x \mid y)| = \|x\| \cdot \|y\|$ (Theorem 5.1.8).
    Give a lightning proof for vectors in $\mathbb{R}^3$. (Hint: Exercise 1.)
\end{tcolorbox}

\begin{proof}
    By the Cauchy-Schwarz inequality, $|(x \mid y)| \le \|x\| \cdot \|y\|$.
    Equality holds if and only if $x$ and $y$ are linearly dependent.
\end{proof}

\begin{proof}
    By Exercise 1, $\|x \times y\|^2 = \|x\|^2\|y\|^2 - (x \mid y)^2$. Then
    \[x, y \text{ are dependent} \iff x \times y = \theta \iff \|x \times y\|^2 = 0 \iff \|x\|^2\|y\|^2 - (x \mid y)^2 = 0 \iff |(x \mid y)| = \|x\| \cdot \|y\|.\]
\end{proof}

\subsection{Determinant of a $3 \times 3$ matrix}

\begin{tcolorbox}[title=Problem 7, breakable]
    Calculate the determinant of the matrix 
    \[
    A = 
    \begin{bmatrix}
        2 & 3 & 7 \\
        0 & 4 & 5 \\
        0 & 0 & -1
    \end{bmatrix}
    \]
\end{tcolorbox}

\begin{proof}
    Since $A$ is upper triangular, $\det(A) = 2 \cdot 4 \cdot (-1) = -8$.
\end{proof}

\subsection{Characteristic Polynomial of a Matrix ($2 \times 2$ or $3 \times 3$)}

\begin{tcolorbox}[title=Problem 1, breakable]
Find the characteristic polynomial and characteristic roots of each of the following matrices $A$:
\[
\text{(i) } A = \begin{pmatrix}2 & 6\\6 & -3\end{pmatrix}, \quad
\text{(ii) } A = \begin{pmatrix}3 & 0\\0 & 5\end{pmatrix},
\]
\[
\text{(iii) } A = \begin{pmatrix}3 & 0\\0 & 3\end{pmatrix}, \quad
\text{(iv) } A = \begin{pmatrix}3 & 1\\0 & 3\end{pmatrix}.
\]
\end{tcolorbox}

\begin{proof}
\textbf{(i)} $p(\lambda)=\lambda^2+\lambda-42=(\lambda-6)(\lambda+7)$; roots $\lambda=6,-7$.\\
\textbf{(ii)} $p(\lambda)=(\lambda-3)(\lambda-5)$; roots $\lambda=3,5$.\\
\textbf{(iii)} $p(\lambda)=(\lambda-3)^2$; root $\lambda=3$ (multiplicity 2).\\
\textbf{(iv)} $p(\lambda)=(\lambda-3)^2$; root $\lambda=3$ (multiplicity 2).
\end{proof}

\begin{tcolorbox}[title=Problem 2, breakable]
Find the characteristic polynomial and characteristic roots of the matrix
\[
A = \begin{pmatrix}2 & 3 & 7\\0 & 4 & 5\\0 & 0 & -1\end{pmatrix}.
\]
\end{tcolorbox}

\begin{proof}
$p(\lambda)=(\lambda-2)(\lambda-4)(\lambda+1)$; roots $\lambda=2,4,-1$.
\end{proof}

\begin{tcolorbox}[title=Problem 4, breakable]
Give an example of a $3 \times 3$ matrix over $\mathbf{R}$ that has one real and two non-real characteristic roots.
\end{tcolorbox}

\begin{proof}
Consider $p(\lambda) = (\lambda-1)(\lambda^2+1)$, which gives one real root $\lambda=1$ and two non-real roots $\lambda=\pm i$. We see
\[
A = \begin{pmatrix}1 & 0 & 0\\0 & 0 & -1\\0 & 1 & 0\end{pmatrix}
\]
has this characteristic polynomial.
\end{proof}

\begin{tcolorbox}[title=Problem 6, breakable]
Show that the matrices
\[
A = \begin{pmatrix}1 & 0\\0 & 1\end{pmatrix}, \quad B = \begin{pmatrix}1 & 1\\0 & 1\end{pmatrix}
\]
have the same characteristic polynomial, but are not similar.
\end{tcolorbox}

\begin{proof}   
    The characteristic polynomial for both is $(1 - \lambda)^2$.
    Suppose there exists an invertible matrix $C$ such that 
    \[A = C^{-1} B C.\]
    But $A = I$, so $C^{-1}BC = I$ so $B = I$, a contradiction. 
\end{proof}

\begin{tcolorbox}[title=Problem 7, breakable]
If $A$ is a $3 \times 3$ real matrix and $p$ 
is its characteristic polynomial,
show that the constant term of $p$ is $-|A|$ 
and the coefficient of the term of second degree is $-\operatorname{tr} A$ 
(\S4.2, Exercise 7).
\end{tcolorbox}

\begin{proof}
Suppose $A$ is a $3\times 3$ real matrix and $p$ is its characteristic polynomial. Let
\[
A = \begin{pmatrix} a_{11} & a_{12} & a_{13}\\ a_{21} & a_{22} & a_{23}\\ a_{31} & a_{32} & a_{33} \end{pmatrix}.
\]
First, notice $-|A| = -\det(A)$ and $\operatorname{tr} A = a_{11}+a_{22}+a_{33}$. Then the characteristic polynomial is
\[
p(\lambda) = -\lambda^3 + (a_{11}+a_{22}+a_{33})\lambda^2 - (\cdots)\lambda + (-1)^3\det(A).
\]
So the constant term is $-\det(A) = -|A|$, and the coefficient of $\lambda^2$ is $-(a_{11}+a_{22}+a_{33}) = -\operatorname{tr} A$.
\end{proof}


\begin{tcolorbox}[title=Problem 8, breakable]
Let $T \in \mathcal{L}(\mathbf{R}^3)$ be an orthogonal linear mapping in Euclidean 3-space (5.4.1) and let $A$ be the matrix of $T$ relative to some orthonormal basis of $\mathbf{R}^3$, so that $A$ is an orthogonal matrix (Theorem 5.4.3). Prove:
\begin{enumerate}[(i)]
    \item There exists a nonzero vector $u$ such that $Tu = \pm u$.
    \item The matrix $A$ has either $+1$ or $-1$ as a characteristic root.
    \item If $|A| = 1$ then the orthogonal matrix $A$ has $+1$ as a characteristic root.
    \item If $|A| = 1$ then $T$ may be regarded as a rotation in $\mathbf{R}^3$.
    \item $|A| = \pm 1$.
    \item If $|A| = -1$ then $-T$ is a rotation, so $T = (-1)(-T)$ is composed of a rotation followed by reflection in the origin.
\end{enumerate}
\end{tcolorbox}

\begin{proof}
    Since $A$ is orthogonal we have $AA' = I$,
    so $|A||A'| = |I| = 1$. Since $|A| = |A'|$, we get $|A|^2 = 1$,
    thus $|A| = \pm 1$.
\end{proof}

\begin{proof}
    Since $|A| = \pm 1 \neq 0$, the characteristic polynomial $p_A(r) = |A - rI|$
    is a degree three polynomial with real coefficients, so it has at least one real root $r_1$.
    Since $A$ is orthogonal, $\|Av\| = \|v\|$ for all $v$, so for any eigenvector $v$ with eigenvalue $r_1$
    we have $|r_1| = 1$ thus $r_1 = \pm 1$.
    So $p_A(1) = 0$ or $p_A(-1) = 0$.
\end{proof}

\begin{proof}
    By (ii), $A$ has $+1$ or $-1$ as a characteristic root, so there exists a nonzero vector $u$
    with $Au = \pm u$, so  $Tu = \pm u$.
\end{proof}

\begin{proof}
    Suppose $|A| = 1$.
    Let $r_1, r_2, r_3$ be the characteristic roots.
    Since $A$ is orthogonal, for each eigenvector $v_i$ we have $\|Av_i\| = \|v_i\|$,
    so $|r_i| = 1$.
    Setting $r = 0$ in $\det(A - rI) = (-1)^3(r - r_1)(r - r_2)(r - r_3)$ gives
    $\det(A) = r_1 r_2 r_3 = 1$.
    If $r_1, r_2, r_3$ are all real, they must each be $\pm 1$ and their product is $1$,
    so they cannot all be $-1$, meaning at least one equals $+1$.
    If only one of them is real, say $r_1$, then the other two are complex conjugates
    of each other, so $1 = r_1 r_2 r_3 = r_1 |r_2|^2 = r_1$, therefore $r_1 = 1$.
\end{proof}

\begin{proof}
    Suppose $|A| = 1$.
    By Section 5.4 Problem 6, since $|A| = 1$ we know $A$ is a rotation.
\end{proof}

\begin{proof}
    Suppose $|A| = -1$.
    Then $|-A| = (-1)^3|A| = (-1)^3(-1) = 1$,
    so $-T$ is an orthogonal map with determinant $1$. By (iv), $-T$ is a rotation.
    Thus $T = (-1)(-T)$ is a rotation followed by reflection in the origin.
\end{proof}


\begin{tcolorbox}[title=Problem 9, breakable]
In the Euclidean plane $\mathbf{R}^2$, let $x_1 = (1,0)$, $x_2 = (1,1)$, 
and let $T \in \mathcal{L}(\mathbf{R}^2)$ be the linear mapping such 
that $Tx_1 = x_2$, $Tx_2 = x_1$. Prove that the matrix of $T$ relative 
to the basis $x_1$, $x_2$ is symmetric, but $T$ is not self-adjoint. 
Does this contradict Theorem 6.4.5? \{Hint: Calculate the matrix of $T$ relative to the canonical basis $e_1, e_2$.\}
\end{tcolorbox}

\begin{proof}
    We have 
    $T(x_1) = 0 x_1 + 1 x_2$ and 
    $T(x_2) = 1 x_1 + 0 x_2$ so the matrix of $T$ with respect to 
    the basis $x_1, x_2$ is 
    \[
    A = \begin{bmatrix}
        0 & 1 \\
        1 & 0
    \end{bmatrix}.
    \]
    It is clear that $T$ relative to the basis $x_1, x_2$ is symmetric since $A = A'$.
    To find the matrix with respect to the canonical basis $e_1, e_2$, note that
    $x_1 = e_1$ and $x_2 = e_1 + e_2$, so $e_2 = x_2 - x_1$. Then
    \[
    Te_1 = Tx_1 = x_2 = (1,1), \quad Te_2 = T(x_2 - x_1) = Tx_2 - Tx_1 = x_1 - x_2 = (0,-1).
    \]
    Thus the matrix with respect to $e_1, e_2$ is 
    \[
    B = \begin{bmatrix}
        1 & 0 \\
        1 & -1
    \end{bmatrix},
    \]
    which is not symmetric, so $T$ is not self-adjoint. This does not contradict
    Theorem 6.4.5, which states that a self-adjoint operator has a symmetric matrix
    relative to an \emph{orthonormal} basis. The basis $x_1, x_2$ is not orthonormal
    since $x_1 \cdot x_2 = 1 \neq 0$, so the theorem does not apply.
\end{proof}

\begin{tcolorbox}[title=Problem 10, breakable]
Prove that the matrix
\[
A = \begin{pmatrix}1 & 1\\0 & 1\end{pmatrix}
\]
is not similar to a diagonal matrix. \{Hint: Corollary 6.4.20 and Exercise 6.\}
\end{tcolorbox}

\begin{proof}
    Note that $|A - \lambda I| = (1-\lambda)^2$, so $r_1 = r_2 = 1$.
    Suppose, for contradiction, that $A$ is similar to a diagonal matrix.
    So, there exists $C$ such that $A = C^{-1} B C$ where $B$ is diagnol.
    Now, since $B$ shares the characteristic roots of $A$ we must have $B = I$.
    But then this contradicts Exercise 6.
\end{proof}


\begin{tcolorbox}[title=Problem 11, breakable]
Let $T$ be a self-adjoint linear mapping in a Euclidean space. Show that:
\begin{enumerate}[(i)]
    \item $(T(x+y)\mid x+y) - (T(x-y)\mid x-y) = 4(Tx\mid y)$ for all vectors $x$ and $y$.
    \item If $(Tx\mid x) = 0$ for all vectors $x$, then $T = 0$ (cf.\ \S5.2, Exercise 11).
\end{enumerate}
\end{tcolorbox}

\begin{proof}
    We have 
    \begin{align*}
        (T(x+y)\mid x+y) &= (Tx+Ty \mid x+y) \\
        &= (Tx\mid x) + (Tx\mid y) + (Ty\mid x) + (Ty\mid y)
    \end{align*}
    and
    \begin{align*}
        (T(x-y)\mid x-y) &= (Tx-Ty \mid x-y) \\
        &= (Tx\mid x) - (Tx\mid y) - (Ty\mid x) + (Ty\mid y).
    \end{align*}
    Subtracting
    \begin{align*}
        (T(x+y)\mid x+y) - (T(x-y)\mid x-y) &= 2(Tx\mid y) + 2(Ty\mid x).
    \end{align*}
    Since $T$ is self-adjoint, $(Ty\mid x) = (Tx \mid y)$ thus
    \[
        = 2(Tx\mid y) + 2(Tx\mid y) = 4(Tx\mid y). 
    \]
\end{proof}

\begin{proof}
    For $x, y \in E$, by part (i) and the self-adjointness of $T$
    \[
        (Tx \mid y) = \frac{1}{4}\{(T(x+y)\mid x+y) - (T(x-y)\mid x-y)\}.
    \]
    Since $(Tz \mid z) = 0$ for all $z$, we have $(Tx \mid y) = 0$ for all $x, y \in E$.
    Setting $y = Tx$ gives $(Tx \mid Tx) = \|Tx\|^2 = 0$, so $Tx = 0$ for all $x$, thus $T = 0$.
\end{proof}

\subsection{Diagnolizing $2 \times 2$ Symmetric Real Matrices}

\begin{tcolorbox}[title=Problem 2, breakable]
    If $T \in \mathbb{L}(\mathbb{R}^2)$ and if, relative to some 
    basis of $\mathbb{R}^2$ (not necessarily orthonormal), the matrix of 
    $T$ is symmetric, prove that there exists a basis of 
    $\mathbb{R}^2$ consisting of eigenvectors of $T$. 
\end{tcolorbox}

\begin{proof}
    Let $A$ be the matrix of $T$ relative to some basis of $\mathbb{R}^2$. Since $A$ is symmetric,
    by Corollary 6.5.3, there exists a $2 \times 2$
    orthogonal matrix $C$ such that $C'AC$ is diagonal.
    Let $x_1, x_2$ be the original basis and $y_1, y_2$ be the basis corresponding to the columns of $C$.
    Let $B = C'AC$ be the matrix of $T$ relative to $y_1, y_2$.
    By Theorem 4.10.4, $B$ is the matrix of $T$ relative to $y_1, y_2$. Since $B$ is diagonal,
    by Theorem 6.4.17, $y_1, y_2$ are eigenvectors of $T$, and thus form a basis of $\mathbb{R}^2$ consisting of eigenvectors of $T$.
\end{proof}

\subsection{Diagnolizing $3 \times 3$ Symmetric Real Matrices}


\begin{tcolorbox}[title=Problem 2, breakable]
If $T \in \mathcal{L}(\mathbf{R}^3)$ and if, 
relative to some basis of $\mathbf{R}^3$ (not necessarily orthonormal), 
the matrix of $T$ is symmetric, prove that $\mathbf{R}^3$ has a basis consisting 
of eigenvectors of $T$. \{Hint: Cf.\ \S6.5, Exercise 2.\}
\end{tcolorbox}

\begin{proof}
    Let $A$ be the matrix of $T$ relative to some basis of $\mathbb{R}^3$. Since $A$ is symmetric,
    by Corollary 6.5.3, there exists a $3 \times 3$
    orthogonal matrix $C$ such that $C'AC$ is diagonal.
    Let $x_1, x_2, x_3$ be the original basis and $y_1, y_2, y_3$ be the basis corresponding to the columns of $C$.
    Let $B = C'AC$ be the matrix of $T$ relative to $y_1, y_2, y_3$.
    By Theorem 4.10.4, $B$ is the matrix of $T$ relative to $y_1, y_2, y_3$. Since $B$ is diagonal,
    by Theorem 6.4.17, $y_1, y_2, y_3$ are eigenvectors of $T$, and thus form a basis of $\mathbb{R}^3$ consisting of eigenvectors of $T$.
\end{proof}

\begin{tcolorbox}[title=Problem 3, breakable]
If you're familiar with `Euclid's algorithm', 
here's a shortcut for deciding in 6.6.6 whether $p$ has a repeated root. 
Calculate the greatest common divisor $d$ of $p$ and $p'$ (using Euclid's algorithm); 
$p$ has a repeated root if and only if $d$ is not a constant (Appendix B.5.4). 
The virtue of this method is that it avoids the quadratic formula 
and the radicals that usually come with it.
\{Hint: The only possible degrees for $d$ are $0, 1, 2$. 
Degree $0$ means $d$ is a constant ($p$ has no repeated roots); 
degree $2$ means that $p'$ is a divisor of $p$ 
(possible only when $p$ has a single root of multiplicity $3$); 
degree $1$ means that $p$ has two distinct roots, of multiplicities 
$2$ and $1$, respectively, the root of multiplicity $2$ being the one 
it shares with $p'$.\}
\end{tcolorbox}

\textbf{Solution: } Alrighty Then.

\subsection{A Geometric Application}


\begin{tcolorbox}[title=Problem 2, breakable]
For a real matrix
\[
A = \begin{pmatrix} a & c \\ b & d \end{pmatrix},
\]
let
\[
B = \begin{pmatrix} a & (b+c)/2 \\ (b+c)/2 & d \end{pmatrix}, \quad
C = \begin{pmatrix} 0 & (c-b)/2 \\ (b-c)/2 & 0 \end{pmatrix},
\]
that is, $B = \frac{1}{2}(A + A')$ and $C = \frac{1}{2}(A - A')$. Then $A = B + C$, with $B' = B$ and $C' = -C$. (Such matrices $C$ are called \textit{skew-symmetric}.)
\begin{enumerate}[(i)]
    \item Show that the characteristic roots of $C$ are of the form $\pm ri$ with $r$ real (that is, they are `pure imaginary').
    \item If $AA' = A'A$, show that $A$ is one of the two matrices
    \[
    \begin{pmatrix} a & b \\ b & d \end{pmatrix}, \quad
    \begin{pmatrix} a & -b \\ b & a \end{pmatrix} = aI + \begin{pmatrix} 0 & -b \\ b & 0 \end{pmatrix},
    \]
    thus either $A$ is symmetric or $A - aI$ is skew-symmetric. A matrix $A$ of the latter type is a scalar multiple of a rotation (5.4.10). (See also \S4.4, Exercise 5.)
    \item If either $A$ is symmetric or $A - aI$ is skew-symmetric, show that $AA' = A'A$. (An $n \times n$ real matrix that commutes with its transpose is said to be \textit{normal}.)
    \item Guess the definition of `normal' for a linear mapping in Euclidean space; for a complex matrix; for a linear mapping in unitary space.
\end{enumerate}
\end{tcolorbox}

\begin{proof}
    The characteristic polynomial of $C$ is
    \[
    |C - \lambda I| = \lambda^2 + \left(\frac{c-b}{2}\right)^2 = 0,
    \]
    so $\lambda^2 = -\left(\frac{c-b}{2}\right)^2$, which gives $\lambda = \pm \frac{c-b}{2}i$. Setting $r = \frac{c-b}{2} \in \mathbb{R}$, the characteristic roots are $\pm ri$.
\end{proof}

\begin{proof}
    We compute
    \[
    AA' = \begin{pmatrix} a & c \\ b & d \end{pmatrix}\begin{pmatrix} a & b \\ c & d \end{pmatrix} = \begin{pmatrix} a^2+c^2 & ab+cd \\ ab+cd & b^2+d^2 \end{pmatrix},
    \]
    \[
    A'A = \begin{pmatrix} a & b \\ c & d \end{pmatrix}\begin{pmatrix} a & c \\ b & d \end{pmatrix} = \begin{pmatrix} a^2+b^2 & ac+bd \\ ac+bd & c^2+d^2 \end{pmatrix}.
    \]
    Setting $AA' = A'A$, comparing entries gives $c^2 = b^2$ and $ab + cd = ac + bd$. From $c^2 = b^2$ we get $c = b$ or $c = -b$. If $c = b$ then $A = \begin{pmatrix} a & b \\ b & d \end{pmatrix}$, which is symmetric. If $c = -b$ then $A = \begin{pmatrix} a & -b \\ b & d \end{pmatrix}$, and substituting into $ab + cd = ac + bd$ gives $ab - bd = -ab + bd$, so $a = d$, giving $A = \begin{pmatrix} a & -b \\ b & a \end{pmatrix} = aI + \begin{pmatrix} 0 & -b \\ b & 0 \end{pmatrix}$, so $A - aI$ is skew-symmetric.
\end{proof}

\begin{proof}
    Suppose $A$ is symmetric, so $c = b$. Then
    \[
    AA' = \begin{pmatrix} a^2+b^2 & ab+bd \\ ab+bd & b^2+d^2 \end{pmatrix} = A'A,
    \]
    so $AA' = A'A$. Now suppose $A - aI$ is skew-symmetric, so $c = -b$ and $a = d$. Then
    \[
    AA' = \begin{pmatrix} a^2+b^2 & 0 \\ 0 & a^2+b^2 \end{pmatrix} = A'A,
    \]
    so $AA' = A'A$ in both cases.
\end{proof}

\begin{proof}
    A linear mapping $T$ on a Euclidean space is \textit{normal} if $TT^* = T^*T$, where $T^*$ is the adjoint of $T$. A complex matrix $A$ is \textit{normal} if $AA^* = A^*A$, where $A^*$ is the conjugate transpose. A linear mapping $T$ on a unitary space is \textit{normal} if $TT^* = T^*T$, where $T^*$ is the adjoint with respect to the unitary inner product.
\end{proof}